
## Introduction

For most of our daily lives, our senses are bombarded with vast amounts of information. Even the most mundane tasks, like grocery shopping, can involve encountering thousands of objects, people, and sounds. Successfully performing small, short-term goals like finding a specific flavored ice cream, involves holding information in mind while we sift through the near-unlimited amount of information available in the environment. The images we hold in memory inform those objects that capture our attention. We might recall a specific color from the packaging and filter information based on whether it matches that color, or we might remember its general location and selectively attend to that area. At the same time, the information we receive from the environment updates what we store in memory. We store the prices, and sizes of the objects that we have encountered and use this information to compare mentally across brands. Successful performance in everyday situations depends on the effortless execution of a continual back and forth between these complex processes, and in this very real-world sense, the processes of selective attention and short-term memory are functionally linked.           

Since the beginning of experimental psychology in the late 19th century, the study of human cognition has been parcellated into a set of distinct, fundamental constructs. Typically, these distinctions have been made based on the intuitions of foundational thinkers in psychology, and in his seminal work \textit{The Principles of Psychology}, William James recapitulated one such historical distinction between the constructs of attention and memory [@james_1890]. Throughout the 20th century, the concepts of both attention and memory were increasingly specified and formalized. As a result, selective attention is understood to encompass a set of underlying distinctions like overt versus covert orienting and endogenous versus exogenous attention. Similarly, the concept of memory is separated into specialized processes like short-term versus long-term memory and semantic versus episodic memory. These processes have in turn been parcellated into even more specific functional units. For example, the deployment of endogenous, covert attention depends on fundamental neural processes like target selection and distractor suppression.

Recently, empirical work has started to show that the fundamental processes necessary for the optimal functioning of selective attention may be related to, or shared by, the fundamental units necessary for the maintenance of objects in short-term memory. Modern models of short-term memory, or working memory as it has come to be known, typically depend on a system of executive control. Executive control determines the set of information that gains access to the resources that are responsible for storing and processing information in the short term. The role of this executive control system in working memory has considerable conceptual overlap with the broad role that selective attention plays in information processing in the human brain. Accordingly, modern approaches in experimental psychology and cognitive neuroscience are beginning to unify these traditionally disparate constructs and specify the nature of their interaction.

While historically progress in experimental psychology has been based on measures of behavior, a range of non-invasive techniques now exist which allow researchers to measure brain activity in awake humans. One of the most popular techniques for recording neural activity is electroencephalography (EEG) which allows for the direct measurement of neural activity at the timescale of actual neural processing. Methods of EEG data analysis have matured to the point where modern techniques can directly measure neural activity and make nuanced distinctions between processes that are invisible to behavioral measures. The event-related potential (ERP) technique is one such widely adopted method of EEG processing. ERPs now provide reliable, dissociable measures of fundamental neural processes such as those involved in covert attention, like target selection and distractor suppression.

This thesis aims to expand our understanding of the relationship between working memory and selective attention and to specify the neural mechanisms that may be shared by these two seemingly disparate systems. In study one, we used a behavioral task to perform a systematic analysis of the effect that irrelevant objects have on performance in the change-detection task. The change-detection task is a popular way of measuring visual working memory capacity; however, there are many subtle variations in the way it has been used. The effect of these variations on capacity measures is undetermined, and \textit{Study One} therefore sought to fill this gap in the literature. \textit{Studies Two} and \textit{Three} aimed to follow up two main effects established by study one while using EEG to simultaneously measure neural indices of attentional control. Specifically, in study two we were interested in seeing the effect that increased working memory load may have on neural measures of target selection, and distractor suppression. In study three, we aimed to understand how the presence of irrelevant objects in a change detection task may affect neural indices of target selection and distractor suppression.

## Interactions Between Working Memory and Attention
```{r copiedTextFromSAWMDistIntro}
#Everyday situations such as grocery shopping and driving depend on our ability to both efficiently allocate attention to relevant objects while suppressing distraction, as well as maintain and retrieve information from working memory. Although research over the past decade has demonstrated significant functional overlap between attention and working memory, the multifaceted nature of the relationship between these two constructs is not well understood [@fougnie_relationship_2008;@de_fockert_beyond_2013]. Converging evidence suggests that when the load on a concurrent working memory task is increased, performance on an attention task is subject to increased interference from irrelevant distractors [@ahmed_focusing_2012;@de_fockert_role_2001;@stins_role_2004]. There is also evidence that individuals low in working memory capacity show greater interference on a standard Stroop task [@kane_working-memory_2003], as well as greater interference on an Eriksen flanker task [@shipstead_working_2012]. Taken together, these findings suggest that the relationship between selective attention and working memory may be framed better in terms of working memory availability. From this perspective, increasing the working memory load on an individual would lead to a decrease in their working memory availability. What's more, individuals with low working memory capacity would have less overall available working memory (see @de_fockert_beyond_2013 for a review).

#Contemporary accounts of working memory availability now typically incorporate attentional control either as an important contributor to working memory capacity[@kane_controlled-attention_2001; @shipstead_mechanisms_2014], or in some cases as the primary determinant of working memory capacity [@engle_working_2018]. The question of why working memory availability is important for selective attention remains unanswered. The aim of this research was to specify the relationship between selective attention and working memory by recording electrophysiological indices of attentional control under varying working memory load.

#Evidence for the effects of low working memory availability on attentional interference is equivocal, and interference with any one of these processes [target selection, distractor suppression] would produce impaired behavioral performance associated with low working memory availability. Some evidence suggests that low working memory availability delays the speed with which individuals can deploy attention to relevant targets [@heitz_focusing_2007; @scalf_working_2011]. Yet, findings from other work suggests that low working memory availability may cause an increase in capture by irrelevant distractors [@fukuda_individual_2011; @vogel_neural_2005].

#A different account was proposed by @fukuda_individual_2011 in research using both psychophysical and electrophysiological measures of recovery from attentional capture in low and high capacity individuals. Findings from this work suggest that the two groups are equally prone to initial capture of attention, but availability of working memory allows more efficient disengagement from irrelevant objects after they have captured attention.
```
### The effect of attention on working memory.

A primary goal of the human visual system is to transform the light being received by photoreceptors on the retina, into a conscious percept which is useful for an individual's behavioral goals. Throughout this process, however, there are many stages that are limited in their processing capacity and therefore challenge the visual system's ability to optimize performance in complex visual environments. Visual short-term memory is an integral part of visual processing which is limited in both the rate at which it can consolidate information and the amount of information that it can store at a given point in time (Cowan, 2000; Marois & Ivanoff, 2005). Perceptual awareness is also inherently limited with regard to the amount of information that can be consciously perceived, unfolding serially such that at any point in time only a single percept gains dominance (Chelazzi, Libera, Sani, & Santandrea, 2010; Kim & Blake, 2005). Similarly, the motor system which vision informs is fundamentally limited in the number of actions which it can perform. An individual cannot simultaneously grasp and throw with the same hand for example, and performance of one action can interfere with the performance of subsequent actions (Telford, 1931; Smith, 1969; McCann & Johnston, 1992; Pashler 1994).

It has been suggested that the processing limitations of the visual system could be an inherent consequence of both the dynamics of neuronal energy demands, and the visual system's hierarchical architecture (Herculano-Houzel, 2011; Ames, 2000; Carrasco, 2011; Beck & Kastner, 2009; Desimone & Duncan, 1995; Duncan, 2005). Selective attention offers a solution to this problem, allowing for the flexible allocation of these limited resources to the most salient, and goal-relevant objects in the visual field. The classical view of how attention and working memory interact comes from this context where attention serves as a domain-general process for gating incoming information to limited capacity systems, of which working memory is one. A functioning working memory system is dependent on the successful operation of three main steps, encoding, maintenance, and retrieval, and research has established an essential role for attention in each of these three steps [@gazzaley_topdown_2012].

#### Attention modulates working memory performance.

`r #Alpha Power Gates Relevant Information during Working Memory Updating Peter Manza, Chui Luen Vera Hau and Hoi-Chung Leung `

Early experimental work based on the view of attention as a gating mechanism for short-term memory was unanimous in showing that attention during working memory encoding was critical to optimal memory performance. Typically these experiments employed a divided attention paradigm where participants performed a short-term memory task along with a concurrent, secondary, attention-demanding task. The rationale for these paradigms was that if the successful performance of a process like working memory encoding requires attention, then the division of attention during encoding should lead to impaired working memory performance. Indeed, multiple variations of this general method consistently confirmed that dividing attention during the encoding of memory objects lead to significant impairments in memory performance and that the size of the impairment increased as the attentional demands of the concurrent task increased [@craik_effects_1996;@baddeley_attention_1984;@anderson_effect_1974;@murdock_effects_1965]. The evidence, therefore, is reasonably unequivocal that attention is necessary for encoding objects into working memory, and that if attention is directed elsewhere during encoding, then task-relevant objects are not encoded into working memory.

`r #In addition, attention supports the transfer of perceptual information into VSTM (Averbach & Coriell, 1961; Hollingworth & Henderson, 2002; Irwin, 1992; Schmidt, Vogel, Woodman, & Luck, 2002; Sperling, 1960)`

Attention has also been shown to be critical to the maintenance of encoded information in working memory. @smyth_characteristics_1994 showed in a series of experiments that maintaining the ordered sequence of a set of locations is impaired when the maintenance period is filled with tasks that require shifts of attention. @awh_rehearsal_1998 expanded on this effect to show that not only did forcing unrelated shifts of attention during maintenance lead to working memory impairments, but that performance on the secondary task was improved when secondary task targets were presented in locations which matched the location of items in working memory. These results have been used to suggest that spatial attention is used as a rehearsal mechanism for the maintenance of locations in working memory.

Neuroimaging studies have also taken techniques traditionally developed to measure attentional control, and used them to observe the role that attention plays in the maintenance of information in working memory. When attention is deployed to objects in a given visual field, a range of techniques including functional magnetic resonance imaging (fMRI) and positron emission tomography (PET) have shown modulation of activity in the contralateral hemisphere of the visual cortex [@gratton_attention_1997;@heinze_combined_1994;@mangun_spatial_1987;@moran_selective_1985;@petersen_pet_1994]. @awh_rehearsal_1999 took advantage of this fact to show that the same effect is observed during the maintenance of information in working memory. Similarly, EEG has been used to show that when attention is deployed to a specific location, the presentation of probes in that location will elicit larger neural responses than the presentation of probes in unattended spaces. Taking advantage of this phenomenon, experiments have presented probes during the maintenance interval of a working memory task and measured the neural response to those probes using EEG. Results show that probes presented in the location of a concurrently maintained object, elicit larger neural responses than probes presented elsewhere [@jha_tracking_2002;@awh_role_2000]. This result mirrors the effect that attention has on a probe stimulus and suggests that the maintenance of an object in working memory is accompanied by maintenance of attention at that location.

The evidence is more equivocal regarding the effect of attention on working memory retrieval; however, there do appear to be instances in which attention can be shown to influence retrieval ability [@fernandes_divided_2000]. Studies investigating the effect of attention on working memory retrieval have traditionally relied on the divided attention paradigms previously used to establish the importance of attention for working memory encoding. Early results demonstrated that dividing attention during retrieval lead to similar impairments as dividing attention during encoding, although the size of the impairment was reduced [@dywan_effects_1990;@moscovitch_cognitive_1994;@park_effects_1989]. Other work showed no such effect of divided attention at retrieval on memory performance leading to suggestions that retrieval processes were automatic and not reliant on attention [@craik1996effects;@baddeley_attention_1984]. @fernandes_divided_2000 proposed a resolution to these inconsistencies and used a series of experiments to conclude that attention is necessary for the successful retrieval of items from working memory, but only when the concurrent task was competing for access to word-specific representational systems.

The role that attention plays in retrieving information from working memory has since been investigated using neuroimaging methods. The most common method of doing this has been to record EEG while participants perform a probed working memory task. In probed memory tasks, participants encode a set of information which they maintain over a short delay, and the test display presents a probe indicating which of the encoded objects they should retrieve. ERP measures previously established to reflect the allocation of attention to locations in space are also elicited by the probe, suggesting that attention is being used to search the contents of working memory and retrieve relevant information from the probed locations [@leszczynski_recoding_2012;@dellacqua_orienting_2010;@eimer_electrophysiological_2010]. Importantly, @kuo_searching_2009 showed that participants attend to lateralized locations during retrieval even when the probe itself is presented centrally, as long as the retrieved object was originally encoded at that lateralized location (although see Broadway, Hilimire, Corballis 2012 for an example where this did not occur). Together, this evidence suggests that the process of retrieving information from working memory requires the allocation of attention to spatiotopically organized representations maintained in working memory, which is analogous to the selection of information from the external environment. `r #Rehearsal in Spatial Working Memory: Evidence From Neuroimaging showed this with fMRI`

The evidence reviewed above establishes a critical role for attention in the successful operation of working memory. Attention appears to be crucial for the selective encoding of relevant objects, and maintenance of those objects within working memory, as well as the subsequent retrieval of those objects. This supports initial conceptions of attention as an independent cognitive system which is used to gate the limited resources of working memory. However, a separate body of literature has established a similarly critical role for working memory in the efficient allocation of selective attention.
`r #Attention appears to gate VSTM, increasing recall ability (Dudukovic, Du Brow, & Wagner, 2009), modulating the configuration of VSTM (Jiang, Olson & Chun, 2000), and maintaining information about specific features in a display, as well as information about how those features are bound into discrete objects (Johnson, Hollingworth, & Luck, 2008).`

### The effect of working memory on attention.

#### Working memory guides attention.

```{r WMGuidesAttn}
#Automatic guidance of attention from working memory David Soto1 , John Hodsoll , Pia Rotshtein and Glyn W. Humphreys
#Different states in visual working memory: when it guides attention and when it does not Christian N.L. Olivers , Judith Peters , Roos Houtkamp and Pieter R. Roelfsema
```

`r #Automatic and strategic effects in the guidance of attention by working memory representations Nancy B. Carlisle and Geoffrey F. Woodman`

One of the primary ways that working memory and attention have been linked is through either implicit or explicit recognition of working memory as the store for attention-guiding templates. Visual search tasks, where participants are presented with an array of items and must identify a target within the set, are regarded as a classic example of an attention task. A prominent model of the processing involved in this task is the guided search model [@wolfe_guided_1989;@wolfe_guided_1994]. The guided search model is a two-stage model where objects in the visual system initially get decomposed into a set of basic features like color and orientation which are then bound by attention into objects. The novelty of the guided search model as opposed to earlier two-stage models (such as feature integration), was the addition of an abstract guiding feature representation which gates access to the attentional bottleneck, but which is itself not a part of the processing pathway [@nobre_oxford_2014]. While visual search is often considered an exclusively attention-based task, extant models of visual search performance typically incorporate this idea of an attentional template where visual objects are temporarily stored and used to guide search. The properties of guiding templates superficially line up with the properties of working memory, they are both internally maintained sets of bound features and locations, and empirical evidence has since accumulated to suggest that they are one and the same.

The role of working memory in visual search has been demonstrated by examining the interaction between working memory contents and search efficiency. Central to the development of two-stage models of visual search was the observation that visual search could be either inefficient or efficient depending on the properties of the search task. Inefficient search is visual search which takes longer as the number of on-screen objects increases, whereas efficient search is visual search which is unaffected by the number of on-screen objects [@nobre_oxford_2014]. Typically efficient search occurs when the target possesses a pop-out feature, for example, if the target is one color and all of the distractors are another. In this case, participants can quickly identify the target no matter how many irrelevantly colored distractors are present. The explanation for this effect in the guided search model is that the target is distinct on a pre-attentive feature and therefore the target and distractor are dissociated before the attentional bottleneck. Experimental evidence has since shown that the extent to which search can be efficient, at least in the case of orientation and size based pop-out, depends on having a template of the target feature maintained in working memory [@hodsoll_effect_2005;@hodsoll_dissociating_2006;@hodsoll_driving_2001]. In trials where participants did not know the orientation of an upcoming target but instead just had to identify the odd one out, the advantage of a category based pop-out disappeared.
`r #Contingent capture`
The most convincing evidence supporting the idea that working memory may be the system used to guide attention comes from dual tasks where working memory contents are deliberately unrelated to the search task. In one such study, @olivers_feature-based_2006 used a dual task paradigm where participants were required to maintain a specific color in working memory from the start of the trial. While this color was maintained, participants performed a visual search task of a circular array to find and respond to a target shape. Crucially in their task, the search displays also contained distractor stimuli which had either no color, unrelated color, or matched the color of the information stored in working memory. Consistent with the hypothesis that the contents of working memory guide attention, distractors which shared the color of working memory contents resulted in slowed visual search responses. This is particularly compelling given that the working memory contents were irrelevant to the visual search task and the target had been defined along a completely different dimension (shape). Their results imply not only that the contents of working memory can be used to guide attention, but that the contents of working memory automatically guide attention, even if it leads to impaired performance on the task.

Additional evidence of the effect that working memory contents have on visual search has been shown using neural measures taken during these tasks. For example, @kumar_electrophysiological_2009 had participants maintain a colored shape in working memory while they performed a concurrent visual search task. The visual search objects were each presented inside a colored shape on the left and right sides of the display. In half of the trials, one of these colored shapes matched the object stored in working memory. Throughout the task, @kumar_electrophysiological_2009 recorded EEG and used the recordings to extract an electrophysiological component which indexes the shift of attention to the left and right of the display. Both their behavioral results and EEG measures showed that attention was automatically deployed to the location of objects which matched the contents of working memory. This effect was observable even though the objects were not relevant to the visual search task. A similar paradigm used in conjunction with fMRI showed that the presentation of a stored object during the visual search display leads to enhanced activity in a frontotemporal network involved in encoding the original object. This pattern of results is not elicited by the repeated presentation of the object, indicating that this effect is dependent on the object being actively maintained in working memory [@soto_dissociating_2007].

#### Working memory availability modulates attention.

##### Evidence from within-subject manipulation of working memory load.

The critical role that working memory plays in the successful deployment of attention is also demonstrated by the observation that the amount of working memory resources available to an individual has significant effects on their ability to perform attention-based tasks [@de_fockert_beyond_2013]. Evidence for this fact comes from converging approaches, the first of which focuses on within-subject comparisons where concurrent working memory load is manipulated while participants perform the attention-based task. An early example of this approach used a dual task where participants encoded a set of numbers at the start of the trial, and during the maintenance period were shown pictures of famous faces with famous names attached [@de_fockert_role_2001]. In half of these trials, the face would match the name, whereas in the other half the face and name would be incongruent. Participants were required to respond to the names while ignoring the faces. Results showed that as the amount of information being maintained in working memory increased, participants performed worse on the incongruent trials. This indicates that participants struggled to ignore the task-relevant faces when concurrent working memory load increased.

This pattern of results has been replicated with a range of interference effects that are measurable with classic attention tasks. A seminal interference effect is the Stroop effect where participants are required to read aloud a list of color names printed in colored ink. Interference in this task occurs when the color name that the participant is reading has been printed in an incongruent ink color, for example, the word "red" printed in green [@Stroop_studies_1935]. The Stroop effect is quantified as the response time difference between these incongruent trials, and congruent trials where the color name matches its ink color. If participants perform a concurrent working memory task, increasing the amount of load on working memory leads to increases in the size of the Stroop effect [@stins_role_2004]. Similarly, performance on the Eriksen flanker task [@Eriksen_effects_1974] where participants respond to a central stimulus which is flanked by either congruent or incongruent stimuli, interacts with concurrent working memory load. In this paradigm, the response time difference between the congruent and incongruent trials is believed to index the extent to which participants can focus on the central target and suppress the effect of the irrelevant flankers. The concurrent maintenance of six digits in working memory results in larger interference effects by the flankers than the concurrent maintenance of only one digit [@de_fockert_no_2010;@lavie_load_2004;@ahmed_focusing_2012]. In all of these paradigms, distractors are present on every trial, and therefore their presence is perfectly predictable. Distractors in these tasks are also congruent in half of the trials making them potentially task-relevant. This evidence would, therefore, limit our interpretation of the role that working memory has in attention, to the active suppression of predictable, partially relevant distractors.

However, the influence of working memory load on interference effects has also been established in paradigms where distractor presence is unpredictable and completely irrelevant to the task. For example, when participants are required to search for a target shape, the presence of a uniquely colored distractor causes performance impairments reflecting the extent to which the salient distractor captures their attention [@theeuwes_perceptual_1992]. When paired with a concurrent working memory task, high working memory load results in larger interference from these distractors even though the distractor is present in only some trials and is defined on a task-irrelevant dimension [@boot_attention_2005;@lavie_role_2005;@lavie_frontal_2006]. Working memory load has also been shown to mediate the effect of inattentional blindness; a phenomenon where the performance of perceptually demanding tasks can result in unexpected stimuli going unnoticed. Most famously, inattentional blindness was demonstrated when participants tasked with counting basketball passes, often missed the appearance of a person dressed in a gorilla costume [@simons_gorillas_1999]. This effect can be eliminated, however, by the concurrent maintenance of information in working memory. This means that participants are much more likely to report seeing the unexpected stimulus when concurrent working memory load is high. 

In contrast to the above findings, a number of studies have failed to show an effect of working memory load on visual search efficiency. @logan1978attention investigated this effect using a verbal working memory task and showed that while adding a concurrent working memory load had a general effect on performance of the visual search task, it did not interact with visual search set size as you would expect if it was impacting on search speed. @woodman2001visual carried out a similar expeirment this time using a visual working memory task and found the same results, concurrent working memory load had the same effect on visual search speed regardless of how many visual search items were present in the display. In these tasks, if working memory load impacted on search speed then doubling the number of search items should result in a doubling of the effect of working memory load, in both cases it did it. A key distinction between these studies and those studies which have found effects is the salience of the visual search distractors. As suggested by @lavie_load_2004, these discrepancies suggest that working memory's role is specifically relevant in situations where targets are competing for attention with low priority but highly salient distractors.

Burgeoning neuroimaging evidence has also provided converging evidence for the effect of working memory load on attention. @de_fockert_role_2001 showed in their study that while participants responded to famous names, the interference caused by irrelevant faces, which increased under higher working memory load, also coincides with increased face related processing in the visual cortex. Activity in frontal areas associated with working memory have also been associated with the size of interference effects in attention tasks [@fockert_neural_2004], and more significantly, activity in the right prefrontal cortex has been correlated with interference effects exclusively under high working memory load [@de_fockert_role_2012]. The pervasiveness of these effect has been demonstrated by @kelley_working_2010 who used fMRI to show that the relationship between working memory and distractor interference is observable at the level of the primary visual cortex. These data, along with the body of behavioral work, suggest that working memory is essential for the optimal performance of selective attention, and that placing an individual under increased working memory load causes impairments of their attentional processing.

##### Evidence from individual differences in working memory capacity.

The second main approach that has been used to demonstrate the importance of working memory to selective attention is a between-subjects approach where the natural variation in working memory capacity is associated with performance on attention-based tasks. It is well known that while the average person's working memory can store approximately three to four pieces of information [@alvarez_capacity_2004;@awh_visual_2007;@davis_capacity_2005;@pashler_familiarity_1988;@sperling_information_1960;@xu_dissociable_2006], this number can vary significantly across individuals [@awh_visual_2007a;@rouder_assessment_2008]. The rationale for relating this to selective attention is that if some individuals have a measurably smaller working memory capacity than others, and working memory is critical for selective attention, then those same individuals will perform worse on tests of attention. Indeed, there appear to be reliable effects of working memory capacity on performance on many of the attention tasks described earlier.

Individual working memory is associated with interference effects derived from tasks like the Stroop task and Eriksen flanker task. @kane_working-memory_2003 carried out a series of experiments where working memory capacity was measured using the operation span task, and performance on the Stroop task was compared between individuals with high versus low working memory capacity. Their results consistently showed that individuals with a high working memory capacity incurred significantly less interference in the Stroop task than individuals with low working memory capacity. In their task, @kane_working-memory_2003 also manipulated the number of congruent trials within the task with the expectation that when the number of incongruent trials was low, some individuals would stop maintaining the task goals and therefore suffer greater interference from the rare incongruent trials. The results showed that high working memory capacity participants were better at not just competition resolution in the Stroop task, but also at goal maintenance. They therefore elicited smaller interference effects in all situations. Similarly, interference measured using the Eriksen-type flanker tasks is seen to be significantly smaller for high capacity individuals [@shipstead_working_2012].

A more nuanced measure of this relationship was established by @kane_controlled-attention_2001 using both prosaccade and antisaccade tasks to tease apart the effect that working memory capacity differences have on reflexive orienting. In the prosaccade task, a salient cue appears on screen indicating that an upcoming target will appear in its location. In this case, the abrupt onset of the cue attracts attention and participant performance benefits from that allocation of attention. In the antisaccade task, however, the cue indicates that the upcoming target will be located on the opposite side of the screen. In this case, optimal performance on the task is achieved by either efficiently recovering from attentional capture by the cue, or by preventing capture in the first place. These data show that individuals with a high working memory capacity outperform individuals with a low working memory capacity in the antisaccade task but not the prosaccade task. This indicates that the benefit of working memory capacity may lie in the suppression of, or disengagement from, the onset of salient visual objects rather than orienting speed. They also show that this effect remains even when participants get to practice the task across ten blocks [@kane_controlled-attention_2001].

The role that working memory capacity plays in selective attention has also been demonstrated in the auditory domain. @conway_cocktail_2001 investigated the cocktail party effect and its relationship to working memory capacity in a task where participants listened to two auditory messages simultaneously. The classic cocktail party effect demonstrates that while participants are asked to attend to one of the messages, a portion of them will report hearing their name in the irrelevant auditory stream even though it is never there. @conway_cocktail_2001 managed to replicate this general effect and show that those individuals who reported hearing their name in the irrelevant message, also tended to have a lower working memory capacity. They used this as evidence that low capacity individuals are struggling to suppress the irrelevant stream of information.

Similar effects of capacity on distraction have been demonstrated to occur across sensory domains. When participants perform a simple visual task categorizing sets of arrows as pointing either left or right, their performance is impaired by the onset of an auditory oddball presented just before the arrows are shown [@sorqvist_working_2012]. This interference effect is relatively large at the start of the experiment and attenuates toward the end of the experiment. Presumably, this is the result of participants anticipating oddball onset as the experiment progresses, and engaging preparatory distractor suppression. Notably, working memory capacity was related to the size of the interference effect at the end of the experiment but not at the start of the experiment [@sorqvist_working_2012]. This cross-domain evidence suggests that working memory capacity is related to the engagement of attentional control mechanisms caused by the expectation of distraction and is not necessarily related to a ubiquitous advantage in distractor disengagement processes. `r # at some point reference Tsuchida et al., 2012 who used EEG with this to show that the N1 to the oddball is smaller for high WM Ss`

`r ## Engle incorporating attention into working memory models: Working Memory and Executive Attention: A Revisit Randall W. Engle `
`r ## Unnecessary storage and distractor suppression`
`r ## Working memory benchmarks and relevant attention effects`

## Specifying the Relationship Between Working Memory and Attention

A consensus is now building in favor of the general view that working memory and selective attention overlap in their roles in cognition. Contemporary research, therefore, is attempting to specify the attentional process or processes that are related to working memory performance. Optimal performance of selective attention relies on several underlying processes including target identification and selection, proactive suppression of possible distractors, and efficient disengagement from irrelevant distractors that capture attention [@carrasco_visual_2011]. Evidence for the effects of low working memory availability on attentional interference is equivocal because interference with any one of these processes would produce impaired behavioral performance. The focus on filtering and interference effects have led many to suggest that working memory is essential for distractor suppression [@fukuda_individual_2011;@vogel_neural_2005]. However, other accounts have suggested that working memory is principally involved in the maintenance of target information [@engle2018working;@heitz_focusing_2007;@scalf_working_2011], and this issue has come to occupy a central role in the literature. A range of experiments have now attempted to establish which of these distinct, but interrelated, attentional sub-processes is primarily responsible for the relationship between attention and working memory.

### Target selection.

One critical function required to perform effectively in a goal-directed task is the identification and selection of relevant targets. Target selection is essential to the successful performance of selective attention at all levels, from the overt orienting of the head and eyes to place relevant objects onto the fovea, to covert orienting of neural resources which increase the processing of target representations in the cortex [@carrasco_visual_2011]. When investigating the overlap between working memory and attention, therefore, many researchers have focused on the process of target selection and its overlapping role in the use of these two cognitive constructs.

@scalf_working_2011 paired fMRI with a dual task to examine whether working memory load affects the speed with which individuals can deploy attention to relevant targets. In their task, participants were presented with a target set of symbols (T1) and attempted to store their identity and location. After a short delay, a letter (T2) was shown on screen and participants were subsequently tested on their storage of T1. In some trials, participants were instructed to ignore T2, while in other trials they were required to report the letter's identity. fMRI revealed a delayed response to T2 in the visual cortex when it followed T1 at a short delay, as well as when the encoding demands of T1 were high. @scalf_working_2011 interpreted this evidence as indicating that increased working memory demands lead to a delay in processes of target selection due to their concurrent use in the working memory task.

Systematic manipulation of the Eriksen flanker task has also been used to suggest that individual differences in working memory capacity affect the speed of attentional deployment to targets amongst distractors [@heitz_focusing_2007]. In their version of the Eriksen flanker task @heitz_focusing_2007 showed participants a string of letters containing a central target and either congruent or incongruent flankers. Crucially, the response deadline was varied across blocks such that participants had 700ms to respond at the start of the experiment which was reduced to a 200ms response period by the end. Participant accuracy was at chance when response deadlines were very short, as participants did not have enough time to identify any of the objects on screen and were therefore guessing. As response periods increase, participants have enough time to extract information from the set of incongruent flankers, and therefore accuracy drops significantly below chance as they respond to incongruent information. Once participants have enough time to focus their attention away from the flankers and down onto the central target, participant accuracy increases and eventually asymptotes. High capacity individuals can do this at shorter delays, implying that they are faster at focusing their attention onto the target than low capacity individuals. @poole_working-memory_2009 subsequently showed that they are also better at maintaining the focus of spatial attention on targets across time.

While load manipulations and capacity differences have each been shown to have independent effects on attentional deployment to targets, @ahmed_focusing_2012 investigated the interaction between load and capacity within the same experiment. An Eriksen-type flanker task was again used; however, this time it was presented during the maintenance interval of a digit recall task which had high load and low load conditions. @ahmed_focusing_2012 systematically varied the distance between the target and flankers in an Eriksen flanker while participants made speeded responses. The resulting pattern of interference across target-flanker distances provided a measure of the spatial distribution of attention on the task on the basis that flankers will only interfere with the target when they fall within the focus of attention. The results showed that spatial attention is more constrained to the target under low load than high load, and is more constrained in high capacity individuals than low capacity individuals. These patterns interact such that high capacity individuals who are under low load have the most tightly constrained attentional focus. When they are placed under high load, however, high capacity individuals begin to look more like low capacity individuals under low load. When low capacity individuals are under high load, the distribution of spatial attention is the least constrained of all. These data further suggest that decreased working memory availability, whether because of a smaller innate capacity or temporary increases of concurrent load, causes slower and less spatially specific allocation of attention to targets.

The evidence provided has been used to suggest that when the availability of working memory is reduced, processes of target selection and maintenance are reduced. Therefore the specific attentional process shared by working memory and attention is posited to be the process of target selection. The results presented however are not functionally specific enough to make these claims with certainty. In their fMRI study, for example, @scalf_working_2011 recorded delayed target processing when a concurrent working memory load was introduced. An alternate possibility, however, is that delayed disengagement from the T1 stimulus is the cause of the delayed response to T2, and that target selection speed per se, is unaffected. Similarly, many of these paradigms use a variation of the Eriksen flanker task which includes distracting flankers [@heitz_focusing_2007;@poole_working-memory_2009;@ahmed_focusing_2012]. Consequently, in each case, it is impossible to tease apart the effects of target selection, distractor suppression, and distractor disengagement. In fact, other evidence has been used to argue that distractor related processes underlie the relationship between working memory and attention.

### Distractor capture.

Although the pursuit of an individual's goals requires voluntary allocation of attention to goal-relevant objects and locations, it is well established that objects in the environment can involuntarily capture an individual's attention [@nobre_oxford_2014]. Performance on goal-oriented tasks is, therefore, the output of competitive interactions between these two ways of orienting attention. Sub-optimal performance of goal-directed behavior can, therefore, be the result of underactive processes of goal maintenance and target selection as described in the previous section. However, an alternate account is that it is the result of the overactive capture of attention by task-irrelevant stimuli. A separate line of research into working memory and attention has investigated whether working memory and attention interact through their shared involvement with systems of distractor capture.

@fukuda_human_2009 used a cued target identification task along with EEG to establish that working memory is related specifically to distractor capture and not to target selection. In their task, participants were cued to the location of an upcoming target box and had to report which side of the target box had a gap in it. In two-thirds of trials, the target array was followed by a salient probe stimulus 50ms later, at either the target location or at the location of one of the irrelevant objects. They measured early visual responses to the target display and the probe display to show that while responses to the target stimuli are the same for individuals with low and high working memory capacity, probe responses differ. For high capacity individuals, probes presented at the target location elicited large neural responses whereas probes presented at the distractor locations did not. This suggests that their attention was constrained to the target location and was not captured by probe onset. Low capacity individuals, on the other hand, showed equivalent responses to both probe types, implying that irrelevant stimuli more easily capture their attention.

@fukuda_human_2009 also tested the idea of unnecessary storage, a specific mechanism which would explain why distractor capture is associated with working memory capacity. Unnecessary storage is the proposal that increased distractor capture leads to the storage of irrelevant items in working memory. This would reduce the functional capacity of an individual as the inclusion of any irrelevant items in working memory reduces the amount of capacity that is available for storing task-relevant objects. In their experiment, @fukuda_human_2009 included a working memory version of their paradigm where participants stored a set of objects which were quickly followed by a probe, and were then tested on the stored objects after a delay. @fukuda_human_2009 used an electrophysiological measure of object storage which increases as working memory set size increases [@vogel_neural_2005]. Individuals whose measure of object storage increased in the presence of distractors were posited to be unnecessarily storing those objects, and the size of this effect was used to calculate an individual's filtering efficiency. Filtering efficiency was shown to be correlated with working memory capacity, and therefore they concluded that low capacity individuals have impaired distractor inhibition which leads to the unnecessary storage of distractor items in working memory.

Other authors have used similar effects to reinforce the view that working memory capacity is specifically related to an individual's ability to ignore irrelevant objects. Brain activity recorded using fMRI has also measured filtering ability by informing participants of the presence or absence of distractors in upcoming displays, and measuring the difference in preparatory activity. This activity is significantly correlated with working memory capacity [@mcnab_prefrontal_2008]. EEG evidence of item storage has shown that low capacity individuals can be shown to have stored more objects than high capacity individuals when some of the objects displayed are irrelevant, again suggesting that they are storing not only the task-relevant objects but the irrelevant objects as well. While these experiments have concluded that low capacity individuals struggle with the ability to ignore irrelevant objects, as was the case with evidence for target selection, they similarly lack the functional specificity to make this claim with certainty.

In all cases, these paradigms seem unable to rule out the possibility that low capacity individuals are failing at the maintenance of target information. In the task used by @fukuda_human_2009, it is possible that high capacity individuals are better at using the cue to constrain attention to the target representation. Evidence of apparent differences in distractor capture could, therefore, be a consequence of differences in target selection. Low and high capacity individuals may be equally prone to the capture of their attention by distractor items present in the focus of their attention, but high capacity individuals may simply be more capable of narrowing this focus as compared to low capacity individuals. Similarly, the preparatory activity measured by @mcnab_prefrontal_2008, and unnecessary storage itself, may be a consequence of impaired target selection and maintenance. A third alternative has also since been proposed, proposing that it may not be the initial capture of attention which differs, but rather the subsequent recovery speed.

### Distractor disengagement.

The fact that irrelevant distractors impact individuals with low working memory capacity more than individuals with high working memory capacity suggests that low capacity individuals struggle more with suppressing distractor capture. An alternate account, however, is that both groups are equally prone to the initial capture of attention by irrelevant distractors, and that performance differences are the result of differences in their ability to disengage attention from the distractor object, before reorienting attention to the target. This nuanced distinction was tested specifically by @fukuda_individual_2011.

@fukuda_individual_2011 used both psychophysical and electrophysiological measures in a visual search task to distinguish between distractor capture and distractor disengagement. Participants in their task had to identify the orientation of a target object defined by a specific color. Before the onset of the search array, a flanker would briefly appear in two-thirds of trials possessing either the target color, or a non-target color. The onset of the flanker is predicted to cause a shift of attention to the flanker location, decreasing performance on the search task relative to trials where there is no flanker. Flankers possessing the target color are predicted to be more difficult to disengage from, and therefore differences in distractor disengagement speed should be present in these trials. @fukuda_individual_2011 also titrated the length of time between flanker and target to observe the length of time each individual needs to recover from flanker onset. Their results showed that high and low capacity individuals are equally prone to attentional capture by non-target flankers; however, high capacity individuals recover faster from target colored flankers.

@fukuda_individual_2011 followed up with a similar EEG experiment to provide neural evidence to distinguish between distractor capture and distractor disengagement [@fukuda_individual_2011]. In this task, participants were cued to the location of an upcoming target which was presented amongst distractors. Their task was to respond to the target, and then a salient probe would appear at either the target or distractor location. In this version, however, they varied the interval between target and probe displays from 50ms to 200ms to measure the effect of probe location as a function of available disengagement time. Their results show that with a 50ms interval, there is no difference between the neural response to probes at distractor and target locations for either high or low capacity individuals. This indicates that at very short delays, neither group can disengage from distractor locations and focus attention on the target. High capacity individuals show a reliable difference by 100ms, whereas low capacity individuals do not show equivalent differences until the interval is 200ms long. These results corroborate the initial findings that low capacity individuals are not necessarily more prone to capture by distractors but specifically struggle with the ability to disengage efficiently from distractors which have captured attention.

Experimental evidence for impairments of distractor disengagement in low capacity individuals is reasonably scant. Critically, while there is very little evidence to contradict the findings of @fukuda_individual_2011, there is also very little replication or extension of the effects they reported. The experimental paradigms used to date have typically lacked the functional specificity required to tease apart nuanced sub-processes of attention like target selection, distractor capture, and distractor disengagement.

## Measuring Attention with EEG
In order to concretely specify the nature of the relationship between working memory and selective attention, we therefore require methods which allow us to dissociate subtle differences in sub-processes of attention which are highly related and interacting. Early models of selective attention have been based on the use of classic behavioral paradigms to establish evidence for both target processing (Carrasco, Williams, & Yeshurun, 2002; Carrasco, Ling, & Read, 2004; Ling & Carrasco, 2006) and distractor suppression (Lu & Dosher, 2000; Frings, Wentura, & Wuhr, 2012). Recent work has supplemented these paradigms with neuroimaging techniques to allow for a more direct examination of the neural processes involved. Single cell recordings in non-human primates have been used to measure target enhancement, and distractor suppression,  as has functional magnetic resonance imaging (fMRI) in humans (Gandhi, Heeger, & Boynton, 1999; Brefczynski & DeYoe, 1999; Kastner, Pinsk, De Weerd, Desimone, & Ungerleider, 1999; Kastner, De Weerd, Desimone, & Ungerleider, 1998). The high temporal resolution of EEG has allowed for the detailed study of the time course of attentional processes in humans; however EEG analysis often involves traditional ERP techniques which are limited in their ability to attribute changes in activity to specific psychological processes.
`r #Alpha`
Electrophysiological recordings in humans have provided evidence of attention's role in enhancing the signal of an attended item. When EEG is used to calculate ERPs in the Posner cueing paradigm (Posner, 1980), valid trials (where individuals are cued and therefore attend to the location of a subsequent stimulus) correspond to increases in the amplitude of the P1 and N1 components when compared to invalid trials (where the stimulus appears in a non-cued location) (Mangun & Hillyard, 1991). Luck, Hillyard, Mouloua, Woldorff, Clark, and Hawkins (1994) refined this finding and suggested that it is the amplitude of the N1 specifically which indexed enhancement of an attended stimulus. The P3 has also been shown to significantly increase in amplitude during attention-demanding tasks as has the N4, a component traditionally observed in response to words (Coull, 1998). In contrast, the number of studies utilizing traditional ERP methods to investigate distractor representations is comparatively small. One ERP component which has been associated with distractors is the P3a which, along with the P3b, is a subcomponent of the P300. Bledowski et al. (2004) used an oddball paradigm to show that while P3b is elicited by both targets and distractors, and is localized to parietal and inferior temporal areas, P3a is exclusively elicited by distractors and localized to the precentral sulcus and anterior insula. A frontal negativity has also been observed to cumulatively activate as the number of distractors preceding a target increases (Niedeggen, Michael, & Hesselman, 2012). 

While these traditional event-related components like the P1, N1, P3, and N4 provide neural indices of attentional processing in the human visual system, it is difficult to attribute changes in traditional ERP activity to specific psychological processes. However, a procedure known as the contralateral control method traditionally developed for studying the motor system has recently been applied to event-related potentials in the visual search domain. This has yielded a set of dissociable components which appear to index the processes of target selection, distractor suppression, and storage of target features relevant to the upcoming response. Accordingly, it has offered significant insight into the study of attention and provides the functional specificity needed to interrogate the fundamental processes shared by working memory and attention.

### The contralateral control method.

The contralateral control method addresses many of the problems associated with traditional ERP measures. It allows for the isolation of activity related specifically to the experimental variables that are being manipulated and removes unrelated activity by taking advantage of the hemispheric organization of the cortex [@oostenveld_brain_2003]. A well-known example of contralateral organisation is observed in the motor cortex, where preparing movements of the right hand elicits greater activity in the left motor cortex whereas preparing movements of the left hand elicits increased activity in the right motor cortex. It is possible then, if EEG is recorded during these tasks, to use the contralateral control method of analysis to extract only that activity which is systematically related to a hand movement [@eimer_lateralized_1998].

Standard EEG nets are arranged symmetrically such that each electrode on the left-hand side of the scalp, has an equivalently placed electrode on the right. This means that in the case of preparing a right-handed movement, activity is recorded at equivalent scalp locations over the right and left motor cortex and when participants are preparing a left-handed movement, activity is recorded at equivalent scalp locations over the right and left motor cortex. Activity is then collapsed across conditions by averaging the contralateral activity together (left hemisphere electrodes for the right-hand condition and right hemisphere electrodes in the left-hand condition) and then the ipsilateral activity together (right hemisphere electrodes for the right-hand condition and left hemisphere electrodes in the left-hand condition). Finally, ipsilateral activity is subtracted from contralateral activity to produce the difference wave which shows only the activity produced contralateral to a prepared hand action. Crucially, all activity that is the same in both hemispheres has been removed, as well as any activity that is systematically different between hemispheres. This makes it easier to relate brain activity to underlying psychological processes because as long as an appropriate experimental design is used, the only activity remaining is the activity systematically lateralized in response to manipulations of the experimental variable (Gratton, 1998). 

The visual system has a hemispheric organisation similar to the motor system such that the left visual field (LVF) projects to the right visual cortex and the right visual field (RVF) projects to the left visual cortex. Researchers have therefore been able to apply the contralateral control method to isolate lateralized activity which specifically indexes attentional processes in the visual system. Lateralized ERPs have typically been studied in visual selective attention with visual search paradigms, where participants are presented with an array of objects and must identify and respond to some feature of a target stimulus embedded within the array. Participants fixate on a central cross throughout, and bilateral displays are used to ensure a sensory balance between visual fields. Using measurements around the onset of the visual search array and applying the contralateral control method makes it possible to identify lateralized ERPs reflecting mechanisms of selective attention. Electrophysiological studies utilizing this approach have identified a set of lateralized components which appear to index attentional processes consistently and may, therefore, be crucial to the study of visual attention.

### The N2pc component.

The lateralized component which has become a focus of studies of visual selective attention is the N2pc, named after its latency and scalp distribution. It is recorded as an increased negative voltage occurring approximately 180-250ms post-stimulus presentation, around the N2 time range, at posterior scalp sites contralateral to the attended stimulus. The precise attentional mechanism which the N2pc reflects has received a lot of attention as a full understanding of the N2pc is increasingly essential for researchers in many fields. N2pc-like effects were initially observed in many studies [@heinze_visual_1990;@luck_visual_1990;@luck_electrophysiological_1990] but were first described as the N2pc by [@luck_electrophysiological_1994]. It has since been described as indexing both target selection and distractor suppression by different authors at various times however substantial progress has been made to determine its functional significance.

In their original description of the N2pc, [@luck_electrophysiological_1994] used displays containing eight identical bars scattered around a fixation cross. In half of the displays, one of the bars would pop-out from the rest by being different in either orientation, color, or size. Participants had to identify whether the pop-out bar possessed a predefined target attribute. Their results showed that the N2pc was significantly larger when the pop-out possessed the target attribute than when a non-target pop-out appeared in the display. Current source density maps indicated that despite its late latency, the generator of N2pc appeared to be in the occipital lobe. They concluded from the N2pc modulations, latency, and location estimates, that it indexes a process being applied to targets rather than non-targets, and may reflect the control of information flow in the visual system through a top-down filtering mechanism. @eimer1996n2pc extended this finding by showing that target attributes like form, color, and content could affect the N2pc time range, also arguing that the presence of the N2pc when distraction is minimal indicates that it represents the identification of task-relevant stimuli.

A group of early experiments, however, appear to contradict this finding and instead suggest that the N2pc indexes distractor suppression. When distracting items are removed from a display, made relevant to the task at hand, or when all items in the display are made to be identical targets, an N2pc is no longer elicited [@luck_spatial_1994]. @luck_bridging_1997 proposed the ambiguity resolution theory as a result of this work as well as their work comparing the N2pc to electrophysiological studies in monkeys. Single unit recordings in non-human primates have provided significant evidence for the existence of a suppressive mechanism in visual attention which shares some of the features of N2pc [@moran_selective_1985;@chelazzi_neural_1993;@treue_attentional_1996]. For example, N2pc modulates in response to the number of stimuli in each hemifield, the location of the stimulus in upper or lower visual fields, and changes in task difficulty [luck_bridging_1997]. These consistencies with the suppressive mechanism observed in non-human primates led Luck and colleagues to suggest that the N2pc reflects a human correlate of this well established suppressive mechanism.

More recently, however, studies have provided evidence once again for the conception of the N2pc as an index of target selection. When a target and an irrelevant salient distractor are presented in opposite hemifields, an N2pc is elicited initially by the salient distractor and subsequently by the less salient target. It is difficult to reconcile this shifting of the N2pc from distractor to target with an N2pc which has a primary role in distractor suppression [@hickey_electrophysiological_2006]. Similar effects were found with displays consisting of sequential streams of stimuli when participants were randomly instructed to attend to targets to the left or the right stream [@dellacqua_spatial_2006]. More recently, @mazza_attention_2009 showed that an increased N2pc was, in fact, found when distractors were necessary for identifying the target and that heterogeneous distractors did not modulate N2pc amplitude even though they did negatively affect behavioral performance. The results of these studies have been argued as evidence that while distractor numerosity may play some part in producing the N2pc, it primarily indexes stimulus selection or enhancement processes.

N2pc has since been used widely as a research tool in the study of attention. Properties of the visual system itself have been investigated through the use of the N2pc, which has shown that visual search is executed by serial processing of multiple targets within a scene rather than through parallel processes [@woodman_electrophysiological_1999]. It has also been used in various lines of research to argue for example, that the right hemisphere has a processing advantage for fast sequences [@verleger_mechanisms_2011], that top-down processes are necessary for the attentional capture of target singletons [@holguin_n2pc_2009], and that color cues which are not consciously perceived and do not register behavioral effects are still capturing attention [@ansorge_goal-driven_2009]. The N2pc has been combined with other techniques to demonstrate that single-pulse transcranial magnetic stimulation to the right posterior parietal cortex affects behavioral performance through the interference of attentional selection [@fuggetta_cortico-cortical_2006]. Participants with high trait anxiety have been shown to elicit enhanced N2pc components to threatening stimuli [@fox_trait_2008], and similarly, people with blood phobia have been shown to elicit an enhanced N2pc to images of injuries [@sarlo_emotional_2011]. In both cases, this was used as evidence that these groups have early attentional biases towards these images. N2pc, therefore, offers an easily identified and reliable measure of attentional control processes involved in the selection of task-relevant stimuli on screen.

### The Ptc component.

More recent research using lateralized components in the study of attention has identified a lateralized positivity that typically occurs slightly later than the N2pc and is most commonly associated with distractor processing. @hickey_electrophysiological_2009 took advantage of one of the features of the contralateral control method to tease apart the contributions of targets and distractors to lateralized potentials. In their series of experiments, @hickey_electrophysiological_2009 presented participants with displays consisting of two objects; one of which was designated the target which participants had to respond to, while the other served as a distractor. A crucial feature of the contralateral control method is that activity which is equal in both hemispheres will be subtracted to zero. Therefore, if an object is on the midline in @hickey_electrophysiological_2009 displays, activity related to that object will be equal in both hemispheres and its contribution to the final lateralized potentials will be zero. By including trials where a distractor was lateralized from a target on the midline and trials where a target was lateralized from a distractor on the midline, they were able to isolate activity related to each of these objects individually. Their results showed an increased negativity contralateral to targets which peaked at approximately 200ms post-stimulus, as well as an increased positivity contralateral to distractors which peaked at approximately 240ms post-stimulus. They named these components the target negativity (Nt) and the distractor positivity (Pd) which, when summed together produced an N2pc-like potential.

An electrophysiological study of salient singletons provided further evidence for a distractor-related positivity that is distinct from a target-related negativity. @sawaki2010capture instructed participants to search for a target within a specific region which sometimes included distractors. The distractors could be similar to the target or have increased bottom-up salience. An N2pc was observed in response to targets and target-similar distractors in the attended region but not the unattended region. An increased positivity peaking around 200ms post-stimulus presentation was elicited by salient distractors regardless of whether or not they were in the attended region. This was interpreted as showing that the salient objects produced attention-grabbing bottom-up signals which are actively suppressed by the Pd when they are task-irrelevant. In both of these investigations of the Nt and Pd, scalp topographies of the voltages indicated that both components had their maximal voltage at the same lateral occipitotemporal sites.

A similar or possibly identical component was independently identified by @hilimire_competitive_2009 and has since been referred to as the Ptc. The Ptc was first described in a study where the target-decoy paradigm was being used to investigate the effects of spatial competition on the amplitude of the N2pc. In their version of the target-decoy paradigm, @hilimire_competitive_2009 randomized the color of the target and decoy on each trial such that both the target and distractor could be green or orange, but they could never be the same color on a given trial. This ensured that participants first had to discern which of the colored objects was the target, before reporting its orientation. They also randomly varied the distance between the target and the decoy to be 2$^\circ$, 6$^\circ$, or 10$^\circ$ of visual angle on each trial. This manipulation was based on previous experiments demonstrating a phenomenon called localized attentional interference, where objects which are closer together result in increased competition for attentional resources and therefore elicit slower responses and increased error rates. By recreating this effect with the target-decoy paradigm, @hilimire_competitive_2009 were able to control for variables which would otherwise confound the contralateral control method and investigate the effects of localized attentional interference on lateralized potentials. The results showed a modulation of the N2pc as a consequence of spatial competition, where N2pc amplitude decreased as targets and distractors moved closer together. A second unexpected result, however, was the observation of an increased positivity following the N2pc which also appeared to be modulated by competition and increased in amplitude as targets and distractors moved closer together. This component was named the Ptc because it was a positivity, temporal in scalp distribution to the N2pc, and contralateral to attended items. The Ptc appeared to be distinct from the Pd due to its different latency and scalp topography.

Initially, it was unclear precisely what process the Ptc might be reflecting. However, given that it appeared immediately following the N2pc, @hilimire_competitive_2009 suggested it may reflect the individuation or isolation of a target after the N2pc related process has identified it. It was also possible at this point that the Ptc modulations were nothing more than a result of the N2pc extending into the time range of this positive component such that the increasing Ptc was merely the result of the decreased negativity of the N2pc [@hilimire_competitive_2009;@hilimire_event-related_2010]. Manipulation of salience and task requirements in the target-decoy paradigm used to discover Ptc has achieved partial dissociation of these components [@hilimire_event-related_2010]. The results of these manipulations showed that in some conditions it was possible to elicit modulations of the N2pc without subsequent modulation of the Ptc - therefore ruling out the possibility that the Ptc reflected late N2pc activity and instead providing evidence that it reflects a subsequent process necessary for target individuation. 

@hilimire_dynamics_2011 carried out a follow up study which took advantage of the same aspect of the contralateral control method that @hickey_electrophysiological_2009 had used to dissociate Nt and Pd. Utilizing the same target-decoy displays, @hilimire_dynamics_2011 this time included conditions in which one of either the target or distractor was placed on the midline while the other was lateralized. The target-decoy paradigm used in this experiment allowed for the measurement of the N2pc and Ptc in displays with multiple objects that were equal in luminance, shape, and color. Their results showed that both targets and distractors elicit an N2pc indicating, as hypothesized, that both objects captured attention initially. Only distractors, however, elicit a Ptc suggesting that it reflects a mechanism of suppression which allows the distractor to be ignored, aiding in the isolation of the target.

### The SPCN component.

The final process critical for successful visual search is visual short-term memory (VSTM) which allows for the short-term maintenance of target features which are required for making a response. Experiments involved in the study of the N2pc have also provided evidence for an electrophysiological analogue of VSTM [@cowan2000processing;@marois2005capacity]. Sustained negativities contralateral to stimuli passing through VSTM have been identified in a range of studies and have been referred to as the contralateral negative slow wave [@klaver1999event], contralateral delayed activity [@vogel_neural_2004], and sustained posterior contralateral negativity (SPCN) [@luck1993attention;@robitaille2006fundamental]. While there are variations in the details of these different components, it is possible that these differences are due to differences in high-level task demands and low-level stimulus properties, and therefore throughout this thesis, we will refer to all sustained lateralized negativities at posterior electrodes after the N2pc time range as SPCN.

The SPCN is often observed in experiments which require a visual search for target objects, followed by further processing and storage of target features. In the previously mentioned experiment by @dellacqua_spatial_2006 where the N2pc was related to the shift of attention towards targets, subjects were presented with two sequential sets of stimuli. One or both of the sets required attention, and in some instances, one or both of the stimuli also required maintenance of target characteristics. In their experiment, an SPCN was observed following the N2pc contralateral to attended targets, and both components were suppressed when the preceding stimulus had been stored in short-term memory. @kiss2008n2pc recorded an SPCN in a visual search task with displays consisting of cued circular arrays. They found that the SPCN was suppressed along with the N2pc when a target was absent from the search array. While these experiments are primarily related to visual search, the nature of the tasks also require the use of VSTM to hold the target object in memory, extract relevant information about its features, and subsequently inform the participant's response [@jolicoeur_dissociation_2008]. These results have been used to argue that the SPCN indexes this maintenance process, however, these experiments are not direct tests of VSTM.

A stronger link between the SPCN and VSTM processing comes from experiments specifically designed to investigate VSTM. @klaver1999event used bilateral displays of polygons to test the contribution of VSTM processing to lateralized ERPs. One of the objects, as indicated by a cue, had to be maintained in VSTM for 1500ms before participants were tested on its attributes. The presence of an SPCN contralateral to the remembered object during both the encoding and retrieval phases was used as direct evidence that it indexes memory processing. @vogel_neural_2004 used arrays of briefly presented colored squares in the left and right visual field to test similar effects. Once again participants were cued as to which side of the display they should retain in memory and after a delay, they were shown a test display and had to indicate whether the two displays matched. In agreement with the findings of @klaver1999event, @vogel_neural_2004 observed an SPCN throughout the maintenance period and more importantly, demonstrated that the SPCN increases in amplitude as the number of remembered stimuli increases, but only up to its estimated capacity limit. The finding that SPCN is modulated by changes in the number of stimuli maintained in VSTM has since been replicated and extended to rule out the possibilities that SPCN reflects either general task difficulty or the spatial distribution of an attentional spotlight [@mccollough2007electrophysiological].

These results provide direct evidence for the involvement of the SPCN in VSTM and support the suggestion that its presence in visual search paradigms is a result of the use of VSTM as an intermediate processing buffer. @jolicoeur_dissociation_2008 wanted to establish that the SPCN observed in direct measures of VSTM was the same as that seen in traditional search tasks, as well as functionally dissociate the N2pc from the SPCN within the same experiment. To achieve this, participants were presented with bilateral displays consisting of 4 digits (2 in the LVF and 2 in the RVF) and had to identify and respond to the object of a specified color. Participants, therefore, had to search for the appropriate item before responding, and on half of the trials, they were required to encode both objects in the visual field of the target object. The results showed that requiring individuals to encode multiple objects led to an increase in the amplitude of the SPCN, and that memory load did not modulate the N2pc. This demonstrates that the SPCN in visual tasks is likely the same component as the SPCN in memory tasks and that it serves a distinct functional role from the N2pc.

## Current Objectives

Given the current controversy over the relationship between working memory and selective attention, the main goal of this thesis is to explore the details of this relationship and specify the attentional processes involved in this interaction. Selective attention is comprised of many separate but related sub-processes and the relationship it has to working memory could be the result of working memory's effect on any one of those sub-processes. While previous research has successfully demonstrated the presence of a relationship between attention and working memory, evidence has diverged when attempting to explicate the specific attentional mechanisms involved.

\textit{Study One} uses a standard change detection task to measure accuracy, capacity, sensitivity, and response bias while the number of irrelevant distractors was manipulated. This allows for a systematic evaluation of the role that irrelevant objects can play in performance of the change detection paradigm. To this end, we used a blocked design which allowed us to look at both the trial-by-trial effects of changing distractor number, as well as at inter-block differences in the distractor context. We had two main goals for this study, first, this experiment would itself provide some understanding of the relationship between attention and working memory by focusing on individual differences in working memory capacity and performance under varying distractor contexts. Second, the systematic manipulation used in \textit{Study One} also allowed us to test various parameters of the change detection task, and therefore informed the design of the paradigms used in \textit{Studies Two and Three}. 

\textit{Study Two} investigates the effect that increased working memory load has on selective attention, and measures lateralized ERP components which index distinct cognitive mechanisms underlying visual search. This allows for specification of the relationship between working memory load and attention to a degree that we currently lack. 

\textit{Study Three} uses a similar approach to \textit{Study Two} to investigate the effect that working memory filtering has on selective attention, again using lateralized ERP components to specify the attentional mechanism that is affected, this time, by working memory filtering. Whereas the change detection task in \textit{Study Two} kept the number of items on screen fixed while varying how much of that information should be encoded, \textit{Study Three} kept the amount of to-be-encoded information fixed while varying the number of items on screen. \textit{Study Three} therefore focusses on the effect that working memory distractors have on subsequent performance of visual search tasks. This acts both as a control for \textit{Study Two}, while again using EEG measures of attention to specify another part of the relationship between working memory and attention, namely the effect of working memory filtering demands on attention.

