
# Introduction

For most of our daily lives our senses are bombarded with vast amounts of information. Even the most mundane tasks like grocery shopping can involve encountering thousands of objects, people, and sounds. Successfully completing even small short-term goals like finding a specific flavoured ice cream involves holding information in mind while we sift through the near unlimited amount of information available in the environment. The images we hold in memory inform those objects that capture our attention. We might recall a specific colour from the packaging and filter information based on whether it matches that colour, or we might remember its general location and select information from that area. At the same time, the information we receive from the environment updates what we have stored in memory. We store the prices, and sizes of the objects we have encountered and use this information to mentally compare across brands. Successful performance in everyday situations depends on the effortless execution of a continual back and forth between these complex processes, and in this very real-world sense, the processes of selective attention and short-term memory are functionally linked.           

Since the beginning of experimental psychology in the late 19th century, the study of human cognition has been parcellated into a set of distinct, fundamental constructs. Typically, these distinctions have been made based on the intuitions of foundational thinkers in psychology, and in his seminal work \textit{The Principles of Psychology}, William James recapitulated one such historic distinction between the constructs of attention and memory [@james_1890]. Throughout the course of the 20th century, conceptions of attention and memory were specified, and formalized. The performance of selective attention encompasses a set of underlying distinctions like overt versus covert orienting, and endogenous versus exogenous attention. Similarly, the concept of memory was separated into specialized processes like short-term versus long-term memory, and semantic versus episodic memory. These processes have in turn been parcellated into even more specific functional units such that the deployment of endogenous, covert attention for example, is dependent on fundamental neural processes like target selection, and distractor suppression.

Recently, empirical work has started to show that the fundamental units necessary for the optimal functioning of selective attention may be related to, or shared by, the fundamental units necessary for the maintenance of objects in short-term memory. Modern models of short-term memory, or working memory as it has come to be known, typically depend on a system of executive control. Executive control determines the set of information that gains access to those limited resources that are involved in storing and processing information in the short term. The role of this executive control system has a lot of conceptual overlap with the role that selective attention plays more broadly in information processing in the human brain. Modern approaches in experimental psychology and cognitive neuroscience are now beginning to unify these traditionally disparate constructs and specify the nature of their interaction.

While historically, progress in experimental psychology has been based on measures of behaviour, a range of non-invasive techniques now exist which allow for the measurement of brain activity in awake humans. One of the most popular techniques for recording neural activity is electroencephalography (EEG) which allows for the direct measurement of neural activity at the time scale of actual neural processing. Methods of EEG data analysis have matured to the point where modern work has started to rely on direct measures of neural activity to make nuanced distinctions between processes that are invisible to behavioural measures. The event-related potential (ERP) technique is one such method of EEG processing which has gained wide adoption and can provide reliable, and dissociable measures of fundamental neural processes like target selection and distractor suppression.

The aim of this thesis is to expand our understanding of the relationship between working memory and selective attention, and to specify the neural mechanisms that may be shared by these two seemingly disparate systems. In study one, we used a behavioural task to perform a systematic analysis of the effect that irrelevant objects have on performance in the change-detection task. The change-detection task is a popular way of measuring visual working memory capacity however there are a number of subtle variations in the way it has been used and the effect of these variations on capacity measures is undetermined. Study one sought to fill this gap in the literature. Studies two and three aimed to follow up two of the benchmark effects established by study one while using EEG to simultaneously measure neural indices of attentional control. In study two we were interested in seeing the effect that increased working memory load can have on neural measures of target selection, and distractor suppression. In study three, our aim was to understand how the effect of irrelevant objects in a change detection task effect neural indices of target selection and distractor suppression.

# Working Memory

Dedicated study of the concept of memory in western thought goes back at least as far as Aristotle [@burnham1888memory], however systematic study of the short-term retention of information began in earnest with investigations into short-term memory span originally published in 1885 by Hermann Ebbinghaus [-@ebbinghaus2013memory]. Working memory is a relatively new term coined by  Miller, Galanter, and Pribram, (1960) which has largely supplanted the concept of short-term memory to define a cognitive system which temporarily stores information for the purposes of active processing and manipulation. The dominant model of working memory which survives to this day (albeit with revisions) was originally proposed by Baddeley and Hitch in 1974 aand has placed working memory at the centre of perception, memory, and action. A large body of empirical work has accumulated to show the important role that working plays in diverse areas of cognitive functioning, and as a result, methods for the measurement and understanding of working memory have become increasingly important.

## Short-term memory
MEASURES OF SHORT-TERM MEMORY: A HISTORICAL REVIEW
John T.E. Richardson

## Miller coining term and magical numbers
## Baddeley Model
WORKING MEMORY: LOOKING BACK AND LOOKING FORWARD
Alan Baddeley
## Working memory and its role in other abilities
## The measurement of capacity
There's a lot of variation in working memory capacity between individuals and this can be measured by each of these tasks. In OSPAN  etc... blah blah, in nback ... in sternberg... in change detection ..
Can't train it, says William james and modern stuff (not really relevant)
Working Memory Updating and Binding Training: Bayesian Evidence Supporting the Absence of Transfer - JEP:G
## Neuroanatomy of working memory/neural measures of working memory (kinda irrelevant)
# Selective attention
```{r notesText} 
#Main goal of this section should be to determine what abilities underlie successful performance of selective attention. End up talking about the dual importance of selecting relevant information and suppressing irrelevant information. Then discuss neural measures of these things.

#https://www.researchgate.net/post/Estimates_of_quantified_human_sensory_system_throughput10

#\begin{quote}
#"Everyone knows what attention is. It is the taking possession by the mind, in clear and vivid form, of one out of what seem several simultaneously possible objects or trains of thought. Focalization, concentration, of consciousness are of its essence. It implies withdrawal from some things in order to deal effectively with others, and is a conditions which has a real opposite in the confused, dazed, scattered state which in French is called distraction, and Zerstreutheit in German."
#\end{quote} - William James
```
## Sub-processes of attention
## Neural measures of attention.

# The relationship between working memory and attention
```{r copiedTextFromSAWMDistIntro}
#Everyday situations such as grocery shopping and driving depend on our ability to both efficiently allocate attention to relevant objects while suppressing distraction, as well as maintain and retrieve information from working memory. Although research over the past decade has demonstrated significant functional overlap between attention and working memory, the multifaceted nature of the relationship between these two constructs is not well understood [@fougnie_relationship_2008;@de_fockert_beyond_2013]. Converging evidence suggests that when load on a concurrent working memory task is increased, performance on an attention task is subject to increased interference from irrelevant distractors [@ahmed_focusing_2012;@de_fockert_role_2001;@stins_role_2004]. There is also evidence that individuals low in working memory capacity show greater interference on a standard Stroop task [@kane_working-memory_2003], as well as greater interference on an Eriksen flanker task [@shipstead_working_2012]. Taken together, these findings suggest that the relationship between selective attention and working memory may be better framed in terms of working memory availability. From this perspective, increasing the working memory load on an individual would lead to a decrease in their working memory availability. What's more, individuals with low working memory capacity would have less overall available working memory (see @de_fockert_beyond_2013 for a review).

#Contemporary accounts of working memory availability now typically incorporate attentional control either as an important contributor to working memory capacity[@kane_controlled-attention_2001; @shipstead_mechanisms_2014], or in some cases as the primary determinant of working memory capacity [@engle_working_2018]. The question of why working memory availability is important for selective attention remains unanswered. The aim of this research was to specify the relationship between selective attention and working memory by recording electrophysiological indices of attentional control under varying working memory load.

#Evidence for the effects of low working memory availability on attentional interference is equivocal, and interference with any one of these processes [target selection, distractor suppression] would produce impaired behavioral performance associated with low working memory availability. Some evidence suggests that low working memory availability delays the speed with which individuals can deploy attention to relevant targets [@heitz_focusing_2007; @scalf_working_2011]. Yet, findings from other work suggests that low working memory availability may cause an increase in capture by irrelevant distractors [@fukuda_individual_2011; @vogel_neural_2005].

#A different account was proposed by @fukuda_individual_2011 in research using both psychophysical and electrophysiological measures of recovery from attentional capture in low and high capacity individuals. Findings from this work suggest that the two groups are equally prone to initial capture of attention, but availability of working memory allows more efficient disengagement from irrelevant objects after they have captured attention.
```
## The effect of attention on working memory

A major goal of the human visual system is to transform the light being received by photoreceptors on the retina, into a conscious percept which is useful for an individual's behavioural goals. Throughout this process however there are a number of stages that are limited in their processing capacity and therefore challenge the visual system's ability to optimise performance in complex visual environments. Visual short term memory is an important part of visual processing which is limited in both the rate at which it can consolidate information, and the amount of information that it can store at a given point in time (Cowan, 2000; Marois & Ivanoff, 2005). Perceptual awareness is also inherently limited with regard to the amount of information that can be consciously perceived, unfolding serially such that at any point in time only a single percept gains dominance (Chelazzi, Libera, Sani, & Santandrea, 2010; Kim & Blake, 2005). Similarly, the motor system which vision attempts to inform is fundamentally limited in the number of actions which it can perform. An individual cannot simultaneously grasp and throw with the same hand for example, and performance of one action can interfere with the performance of subsequent actions (Telford, 1931; Smith, 1969; McCann & Johnston, 1992; Pashler 1994).

It has been suggested that the processing limitations of the visual system could be the result of neuronal energy demands which remain constant at a global level but must increase drastically in local task-dependent regions, as well as being an inherent consequence of the visual system's hierarchical architecture (Herculano-Houzel, 2011; Ames, 2000; Carrasco, 2011; Beck & Kastner, 2009; Desimone & Duncan, 1995; Duncan, 2005). Selective attention allows for the flexible allocation of resources to salient, and goal relevant objects in the visual field, optimising behavioural performance in spite of these capacity limitations. The classical view of how attention and working memory interact comes from this context where attention serves as a domain general process for gating incoming information to limited capacity systems, of which working memory is one. 

### Attention modulates working memory performance

Early experimental work based on this view of attention as a gating mechanism for the contents of short-term memory was reasonably unanimous in showing that attention during encoding was critical to optimal memory performance. Typically these experiments employed a divided attention paradigm where participants performed a short term memory task along with a concurrent, secondary, attention-demanding task. The rationale for these paradigms being that if attention is required for successful performance of a process like encoding, then the division of attention during encoding should lead to impaired memory performance. Indeed multiple variations of this general method consistently confirmed that dividing attention during the encoding of memory objects lead to large impairments in memory performance, and that the size of the impairment increased as the attentional demands of the concurrent task increased [@craik_effects_1996;@baddeley_attention_1984;@anderson_effect_1974;@murdock_effects_1965]. Evidence is more equivocal for the effect of attention on memory retrieval however there do appear to be consistent instances in which attention can be shown to influence retrieval ability [@fernandes_divided_2000].

Attention has also been shown to be critical to the rehearsal of information that is being stored in working memory. This effect has been most clearly demonstrated in the maintenance of spatial information in working memory. @smyth_characteristics_1994 showed in a series of experiments that maintaining the ordered sequence of a set of locations is impaired when the retention interval is filled tasks that require shifts of attention. @awh_rehearsal_1998 expanded on this effect to show that not only did forcing unrelated shifts of attention during retention lead to working memory impairments, but that performance on the secondary task was improved when targets were presented in locations stored in working memory. These results have been used to suggest that spatial attention is used as a rehearsal mechanism for the storage of locations in working memory.

Neuroimaging techniques also confirm the central role that attention plays in the maintenance of information in working memory. When attention is deployed to objects in a given visual field, fMRI recordings from the visual cortex has shown modulation of activity in the contralateral hemisphere `r #Gratton, 1997; Heinze et al., 1994; Hillyard & Mangun, 1987; Moran & Desimone, 1984; Petersen, Corbetta, Miezin, & Shulman, 1994`. `r  #Awh, Jonides, Smith, Buxton, Frank, Love, Wong, Gmeindl 1999` took advantage of this fact in order to show that the same effect is observed during the retetntion of information in working memory. Similarly EEG has been used to record the neural response to probes presented during the retention interval of a working memory task. In line with the effect that attention has been shown to have on the neural response to visual stimuli, the neural response to probes is enhanced when the probe is presented at the location of stored information `r #Tracking the time-course of attentional involvement in spatial working memory: an event-related potential investigation.`. 

Attention appears to gate VSTM, increasing recall ability (Dudukovic, Du Brow, & Wagner, 2009), modulating the configuration of VSTM (Jiang, Olson & Chun, 2000), and maintaining information about specific features in a display, as well as information about how those features are bound into discrete objects (Johnson, Hollingworth, & Luck, 2008).

## Working memory's effect on attention
### Working memory guides attention

```{r WMGuidesAttn}
#Automatic guidance of attention from working memory David Soto1 , John Hodsoll , Pia Rotshtein and Glyn W. Humphreys
#Different states in visual working memory: when it guides attention and when it does not Christian N.L. Olivers , Judith Peters , Roos Houtkamp and Pieter R. Roelfsema
```

One of the primary ways that working memory and attention have been linked is through either implicit or explicit recognition of working memory as the store for attention-guiding templates. Visual search tasks, where participants are presented with an array of items and must identify a target within the set, are regarded as a classic example of an attention task. A prominent model of the processing involved in this task is the guided search model [@wolfe_guided_1989;@wolfe_guided_1994]. The guided search model is a two stage model where objects in the visual system are first decomposed in to a set of basic features like colour an orientation which are then bound by attention into objects. The novelty of the guided search model as opposed to earlier two stage models (like feature integration) was the addition of an abstract guiding feature representation which gates access to the attentional bottleneck, but which is itsef not a part of the processing pathway. While visual search is often considered an exclusively attention-basd task, extant models of visual search performance typically incorporate this idea of an attentional template where visual objects are temporarily stored and used to guide search. The properties of guiding templates superficially line up with the properties of working memory, and empirical evidence has since accumulated to suggest that they are one and the same.

Working memory's role in visual search has been demonstrated by looking at the interaction between working memory contents and search efficiency. Central to the development of two stage models of visual search was the observation that while in many cases visual search is inefficient, meaning that responses times slow as the number of displayed search objects increases, some experimental conditions produce efficient search in which search speed is unaffected by the number of objects on screen [@nobre_oxford_2014]. Typically efficient search occurs when the target possesses a pop-out feature, for example if the target is one colour and all of the distractors are another. The explanation for this effect in the guided search model is that the target is distinct along one a preattentive feature and therefore can be dissociated from distractors before the attentional bottleneck. Experimental evidence has since shown that the extent to which search can be efficient, at least in the case of orientation and size based pop-out, depends on having a template of the target feature stored in working memory [@hodsoll_effect_2005;@hodsoll_dissociating_2006;@hodsoll_driving_2001]. In trials where participants didn't know the orientation of an upcoming target but instead just had to identify the odd one out, the advantage of a category based pop-out disappeared.
`r #Contingent capture`
The most convincing evidence to reinforce the idea that working memory is the system used to guide attention comes from dual tasks where working memory contents are deliberately unrelated to the search task. In their study, @olivers_feature-based_2006 used a dual task paadigm where participants were required to hold a specific colour in working memroy at the start of the trial. While this colour was stored, participants performed a visual search task of a circular array in order to identify and respond to a target which was defined by a specfi shape. Crucially in their task, the search displays also contained distractor stimuli which had weither no colour, unrelated colour, or matched the colour of the information stored in working memory. Consistent with the hypothesis that the contents of wrking memroy guide attention, distractors which shared the colour of working memory contents resulted in slowed visual search responses. This is particularly compeling given that the working memroy contents were irrelevant to the visual search task and the target was defined along a completely different dimension (shape). This implies not only that the contents of working memory can be used to guide attention, but that the contents of working memory automatically guide attention even if it leads to impaired performance on the task.

Additional evidence of the effect that working memory contents have on visual search has been shown using neural measures taken during these tasks. @kumar_electrophysiological_2009 for example had participants perform a task where they stored an object in working memory (of a particular shape and colour), and while this object was stored they performed a visual search task. The visual search objects were presented on the left and right sides of the display, and each search object was presented inside a coloured shape. In half of the trials, one of these coloured shapes matched the object stored in working memory. Throughout the task @kumar_electrophysiological_2009 recorded EEG and used the recordings to extract an established electrophysiological component which indexes the shift of attention to the left and right of the display. Both their behavioural results and EEG measures showed that attention was automatically deployed to the location of objects which match the contents of working memory, in spite of the fact that these objects were not relevant to the visual search task. A similar paradigm used in conjunction with function magnetic resonance imaging (fMRI) showed that the presentation of a stored object during the visual search display leads to enhanced activity in a frontoteporal network involved in encoding the original object. This is in contrast to simple repetition of an object [@soto_dissociating_2007].

### Working memory load impairs attention

## Engle incorporating attention into working memory models
Working Memory and Executive Attention: A Revisit
Randall W. Engle
## Unnecessary storage and distractor suppression
## Working memory bechmarks and relevant attention effects
# Measuring attention with EEG
The apparent overlap in excutive control and attentiona control mechanisms leads to the current situation where we want to see whether measres of attentional control can be recorded in a working memory context and shown to be effected by working memory availability. 

Although it has been established that the appropriate allocation of attention can significantly improve performance on visual tasks to compensate for limitations in the visual system, a major goal of research in this field is to understand the neural mechanisms which facilitate the selective process. A number of models of visual selective attention have been proposed, usually relying on either target enhancement which h increases processing of the attended objects, noise reduction which suppresses irrelevant, distractor stimuli, or a combination of both (Phaf, van der Heijden & Hudson, 1990; Houghton and Tipper, 1994; Desimone & Duncan, 1995). Early models of selective attention have been based on the use of classic behavioural paradigms to establish evidence for both target processing (Carrasco, Williams, & Yeshurun, 2002; Carrasco, Ling, & Read, 2004; Ling & Carrasco, 2006) and distractor suppression (Lu & Dosher, 2000; Frings, Wentura, & Wuhr, 2012), and recent work has supplemented these paradigms with neuroimaging techniques which allow for a more direct examination of the neural processes involved. Single cell recordings in non-human primates has been able to provide support for the presence of target enhancement (Motter, 1993; Treue & Maunsell, 1999; Reynolds, Pasternak, & Desimone, 2000) and distractor suppression (Reynolds, Chelazzi, & Desimone 1999; Miller, Gochen, & Gross, 1993; Reynolds & Desimone, 2003), as has functional magnetic resonance imaging (fMRI) in humans (Gandhi, Heeger, & Boynton, 1999; Brefczynski & DeYoe, 1999; Kastner, Pinsk, De Weerd, Desimone, & Ungerleider, 1999; Kastner, De Weerd, Desimone, & Ungerleider, 1998). The high temporal resolution of EEG has allowed for detailed study of the time course of attentional processes in humans, however EEG analysis often involves traditional event related potential (ERP) techniques which are limited in their ability to attribute changes in activity to specific psychological processes.

## Alpha

Things that Katharina said

## VEP components

Electrophysiological recordings in humans have provided evidence of attention's role in enhancing the signal of an attended item. When EEG is used to calculate ERPs in the Posner cuing paradigm (Posner, 1980), valid trials (where individuals are cued and therefore attend to the location of a subsequent stimulus) correspond to increases in the amplitude of the P100 and N100 when compared to invalid trials (where the stimulus appears in a non-cued location) (Mangun & Hillyard, 1991). Luck, Hillyard, Mouloua, Woldorff, Clark, and Hawkins (1994) refined this finding and suggested that it is the amplitude of the N100 specifically which indexed enhancement of an attended stimulus. The P300 has also been shown to significantly increase in amplitude during attention demanding tasks as has the N400, a component traditionally observed in response to words (Coull, 1998). The number of studies utilising traditional ERP methods to investigate distractor representations is comparatively small. One ERP component which has been associated with distractors is the P3a which, along with the P3b, is a subcomponent of the P300. Bledowski et al. (2004) used an oddball paradigm to show that while a P3b is elicited by both targets and distractors, the P3a is exclusively elicited by distractors and localised to the precentral sulcus and anterior insula. A frontal negativity has also been observed to cumulatively activate as the number of distractors preceding a target increases (Niedeggen, Michael, & Hesselman, 2012). While these traditional measures have provided some evidence for target and distractor related activity in the human visual system, it is hard to attribute changes in the ERP activity to specific psychological processes. One of the best studied electrophysiological components which is used as an index of attentional selection is the N2pc, a lateralised component which is produced with the contralateral control method.

## Lateralized components

While frequency based measures like alpha power, and event-related components like the P3 provide neural indices of attentional processing, they typically suffer from a lack of function specificity. A procedure known as the contralateral control method has recently been applied to event-related potentials in the visual search domain yielding a set of dissociable components which appear to index the processes of target selection, distracctor suppression, and storage of target features relevant to the upcoming response. This technique is promising in providing the functional specifity we need in order to interrogate the fundamental processes shared by working memory and attention.

### The contralateral control method

The contralateral control method addresses many of the problems associated with traditional ERP measures. It allows for the isolation of activity related specifically to the experimental variables that are being manipulated and removes unrelated activity (Luck, 2005), taking advantage of the hemispheric organisation of the cortex. A well-known example of contralateral organisation is observed in the motor cortex, where preparing movements of the right hand will elicit greater activity in the left motor cortex whereas preparing movements of the left hand elicits increased activity in the right motor cortex. It is possible then, if EEG is recorded during these tasks, to use the contralateral control method of analysis to extract only that activity which is systematically related to a hand movement.

Standard EEG nets are arranged symmetrically such that each electrode on the left-hand side of the scalp, has an equivalently placed electrode on the right. This means that in the case of preparing a right handed movement, activity is recorded at equivalent scalp locations over the right and left motor cortex and when participants are preparing a left handed movement, activity is again recorded at equivalent scalp locations over the right and left motor cortex. Activity is then collapsed across conditions by averaging the contralateral activity together (left hemisphere electrodes for the right hand condition and right hemisphere electrodes in the left hand condition) and then the ipsilateral activity together (right hemisphere electrodes for the right hand condition and left hemisphere electrodes in the left hand condition). Finally, ipsilateral activity is subtracted from contralateral activity to produce the difference wave which shows only that activity which is produced contralateral to a prepared hand action (see Figure 1). At this stage all activity that is the same in both hemispheres has been removed, as well as any activity that is systematically different between hemispheres. This makes it easier to relate brain activity to underlying psychological processes because as long as appropriate experimental design is used, the only activity remaining is the activity systematically lateralised in response to manipulations of the experimental variable (Gratton, 1998). 

The visual system has a hemispheric organisation similar to the motor system such that the left visual field (LVF) projects to the right visual cortex and the right visual field (RVF) projects to the left visual cortex. Researchers have therefore been able to apply the contralateral control method to isolate lateralised activity which specifically indexes attentional processes in the visual system. There are important methodological points which must be considered in order to ensure that the activity is specifically related to processes of attention as opposed to any non-attentional activity. The major point to be considered is that the sensory energy of each visual field should be equivalent (Woodman & Luck, 2003). If attention were measured by simply having participants attend to a target which appeared in different parts of the display then the contralateral control method would result in a difference wave containing the activity related to the systematic movement of the stimulus as well as the activity related to the systematic movement of attention. While ideally the sensory stimulation should be identical in each visual field, a number of studies have demonstrated that it is sufficient to balance luminance (Hickey, Dilollo, & McDonald, 2009; Hilimire, Mounts, Parks, & Corballis, 2009; Sawaki & Luck, 2010).

Lateralised ERPs have typically been studied in visual selective attention with visual search paradigms, where participants are presented with an array of objects and must identify and respond to some feature of a target stimulus embedded within the array. Participants fixate on a central cross throughout and bilateral displays are used in order to ensure a sensory balance between visual fields. Using measurements around the onset of the visual search array and applying the contralateral control method makes it possible to identify lateralised ERPs which reflect mechanisms of selective attention. Electrophysiological studies utilising this approach have identified a number of lateralised components which appear to consistently index attentional processes and may therefore be crucial to the study of visual attention.

### The N2pc

The lateralised component which has become a focus of studies of visual selective attention is the N2pc, named after its latency and scalp distribution. It is recorded as an increased negative voltage occurring approximately 180-250ms post-stimulus presentation, around the N2 time range, at posterior scalp sites contralateral to the attended stimulus. The precise attentional mechanism which the N2pc reflects is still unclear however a full understanding of the N2pc is becoming increasingly important for researchers in a number of fields because it is being used as a tool for studying cognitive systems. N2pc-like effects were originally observed in a number of studies (Heinze, Luck, Mangun, & Hillyard, 1990; Luck, Heinze, Mangun, & Hillyard, 1990; Luck & Hillyard, 1990) but were first described as the N2pc by Luck and Hillyard (1994a). It has since been described as indexing both target selection and distractor suppression by different authors at various times and the details of its functional significance are still contentious.

Luck and Hillyard (1994a) used displays containing 8 identical bars scattered around a fixation cross. In half of the displays, one of the bars would pop-out from the rest by being different in either orientation, colour, or size and participants had to identify whether the pop-out bar possessed a predefined target attribute. Their results showed that the N2pc was significantly larger when the pop-out was a target than when a non-target pop-out appeared in the display and that despite its late latency, current source density (CSD) maps estimated its generator to be in the occipital lobe, a region associated with early visual processing. They concluded from the N2pc modulations, latency, and location estimates, that it indexes a process being applied to targets rather than non-targets, and may reflect the control of information flow in the visual system through a top-down filtering mechanism. Eimer (1996) extended this finding by showing that target attributes like form, colour, and content could affect the N2pc time range, arguing also that the presence of the N2pc when distraction is minimal indicates that it represents the identification of task-relevant stimuli.

A group of early experiments however appear to contradict this finding and instead suggest that the N2pc indexes distractor suppression. When distracting items are removed from a display, made relevant to the task at hand, or when all items in the display are made to be identical targets, an N2pc is no longer elicited (Luck & Hillyard, 1994b). Luck, Girelli, McDermott, and Ford (1997) proposed the ambiguity resolution theory as a result of this work as well as their own work comparing the N2pc to electrophysiological studies in monkeys. Single unit recordings in monkeys have provided significant evidence for the existence of a suppressive mechanism in visual attention, and the fact that N2pc modulations are consistent with monkey electrophysiology in response to changes in the number of stimuli in each hemifield, the location of the stimulus in upper or lower visual fields, and changes in task difficulty, led Luck and colleagues to suggest that the N2pc reflects a human correlate of this well established suppressive mechanism. 

More recent studies however have provided evidence once again for the conception of the N2pc as an index of target selection. When a target and an irrelevant salient distractor are presented in opposite hemifields, an N2pc is elicited initially by the salient distractor and subsequently by the less salient target. It is difficult to reconcile this shifting of the N2pc from distractor to target with an N2pc which has a primary role in distractor suppression (Hickey, McDonald, & Theeuwes, 2006). Similar effects were found with displays consisting of sequential streams of stimuli either side of fixation, when participants were randomly instructed to attend to targets in one of the two streams (Dell'Acqua, Sessa, Jolicouer, & Robitaille, 2006). More recently, Mazza, Turatto, and Caramazza (2009) used different visual displays and showed that an increased N2pc was in fact found when distractors were necessary for identifying the target, that increased proximity of distractors to the target did not modulate the amplitude of the N2pc, and that heterogenous distractors did not modulate N2pc amplitude while they did negatively effect behavioural performance. The results of these studies have been argued as evidence that while distractor numerosity may play some part in producing the N2pc, it primarily indexes target enhancement processes.

Resolving the questions surrounding the nature of the N2pc is becoming increasingly important as researchers begin to utilise it as a tool for understanding cognitive systems. Properties of the visual system itself have been investigated through the use of the N2pc, which has been used as evidence that visual search is executed by serial processing of multiple targets within a scene rather than through parallel processes (Woodman & Luck, 1999). It has also been used in various lines of research to argue for example that the right hemisphere has a processing advantage for fast sequences (Verleger, Smigasiewicz, & Moller, 2011), that top-down processes are necessary for the attentional capture of target singletons (Holguin, Doalla, Vizoso, & Cadaveira, 2009), and that colour cues which are not consciously perceived and do not register behavioural effects, are still capturing attention (Ansorge, Kiss & Eimer, 2009). The N2pc has been combined with other techniques to demonstrate that single pulse transcranial magnetic stimulation (TMS) to the right posterior parietal cortex effects behavioural performance through interference of attentional selection (Fugetta, Pavone, Walsh, Kiss, & Eimer, 2006). Participants with high trait anxiety have been shown to elicit enhanced N2pc components to threatening stimuli (Fox, Derakshan, & Shoker, 2008), and similarly people with blood phobia have been shown to elicit an enhanced N2pc to images of injuries (Buodo, Sarlo, & Munafo, 2010). In both cases this has been provided as evidence that these groups have early attentional biases towards these stimuli. A detailed understanding of the N2pc and the processes it reflects appears to be crucial for a detailed understanding of the mechanisms of selective attention and important because of its use as a tool in other areas of research. Electrophysiological studies of visual selective attention have sought to clarify the target and distractor related characteristics of the N2pc.


### Ptc/Pd

A suggestion which may resolve the discrepancies in studies of the N2pc is that the N2pc itself is actually the summation of two subcomponents which individually index target and distractor processing, named the Nt and Pd respectively. Hickey, Di Lollo, and McDonald (2009) took advantage of one of the features of the contralateral control method in order to tease apart the contributions of targets and distractors to lateralised potentials. In their series of experiments, Hickey and colleagues (2009) presented participants with displays consisting of two objects, one of which was designated the target which participants had to respond to, while the other served as a distractor. A crucial feature of the contralateral control method is that activity which is equal in both hemispheres will be subtracted to zero. If an object is on the midline in Hickey and colleagues' (2009) displays, activity related to that object will be equal in both hemispheres and therefore its contribution to the final lateralised potentials will be zero. By including trials where a distractor was lateralised from a target on the midline, and trials where a target was lateralised from a distractor on the midline, they were able to isolate activity related to each of these objects individually. Their results showed an increased negativity contralateral to targets which peaked around 200ms post-stimulus, and an increased positivity contralateral to distractors which peaked around 240ms post-stimulus. They named these components the target negativity (Nt) and the distractor positivity (Pd) which, when summed together produced an N2pc-like potential.

Further evidence for a target related negativity and distractor related positivity was provided by an electrophysiological study of salient singletons. Sawaki & Luck (2010) instructed participants to search for a target within a specific region which sometimes included distractors. The distractors could be similar to the target or have increased bottom-up salience. An N2pc was observed in relation to targets and target-similar distractors in the attended region but not the unattended region. An increased positivity peaking around 200ms post-stimulus presentation was elicited by salient distractors regardless of whether or not they were in the attended region. This was interpreted as showing that the salient objects produced a bottom-up attention grabbing signal which is actively suppressed by the Pd when it is task-irrelevant. In both of these investigations of the Nt and Pd, scalp topographies of the voltages indicated that both components had their maximal voltage at the same lateral occipitotemporal sites.

Multiple contributions to the N2pc are also consistent with earlier attempts at localising the N2pc wave. Hopf and colleagues (2000) used magnetoencephalography (MEG) to record and localise the magnetic analogue of the N2pc with a simple orientation discrimination task. Displays consisted of 24 vertical and horizontal bars randomly distributed across the display, one of which was the target colour. Participants had to indicate whether the target bar was horizontal or vertical while EEG and MEG was recorded. A number of source localisation procedures identified an early parietal source for activity between 180-200ms and a later occipito-temporal source between 220-240ms post-stimulus. Originally these two sources were presented as representing the initial orienting and subsequent focusing of attention to an object however the visual search tasks did not allow for the dissociation of target and distractor related activity and an alternative interpretation may be that they were inadvertently localising the magnetic analogues of the Nt and Pd.

A similar or possibly identical component was independently identified by Hilimire etc. (2009) and has since been referred to as the Ptc.

The Ptc was first described in a study where the target-decoy paradigm was being used to investigate the effects of spatial competition on the amplitude of the N2pc. In their version of the target-decoy paradigm, Hilimire and colleagues (2009) randomised the colour of the target and decoy on each trial such that the target could be green or orange, the distractor could be green or orange, but they could never be the same colour on a given trial. This ensured that participants first had to discern which of the coloured objects was the target, before reporting its orientation. They also randomly varied the distance between the target and the decoy to be 2°, 6°, or 10° of visual angle on each trial. Previous experiments have demonstrated a phenomenon called localised attentional interference, where objects which are closer together result in increased competition for attentional resources and therefore slower responses and increased error rates. By recreating this effect with the target-decoy paradigm, Hilimire and colleagues (2009) were able to control for variables which would otherwise confound the contralateral control method and investigate the effects of localised attentional interference on lateralised potentials. The results showed a modulation of the N2pc as a consequence of spatial competition, where N2pc amplitude decreased as targets and distractors moved closer together. A second unexpected result however was the observation of an increased positivity following the N2pc which also appeared to be modulated by completion, increasing in amplitude as targets and distractors moved closer together. This component was named the Ptc because it was a positivity, temporal in scalp distribution to the N2pc, and contralateral to attended items. The Ptc appeared to be distinct from the Pd due to its different latency and scalp topography.

Initially it was unclear exactly what process the Ptc might be reflecting and given that it appeared immediately following the N2pc, Hilimire and colleagues (2009) suggested it may reflect the individuation or isolation of a target after it has been identified by the N2pc related process. It was also possible at this point that the Ptc modulations were nothing more than a result of the N2pc extending into the time range of this positive component such that the increasing Ptc was simply the result of the decreased negativity of the N2pc (Hilimire et al. 2009; Hilimire, Mounts, Parks, & Corballis, 2010). Partial dissociation of these components was achieved through the manipulation of salience and task requirements in the same target-decoy paradigm used to discover the Ptc (Hilimire et al. 2010). The results of these manipulations showed that in some conditions it was possible to elicit modulations of the N2pc without subsequent modulation of the Ptc therefore ruling out the possibility that the Ptc reflected late N2pc activity and instead providing evidence that it reflects a subsequent process necessary for target individuation. 

Target enhancement and distractor suppression are both candidate mechanisms which would allow for the individuation of a target object. Hilimire, Parks, Mounts, and Corballis (2011) carried out a follow up study which took advantage of the same aspect of the contralateral control method that Hickey and colleagues (2009) had used to dissociate Nt and Pd. Utilising the same target decoy displays, Hilimire and colleagues (2011) this time included conditions in which one of either the target or distractor was placed on the midline while the other was lateralized. The target-decoy paradigm used in this experiment allowed for the measurement of the N2pc and Ptc in displays with multiple objects that were equal in luminance, shape, and colour, something which had not been achieved in examinations of the Nt and Pd. The results showed that an N2pc in response to both targets and distractors indicating, as hypothesized, that both objects captured attention initially. The Ptc however was only elicited contralateral to a distractor, suggesting that it reflects a mechanism of suppression which allows the distractor to be ignored, aiding in the isolation of the target. The apparent functional differences between the N2pc and Ptc, as well as the consistent difference of their scalp topographies suggest that they may reflect distinct processes with separate neural generators. These facts as well as Hopf and colleagues' (2000) finding that multiple generators may be contributing to the lateralized components in visual attention suggest that it may be possible to further dissociate target from distractor processing in the target-decoy paradigm through the use of EEG source localisation.

### SPCN

Visual short term memory is an integral part of the visual attention system that is limited in both storage capacity and encoding rates, and studies of the N2pc have also provided evidence for an electrophysiological analogue of VSTM (Cowan, 2000; Marois & Ivanoff, 2005). Sustained negativities contralateral to stimuli passing through VSTM have been identified in a range of studies and referred to as the contralateral negative slow wave (CNSW) (Klaver, Talsma, Wijers, Heinze, & Mulder, 1999), contralateral delayed activity (CDA) (Vogel & Machizawa, 2004), and sustained posterior contralateral negativity (SPCN) (Eimer 1996; Luck, Fan, & Hillyard 1993; Robitaille & Jolicoeur, 2006). While there are variations in the details of these different components, it is possible that these differences are due to differences in high level task demands and low level stimulation and therefore for the purposes of this study we will refer to all sustained negativities at posterior electrodes subsequent to the N2pc time range as SPCN.

The SPCN is often observed in experiments which require visual search for a target object, followed by further processing and/or memory for features of that target. In the previously mentioned experiment by Dell'Acqua and colleagues (2006) where the N2pc was related to the shift of attention towards targets, subjects were presented with two sequential sets of stimuli. One or both of the sets required attention, and in some instances one or both of the stimuli also required retention of target characteristics. In their experiment, an SPCN was observed following the N2pc contralateral to attended targets, and it was suppressed in the same conditions which caused a suppression of the N2pc. Kiss, Van Velzen, and Eimer (2008) recorded an SPCN in a visual search task with displays consisting of cued circular arrays. They found that the SPCN was suppressed along with the N2pc when a target was absent from the search array. While these experiments are primarily related to visual search, the nature of the tasks also require the use of VSTM to hold the target object in memory, extract relevant information about its features, and therefore inform the participant's response (Jolicoeur, Brisson, & Robitaille, 2008). It has been argued on the basis of these results that the SPCN indexes this retention process, however these experiments are not direct tests of VSTM.

A stronger link between the SPCN and VSTM processing comes from experiments specifically designed to investigate VSTM. Klaver, Talsma, Wijers, Heinze, and Mulder (1999) used bilateral displays of polygons to test the contribution of VSTM processing to lateralised ERPs. One of the objects, as indicated by a cue, had to be retained in VSTM for 1500ms before participants were tested on its attributes. The presence of an SPCN contralateral to the remembered object during both the encoding and retrieval phases was used as direct evidence that it indexes memory processing. Vogel and Machizawa (2004) used arrays of briefly presented coloured squares in the left and right visual field in order to test similar effects. Once again participants were cued as to which side of the display they should retain in memory and after a delay, they were shown a test display and had to indicate whether the two displays matched. In agreement Klaver and colleagues' (1999) findings, Vogel and Machizawa (2004) observed an SPCN throughout the retention period and more importantly, demonstrated that the SPCN increases in amplitude as the number of remembered stimuli increases, but only up to its estimated capacity limit. The finding that SPCN is modulated by changes in the number of stimuli held in VSTM has since been replicated and extended to rule out confounds (McCollough, Machizawa, & Vogel, 2007).

These results provide direct evidence for the involvement of the SPCN in VSTM and support the suggestion that its presence in visual search paradigms is a result of the use of VSTM as an intermediate processing buffer. Jolicoeur and colleagues (2008) wanted to establish that the SPCN observed in direct measures of VSTM was the same as that seen in traditional search tasks, and also functionally dissociate the N2pc from the SPCN within the same experiment. Participants were presented with bilateral displays consisting of 4 digits (2 in the LVF and 2 in the RVF) and had to encode and respond to the object of a specified colour. Participants therefore had to search for the appropriate item before responding and on half of the trials they were required to encode both objects in the visual field of the target object. The results showed that requiring individuals to encode multiple objects led to an increase in the amplitude of the SPCN and that the N2pc was not modulated by memory load in this way. This demonstrates that the SPCN in visual tasks is likely the same component as the SPCN in memory tasks and that it serves a distinct functional role from the N2pc.
