
## Introduction

For most of our daily lives our senses are bombarded with vast amounts of information. Even the most mundane tasks like grocery shopping can involve encountering thousands of objects, people, and sounds. Successfully completing even small short-term goals like finding a specific flavored ice cream involves holding information in mind while we sift through the near unlimited amount of information available in the environment. The images we hold in memory inform those objects that capture our attention. We might recall a specific color from the packaging and filter information based on whether it matches that color, or we might remember its general location and select information from that area. At the same time, the information we receive from the environment updates what we have stored in memory. We store the prices, and sizes of the objects we have encountered and use this information to mentally compare across brands. Successful performance in everyday situations depends on the effortless execution of a continual back and forth between these complex processes, and in this very real-world sense, the processes of selective attention and short-term memory are functionally linked.           

Since the beginning of experimental psychology in the late 19th century, the study of human cognition has been parcellated into a set of distinct, fundamental constructs. Typically, these distinctions have been made based on the intuitions of foundational thinkers in psychology, and in his seminal work \textit{The Principles of Psychology}, William James recapitulated one such historic distinction between the constructs of attention and memory [@james_1890]. Throughout the course of the 20th century, conceptions of attention and memory were specified, and formalized. The performance of selective attention encompasses a set of underlying distinctions like overt versus covert orienting, and endogenous versus exogenous attention. Similarly, the concept of memory was separated into specialized processes like short-term versus long-term memory, and semantic versus episodic memory. These processes have in turn been parcellated into even more specific functional units such that the deployment of endogenous, covert attention for example, is dependent on fundamental neural processes like target selection, and distractor suppression.

Recently, empirical work has started to show that the fundamental units necessary for the optimal functioning of selective attention may be related to, or shared by, the fundamental units necessary for the maintenance of objects in short-term memory. Modern models of short-term memory, or working memory as it has come to be known, typically depend on a system of executive control. Executive control determines the set of information that gains access to those limited resources that are involved in storing and processing information in the short term. The role of this executive control system has a lot of conceptual overlap with the role that selective attention plays more broadly in information processing in the human brain. Modern approaches in experimental psychology and cognitive neuroscience are now beginning to unify these traditionally disparate constructs and specify the nature of their interaction.

While historically, progress in experimental psychology has been based on measures of behavior, a range of non-invasive techniques now exist which allow for the measurement of brain activity in awake humans. One of the most popular techniques for recording neural activity is electroencephalography (EEG) which allows for the direct measurement of neural activity at the time scale of actual neural processing. Methods of EEG data analysis have matured to the point where modern work has started to rely on direct measures of neural activity to make nuanced distinctions between processes that are invisible to behavioral measures. The event-related potential (ERP) technique is one such method of EEG processing which has gained wide adoption and can provide reliable, and dissociable measures of fundamental neural processes like target selection and distractor suppression.

The aim of this thesis is to expand our understanding of the relationship between working memory and selective attention, and to specify the neural mechanisms that may be shared by these two seemingly disparate systems. In study one, we used a behavioral task to perform a systematic analysis of the effect that irrelevant objects have on performance in the change-detection task. The change-detection task is a popular way of measuring visual working memory capacity however there are a number of subtle variations in the way it has been used and the effect of these variations on capacity measures is undetermined. Study one sought to fill this gap in the literature. Studies two and three aimed to follow up two of the benchmark effects established by study one while using EEG to simultaneously measure neural indices of attentional control. In study two we were interested in seeing the effect that increased working memory load can have on neural measures of target selection, and distractor suppression. In study three, our aim was to understand how the effect of irrelevant objects in a change detection task effect neural indices of target selection and distractor suppression.

## Interactions Between Working Memory and Attention
```{r copiedTextFromSAWMDistIntro}
#Everyday situations such as grocery shopping and driving depend on our ability to both efficiently allocate attention to relevant objects while suppressing distraction, as well as maintain and retrieve information from working memory. Although research over the past decade has demonstrated significant functional overlap between attention and working memory, the multifaceted nature of the relationship between these two constructs is not well understood [@fougnie_relationship_2008;@de_fockert_beyond_2013]. Converging evidence suggests that when load on a concurrent working memory task is increased, performance on an attention task is subject to increased interference from irrelevant distractors [@ahmed_focusing_2012;@de_fockert_role_2001;@stins_role_2004]. There is also evidence that individuals low in working memory capacity show greater interference on a standard Stroop task [@kane_working-memory_2003], as well as greater interference on an Eriksen flanker task [@shipstead_working_2012]. Taken together, these findings suggest that the relationship between selective attention and working memory may be better framed in terms of working memory availability. From this perspective, increasing the working memory load on an individual would lead to a decrease in their working memory availability. What's more, individuals with low working memory capacity would have less overall available working memory (see @de_fockert_beyond_2013 for a review).

#Contemporary accounts of working memory availability now typically incorporate attentional control either as an important contributor to working memory capacity[@kane_controlled-attention_2001; @shipstead_mechanisms_2014], or in some cases as the primary determinant of working memory capacity [@engle_working_2018]. The question of why working memory availability is important for selective attention remains unanswered. The aim of this research was to specify the relationship between selective attention and working memory by recording electrophysiological indices of attentional control under varying working memory load.

#Evidence for the effects of low working memory availability on attentional interference is equivocal, and interference with any one of these processes [target selection, distractor suppression] would produce impaired behavioral performance associated with low working memory availability. Some evidence suggests that low working memory availability delays the speed with which individuals can deploy attention to relevant targets [@heitz_focusing_2007; @scalf_working_2011]. Yet, findings from other work suggests that low working memory availability may cause an increase in capture by irrelevant distractors [@fukuda_individual_2011; @vogel_neural_2005].

#A different account was proposed by @fukuda_individual_2011 in research using both psychophysical and electrophysiological measures of recovery from attentional capture in low and high capacity individuals. Findings from this work suggest that the two groups are equally prone to initial capture of attention, but availability of working memory allows more efficient disengagement from irrelevant objects after they have captured attention.
```
### The effect of attention on working memory.

A major goal of the human visual system is to transform the light being received by photoreceptors on the retina, into a conscious percept which is useful for an individual's behavioral goals. Throughout this process however there are a number of stages that are limited in their processing capacity and therefore challenge the visual system's ability to optimize performance in complex visual environments. Visual short term memory is an important part of visual processing which is limited in both the rate at which it can consolidate information, and the amount of information that it can store at a given point in time (Cowan, 2000; Marois & Ivanoff, 2005). Perceptual awareness is also inherently limited with regard to the amount of information that can be consciously perceived, unfolding serially such that at any point in time only a single percept gains dominance (Chelazzi, Libera, Sani, & Santandrea, 2010; Kim & Blake, 2005). Similarly, the motor system which vision attempts to inform is fundamentally limited in the number of actions which it can perform. An individual cannot simultaneously grasp and throw with the same hand for example, and performance of one action can interfere with the performance of subsequent actions (Telford, 1931; Smith, 1969; McCann & Johnston, 1992; Pashler 1994).

It has been suggested that the processing limitations of the visual system could be the result of neuronal energy demands which remain constant at a global level but must increase drastically in local task-dependent regions, as well as being an inherent consequence of the visual system's hierarchical architecture (Herculano-Houzel, 2011; Ames, 2000; Carrasco, 2011; Beck & Kastner, 2009; Desimone & Duncan, 1995; Duncan, 2005). Selective attention allows for the flexible allocation of resources to salient, and goal relevant objects in the visual field, optimizing behavioral performance in spite of these capacity limitations. The classical view of how attention and working memory interact comes from this context where attention serves as a domain general process for gating incoming information to limited capacity systems, of which working memory is one. The literature has since established an important role for attention in the encoding, maintenance, and retrieval of information stored in working memory. `r #Top-down modulation: bridging selective attention and working memory`

#### Attention modulates working memory performance.

`r #Alpha Power Gates Relevant Information during Working Memory Updating Peter Manza, Chui Luen Vera Hau and Hoi-Chung Leung `

Early experimental work based on the view of attention as a gating mechanism for short-term memory was reasonably unanimous in showing that attention during encoding was critical to optimal memory performance. Typically these experiments employed a divided attention paradigm where participants performed a short term memory task along with a concurrent, secondary, attention-demanding task. The rationale for these paradigms being that if attention is required for successful performance of a process like encoding, then the division of attention during encoding should lead to impaired memory performance. Indeed, multiple variations of this general method consistently confirmed that dividing attention during the encoding of memory objects lead to large impairments in memory performance, and that the size of the impairment increased as the attentional demands of the concurrent task increased [@craik_effects_1996;@baddeley_attention_1984;@anderson_effect_1974;@murdock_effects_1965]. Evidence therefore is reasonably unequivocal that attention is necessary for encoding objects into working memory, and if attention is directed elsewhere during encoding, then task relevant objects are not encoded into working memory.

`r #In addition, attention supports the transfer of perceptual information into VSTM (Averbach & Coriell, 1961; Hollingworth & Henderson, 2002; Irwin, 1992; Schmidt, Vogel, Woodman, & Luck, 2002; Sperling, 1960)`

Attention has also been shown to be critical to the rehearsal of information that is being stored in working memory. @smyth_characteristics_1994 showed in a series of experiments that maintaining the ordered sequence of a set of locations is impaired when the retention interval is filled with tasks that require shifts of attention. @awh_rehearsal_1998 expanded on this effect to show that not only did forcing unrelated shifts of attention during retention lead to working memory impairments, but that performance on the secondary task was improved when targets were presented in locations stored in working memory. These results have been used to suggest that spatial attention is used as a rehearsal mechanism for the storage of locations in working memory.

Neuroimaging techniques also confirm the central role that attention plays in the maintenance of information in working memory by using measures that were established in the attention literature. When attention is deployed to objects in a given visual field, a range of techniques including fMRI and PET have shown modulation of activity in the contralateral hemisphere of the visual cortex [@gratton_attention_1997;@heinze_combined_1994;@mangun_spatial_1987;@moran_selective_1985;@petersen_pet_1994]. @awh_rehearsal_1999 took advantage of this fact in order to show that the same effect is observed during the retention of information in working memory. Similarly EEG has been used to show that when attention is deployed to a specific location, the presentation of probes in that location will elicit larger neural responses than the presentation of probes in unattended spaces. Taking advantage of this phenomena, EEG experiments have shown that when probes are presented during the retention interval of a working memory task, the neural response to those probes is also larger when they are presented in the location of a stored object [@jha_tracking_2002;@awh_role_2000].

Evidence is more equivocal for the effect of attention on memory retrieval however there do appear to be instances in which attention can be shown to influence retrieval ability [@fernandes_divided_2000]. Studies investigating the effect of attention on short-term memory traditionally relied on the divided attention paradigm used to establish the importance of attention for encoding. Early results demonstrated that dividing attention during retrieval lead to similar impairments as dividing attention during encoding, although the size of the impairment was reduced `r #(Dywan &Jacoby, 1990; Moscovitch, 1994; Park et al., 1989),`. Other work showed no such effect of divided attention at retrieval on memory performance leading to suggestions that retrieval processes were automatic and not reliant on attention `r #(Baddeley et al., 1984; Craik et al., 1996`. @fernandes_divided_2000 proposed a resolution to these inconsistencies and used a series of experiments to conclude that dividing attention during retrieval could impact on memory performance, but only when the concurrent task was competing for access to word-specific representational systems.

The role that attention plays in retrieving information from working memory has since been investigated using neuroimaging methods. The most common method of doing this has been to record EEG while participants perform a probed working memory task. In probed memory tasks, participants encode a set of information which they maintain over a short delay, and the test display presents a probe indicating which of the encoded objects they should recall. ERP measures previously established to reflect the allocation of attention to locations in space are observed in response to the probe, indicating that attention is being used to search the contents of working memory and retrieve relevant information from the probed locations `r #Leszczyn´ ski, M. et al. (2011) Recoding between two types of STM representation revealed by the dynamics of memory search. J. Cogn. Neurosci. DOI: 10.1162/jocn_a_00102 87 Dell’Acqua, R. et al. (2010) Orienting attention to objects in visual short-term memory. Neuropsychologia 48, 419–428 88 Eimer, M. and Kiss, M. (2010) An electrophysiological measure of access to representations in visual working memory. Psychophysiology 47, 197–200`. Importantly, `r #86 Kuo, B-C. et al. (2009) Searching for targets within the spatial layout of visual short-term memory. J. Neurosci. 29, 8032–8038 ` showed that this occurs when the probe itself is presented centrally, as long as the retrieved representation was presented in a lateralized location (although see Broadway, Hilimire, Corballis 2012 for an example where this did not occur). Together, this evidence suggests that the process of retrieving information from working memory requires the allocation of attention to spatiotopically organized representations held in working memory, which is analogous to the selection of information from the external environment. `r #Rehearsal in Spatial Working Memory: Evidence From Neuroimaging` showed this with fMRI

The evience reviewed above establishes a critical role for attention in the successful operation of working memory. Attention appears to be crucial for selective encoding of relevant objects, the maintenance of those objects within working memory, as well as the retrieval of those objects for later use. This supports initial conceptions of attention as an independent cognitive system which is used to gate the limited resources of working memory. However, a separate body of literature has established a similarly critical role for working memory plays in the efficient allocation of selective attention.
`r #Attention appears to gate VSTM, increasing recall ability (Dudukovic, Du Brow, & Wagner, 2009), modulating the configuration of VSTM (Jiang, Olson & Chun, 2000), and maintaining information about specific features in a display, as well as information about how those features are bound into discrete objects (Johnson, Hollingworth, & Luck, 2008).`

### The effect of working memory on attention.

#### Working memory guides attention.

```{r WMGuidesAttn}
#Automatic guidance of attention from working memory David Soto1 , John Hodsoll , Pia Rotshtein and Glyn W. Humphreys
#Different states in visual working memory: when it guides attention and when it does not Christian N.L. Olivers , Judith Peters , Roos Houtkamp and Pieter R. Roelfsema
```

`r #Automatic and strategic effects in the guidance of attention by working memory representations Nancy B. Carlisle and Geoffrey F. Woodman`

One of the primary ways that working memory and attention have been linked is through either implicit or explicit recognition of working memory as the store for attention-guiding templates. Visual search tasks, where participants are presented with an array of items and must identify a target within the set, are regarded as a classic example of an attention task. A prominent model of the processing involved in this task is the guided search model [@wolfe_guided_1989;@wolfe_guided_1994]. The guided search model is a two stage model where objects in the visual system are first decomposed in to a set of basic features like color and orientation which are then bound by attention into objects. The novelty of the guided search model as opposed to earlier two stage models (like feature integration) was the addition of an abstract guiding feature representation which gates access to the attentional bottleneck, but which is itself not a part of the processing pathway. While visual search is often considered an exclusively attention-based task, extant models of visual search performance typically incorporate this idea of an attentional template where visual objects are temporarily stored and used to guide search. The properties of guiding templates superficially line up with the properties of working memory, and empirical evidence has since accumulated to suggest that they are one and the same.

Working memory's role in visual search has been demonstrated by looking at the interaction between working memory contents and search efficiency. Central to the development of two stage models of visual search was the observation that while in many cases visual search is inefficient, meaning that responses times slow as the number of displayed search objects increases, some experimental conditions produce efficient search in which search speed is unaffected by the number of objects on screen [@nobre_oxford_2014]. Typically efficient search occurs when the target possesses a pop-out feature, for example if the target is one color and all of the distractors are another. The explanation for this effect in the guided search model is that the target is distinct along a preattentive feature and therefore can be dissociated from distractors before the attentional bottleneck. Experimental evidence has since shown that the extent to which search can be efficient, at least in the case of orientation and size based pop-out, depends on having a template of the target feature stored in working memory [@hodsoll_effect_2005;@hodsoll_dissociating_2006;@hodsoll_driving_2001]. In trials where participants didn't know the orientation of an upcoming target but instead just had to identify the odd one out, the advantage of a category based pop-out disappeared.
`r #Contingent capture`
The most convincing evidence to reinforce the idea that working memory is the system used to guide attention comes from dual tasks where working memory contents are deliberately unrelated to the search task. In their study, @olivers_feature-based_2006 used a dual task paradigm where participants were required to hold a specific color in working memory at the start of the trial. While this color was stored, participants performed a visual search task of a circular array in order to identify and respond to a target which was defined by a specifc shape. Crucially in their task, the search displays also contained distractor stimuli which had either no color, unrelated color, or matched the color of the information stored in working memory. Consistent with the hypothesis that the contents of working memory guide attention, distractors which shared the color of working memory contents resulted in slowed visual search responses. This is particularly compelling given that the working memory contents were irrelevant to the visual search task and the target was defined along a completely different dimension (shape). This implies not only that the contents of working memory can be used to guide attention, but that the contents of working memory automatically guide attention even if it leads to impaired performance on the task.

Additional evidence of the effect that working memory contents have on visual search has been shown using neural measures taken during these tasks. @kumar_electrophysiological_2009 for example had participants perform a task where they stored an object in working memory (of a particular shape and color), and while this object was stored they performed a visual search task. The visual search objects were presented on the left and right sides of the display, and each search object was presented inside a colored shape. In half of the trials, one of these colored shapes matched the object stored in working memory. Throughout the task @kumar_electrophysiological_2009 recorded EEG and used the recordings to extract an electrophysiological component which indexes the shift of attention to the left and right of the display. Both their behavioral results and EEG measures showed that attention was automatically deployed to the location of objects which match the contents of working memory, in spite of the fact that these objects were not relevant to the visual search task. A similar paradigm used in conjunction with function magnetic resonance imaging (fMRI) showed that the presentation of a stored object during the visual search display leads to enhanced activity in a frontotemporal network involved in encoding the original object. This is in contrast to simple repetition of an object [@soto_dissociating_2007].

#### Working memory availability modulates attention.

##### Evidence from within-subject manipulation of working memory load.

The critical role that working memory plays in successful deployment of attention is also demonstrated by the observation that the amount of working memory resources available to an individual has significant effects on their ability to perform attention-based tasks @de_fockert_beyond_2013. Evidence for this fact comes from converging approaches, the first of which focuses on within-subject comparisons where concurrent working memory load is manipulated while participants perform the attention-based task. An early example of this approach used a dual task where participants encoded a set of numbers at the start of the trial, and during the maintenance period were shown pictures of famous faces with names of famous people attached [@de_fockert_role_2001]. In half of these trials the face would match the name, and in the other half the face and name would be incongruent. Participants were required to respond to the names while ignoring the faces and their results showed that if load on the concurrent working memory task was increased, participants performed worse on the incongruent trials suggesting they struggled to ignore the irrelevant faces.

This pattern of results has been replicated with a range of interference effects that are measurable in classic attention tasks. A seminal interference effect is the stroop effect where participants are required to read aloud a list of color names printed in colored ink. Interference in this task occurs when the color name that the participant is reading has been printed in an incongruent ink color, for example the word red printed in green [@stroop_studies_1935]. If participants perform a concurrent working memory task, the size of this interference effect is significantly increased in higher working memory load conditions [@stins_role_2004]. Similarly, performance on the eriksen flanker task [@eriksen_effects_1974] where participants respond to a central stimulus which is flanked by either congruent or incongruent stimuli, interacts with concurrent working memory load. In this paradigm the response time difference between the congruent and incongruent trials is believed to index the extent to which participants are able to focus on the central target and suppress the effect of the irrelevant flankers. The concurrent retention of six digits in working memory results in larger interference effects by the flankers than concurrent retention of only one digit [@de_fockert_no_2010;@lavie_load_2004;@ahmed_focusing_2012]. In all of these paradigms, distractor presence is perfectly predictable and congruent in half of the trials making them potentially task relevant. This evidence would limit our interpretation of the role that working memory has in attention to the active suppression of predictable, relevant distractors.

However, the effect of working memory load on interference has also been established in paradigms where distractor presence is unpredictable and completely irrelevant to the task. For example, when participants are required to search for a specifically shaped target, the presence of a uniquely colored distractor causes performance impairments that are believed to result from the extent to which the salient distractor captures their attention [@theeuwes_perceptual_1992]. When paired with a concurrent working memory task, high working memory results in larger interference from these distractors even though the distractor is present in only some trials and is defined along a task irrelevant dimension [@boot_attention_2005;@lavie_role_2005;@lavie_frontal_2006]. Working memory load has also been shown to mediate the effect of inattentional blindness, a phenomenon where the performance of perceptually demanding tasks can result in unexpected stimuli going unnoticed. Most famously, inattentional blindness was demonstrated when participants attempting to count basketball passes often missed the appearance of a person dressed in a gorilla costume walking through the scene [@simons_gorillas_1999]. This effect can be eliminated however by the concurrent maintenance of information in working memory, meaning that participants are much more likely to report seeing the unexpected stimulus when working memory load is high. 

A small body of neuroimaging evidence has also accumulated to provide indirect but converging evidence for the effect of working memory load on attention. @de_fockert_role_2001 showed in their study that while participants categorized famous names, the increased interference by irrelevant famous faces caused by increased working memory load also coincides with increased face related processing in the visual cortex. Activity in frontal areas associated with working memory have also been associated with the size of interference effects in attention tasks [@fockert_neural_2004], and more significantly, activity in the right prefrontal cortex is correlated with interference effects but only when concurrent working memory load is high [@de_fockert_role_2012]. The pervasiveness of these effect has been demonstrated by @kelley_working_2010 who used fMRI to show that the relationship between working memory and distractor interference is observable down to the level of the primary visual cortex. These data along with the body of behavioral work suggest that working memory is essential for the optimal performance of selective attention and when an individual is put under increased working memory load, their attentional processing is impaired.

##### Evidence from individual differences in working memory capacity.

The second main approach that has been used to demonstrate the importance of working memory to selective attention is a between-subject approach where the natural variation in working memory capacity is associated with performance on attention-based tasks. It is well known that while the average person's working memory is able to store approximately three to four pieces of information [@alvarez_capacity_2004;@awh_visual_2007;@davis_capacity_2005;@pashler_familiarity_1988;@sperling_information_1960;@xu_dissociable_2006], this number can vary significantly across individuals [@awh_visual_2007a;@rouder_assessment_2008]. The rationale for relating this to selective attention is that if some individuals have a measurably smaller working memory capacity than others, and working memory is critical for selective attention, then those same individuals will perform worse on tests of attention. Indeed there appears to be reliable effects of working memory capacity on performance on many of the attention tasks used in the within-subject designs described earlier.

Individual working memory is associated with interference effects derived from tasks like the stroop task and Eriksen flanker task. @kane_working-memory_2003 carried out a series of experiments where working memory capacity was measured using the operation span task, and performance on the stroop task was compared between individuals with high versus low working memory capacity. Their results consistently show that individuals with a high working memory capacity incur significantly less interference in the stroop task than individuals with low working memory capacity. In their task, @kane_working-memory_2003 also manipulated the number of congruent trials within the task with the expectation that when the number of incongruent trials was low, some individuals would stop maintaining the task goals and therefore take larger interference penalties from the rare incongruent trials. The results showed that high working memory capacity participants were better at not just competition resolution in the stroop task, but also goal maintenance and they therefore elicited smaller interference effects in all situations. Similarly, interference measured using the Eriksen-type flanker tasks is significantly smaller for high capacity individuals [@shipstead_working_2012].

A more nuanced measure of this relationship was established by @kane_controlled-attention_2001 using both prosaccade and antisaccade tasks in order to tease out the effect of capacity on reflexive orienting. In the prosaccade task, a salient cue appears on screen indicating that an upcoming target will appear in its location. In this case the abrupt onset of the cue attracts attention and participant performance benefits from that allocation of attention. In the antisaccade task however, when the cue appears, it indicates that the upcoming target will be located on the opposite side of the screen. In this case, optimal performance on the task is achieved by either efficiently recovering from attentional capture by the cue, or by preventing capture in the first place. The data show that individuals with a high working memory capacity outperform individuals with a low working memory capacity in the antisaccade task but not the prosaccade task. This indicates that the benefit of working memory capacity lies in suppression of, or disengagement from the onset of salient visual objects. They also show that this effect remains even when participants get to practice the task across ten blocks [@kane_controlled-attention_2001].

The role that working memory capacity plays in selective attention has also been demonstrated in the auditory domain. @conway_cocktail_2001 investigated the cocktail party effect and its relationship to working memory capacity in a task where participants listened to two auditory messages simultaneously. The classic cocktail party effect is that while participants are asked to attend to one of the messages, a portion of them will report hearing their name in the irrelevant auditory stream even though it is never there. @conway_cocktail_2001 managed to replicate this general effect and show that those individuals who reported hearing their name in the irrelevant message, also tended to have a lower working memory capacity. They used this as evidence that low capacity individuals are struggling to suppress the irrelevant stream of information.

Similar effects of capacity on distraction have been demonstrated to occur across sensory domains. When participants perform a simple visual task categorizing sets of arrows as pointing either left or right, their performance is impaired by the onset of an auditory oddball presented just before the arrows are shown [@sorqvist_working_2012]. This interference effect is relatively large at the start of the experiment and attenuates toward the end of the experiment, presumably this is the result of participants anticipating oddball onset as the experiment goes on and engaging preparatory distractor suppression. Notably, working memory capacity was related to the size of the interference effect at the end of the experiment but not at the start of the experiment [@sorqvist_working_2012]. This cross-domain evidence suggests that working memory capacity is related to the engagement of attentional control mechanisms caused by the expectation of distraction and not necessarily related to a ubiquitous advantage in distractor disengagement. `r # at some point reference Tsuchida et al., 2012 who used EEG with this to show that the N1 to the oddball is smaller for high WM Ss`

`r ## Engle incorporating attention into working memory models: Working Memory and Executive Attention: A Revisit Randall W. Engle `
`r ## Unnecessary storage and distractor suppression`
`r ## Working memory benchmarks and relevant attention effects`

## Specifying the Relationship Between Working Memory and Attention

While the classic view of working memory and attention was that attention operated as a domain general system which gated access to limited capacity systems like working memory, the evidence reviewed above has established the central role that working memory plays in the efficient operation of attention. While this is largely consistent with the view that working memory and attention are two independent but interacting systems, recent research has started to question whether working memory and attention are truly distinct processes, and examine the extent to which they may share overlapping neural resources. Contemporary accounts of working memory availability now typically incorporate attentional control either as an important contributor to working memory capacity [@kane_controlled-attention_2001;@shipstead_mechanisms_2014], or in some cases as the primary determinant of working memory capacity [@engle_working_2018].

In their work comparing the effect of capacity on prosaccade and antisaccade performance, @kane_controlled-attention_2001 concluded for example that working memory capacity reflects a basic attentional control capability. The antisaccade task, requiring prevention or disengagment of attention from a cue, doesn't seem to share any of the processes required to store items in working memory. The fact that workng memory capacity is associated with performance on the antisaccade task but not the prosaccade version is therefore motivation for the hypothesis that working memory reflects attentional control. A candidate neural substrate for this interaction is the dorsolateral prefrontal cortex (dPFC) which has been established to play a role in both attention [@jagtap_effective_2016;@knight_role_1995] and working memory [@engle1999individual]. Crucially, dPFC has also been implicated in distinguishing between performance on the antisaccade and prosacade tasks. Patients with dPFC damage show deficits on the antisaccade but not prosaccade task [@fukushima_voluntary_1994;@guitton_frontal_1985;@pierrot-deseilligny_cortical_1991], and neuroimaging has shown increased dPFC activation during antisaccade trials [@sweeney_positron_1996]. The fact that this same difference is related to working memory capacity suggests executive control processes performed by the dPFC may therefore be an example of neural resources shared by working memory and selective attention.

This idea was elaborated on by @shipstead_mechanisms_2014 using a large number of tasks in order to tease apart the contribution of primary memory, secondary memory, and attentional control to performance on working memory tasks. In their study working memory was measured with variations of three main working memory paradigms, while a range of other tasks were used to measure primary memory, secondary memory, and attentional control. Structural equation modeling showed that while the strength of the relationships vary depending on which task you use to measure working memory, in all cases attentional control is a critical component of working memory performance. this is true not only of working memory tasks which explicitly include a secondary processing task which taxes attentional control, but also of working memory tasks which require the storage and retrieval of a set of simple visual objects in the absence of distraction.

Consensus is now building in favour of the general view that working memory and selective attention overlap in their roles in cognition, and research is attempting to specify the attentional process or processes that are related to working memory performance. Optimal performance of selective attention relies on several underlying processes including; target identification and selection, proactive suppression of possible distractors, and efficient disengagement from irrelevant distractors that capture attention [@carrasco_visual_2011]. Evidence for the effects of low working memory availability on attentional interference is equivocal, and interference with any one of these processes would produce impaired behavioral performance associated with low working memory availability. The focus on filtering and interference effects have led many to suggest that working memory is essential for distractor suppression [@fukuda_individual_2011;@vogel_neural_2005] while other accounts have suggested that working memory is principally involved in the maintenance of target information [@engle2018working;@heitz_focusing_2007;@scalf_working_2011]. This issue has come to occupy a central role in the attention and working memory literature and a range of evidence has attempted to support the role of these distinct but interrelated attentional subprocesses.

### Target selection.

One critical function required in order to perform effectively in a goal directed task is the identification and selection of relevant targets. Target selection is essential to the successful performance of selective attention at all levels, from the overt oriting of the head and eyes to place relevant objects onto the fovea, to covert orienting of neural resources which increase the processing of target representations in the cortex [@carrasco_visual_2011]. When investigating the overlap between working memory and attention therefore, a number of researchers have focussed on the process of target selection and its overlapping role in the use of these two cognitive constructs.

@scalf_working_2011 paired fMRI with a dual task in order to suggest that working memory load affects the speed with which individuals can deploy attention to relevant targets. In their task, participants were presented with a target set of symbols (T1) and attempted to store their identity and location. After a short delay a letter (T2) was shown on screen and after further delay participants were tested on their storage of T1. In some trials, participants were instructed to ignore T2, and in the other trials they were required to report the letter's identity. fMRI revealed a delayed response to T2 in the visual cortex when it followed T1 at a short delay, and when the encoding demands of T1 were high. @scalf_working_2011 interpreted this as evidence that increased working memory demands lead to a delay in processes of target selection as a result of their concurrent use in the working memory task.

Systematic manipulation of the Eriksen flanker task has been used to suggest that individual differences in working memory capacity also affect the speed of attentional deployment to targets amongst distactors [@heitz_focusing_2007]. In their version of the Eriksen flanker task @heitz_focusing_2007 showed participants a string of letters containing a central target and either congruent or incongruent flankers. Crucially, the response deadline was varied across blocks such that participants had 700ms to respond at the start of the experiment but this reduced to 200ms by the end. Participant accuracy is at chance when response deadlines are very short, as they increase participants respond initially respond to the salient flanker information. Accuracy eventually increases and asymptotes once the deadline is sufficient for focusing attention completely on the central target. High capacity individuals are faster at focusing their attention onto the target than low capacity individuals. @poole_working-memory_2009 subsequently showed that high capacity individuals are also better at maintaining the focus of spatial attention on targets across time.

While load manipulations and capacity differences have each been shown to have independent effects on attentional deployment to targets, @ahmed_focusing_2012 investigated the interaction between load and capacity within the same experiment. An Eriksen-type flanker task was again used, however this time it was presented during the retention interval of a digit recall task which had high load and low load conditions. @ahmed_focusing_2012 systematically varied the distance between the target and flankers in the Eriksen flanker and the resulting pattern of interference across distances provided a measure of the spatial distribution of attention on the task. The results showed that spatial attention is more constrained to the target under low load than high load, and more constrained in high capacity individuals than low capacity individuals. These patterns interact such that high capacity individuals who are under low load have the most tightly constrained attentional focus. When they are placed under high load, high capacity individuals begin to look like low capacity individuals under low load. When low capacity individuals are under high load, the distribution of spatial attention is the least constrained of all. These data further suggest that decreased working memory availability, whether that be a result of innate capacity or temporary increases of concurrent load, result in a slower and less spatially specific allocation of attention to targets.

The evidence provided has been used to suggest that when the availability of working memory is reduced, processes of target selection and maintenance are reduced. Therefore the specific attentional process shared by working memory and attention is posited to be the process of target selection. The results presented however are not functionally specific enough to make these claims with certainty. In their fMRI study for example, @scalf_working_2011 recorded delayed target processing when a concurrent working memory load was introduced. An alternate possibility however is that delayed disengagement from the T1 stimulus is the cause of the observed effects and that target selection speed per se, is unaffected. Similarly many of these paradigms use a variation of the Eriksen flanker task which includes distracting flankers [@heitz_focusing_2007;Poole&Kane2009;AhmedDeFockert2012]. Consequently in each case it's impossible to tease apart the effects of target selection, distractor suppression, and distractor disengagement, and alternate evidence has been used to argue that distractor related processes underlie the relationship between working memory and attention.

### Distractor capture.

An alternate process central to efficient visual search is distractor capture. Although the pursuit of an individual's goals requires voluntary allocation of attention to goal relevant objects and locations, it is well established that objects in the environment can involuntarily capture an individual's attention `r #Reference`. Performance on goal oriented tasks is often the output of competitive interactions between these two ways of orienting attention. Suboptimal performance of goal directed behaviour can therefore be the result of underactive processes of goal maintenance and target selection as described in the previous section, however an alternate account is that it is the result of overactive capture of attention by task irrelevant stimuli. A separate line of research into working memory and attention has therefore suggested that working memory and attention interact through their shared involvement with systems of distractor capture.

@fukuda_human_2009 used a cued target identification task along with EEG in order to establish that working memory is related specifically distractor capture and not target selection. Participants in their task were cued to the location of an upcoming target box, and had to report the side of the box which had a gap. In two thirds of trials the target array was followed after 50ms by a salient probe stimulus either at the target location or at the location of irrelevant objects in the target array. They measured early visual responses to the target display and the probe display in order to show that while responses to the target stimuli are the same for individuals with low and high working memory capacity, probe responses differ. For high capacity individuals, probes presented at the target location elicited large neural responses whereas probes presented at the distractor locationsdid not suggesting their attention was constrained to the target location and not captured by probe onset. Low capacity individuals on the other hand showed equivalent responses to both probe types suggesting their attention was more easily captured by irrelevant stimuli.

@fukuda_human_2009 also tested the idea of unnecessary storage, a specific mechanism which would explain why distractor capture is associted with working memory capacity. Unnecessary storage is the proposal that increased distractor capture leads to the storage of irrelevant items in working memory. This would reduce funcitonal capacity of an invidiual as the inclusion on any irrelevant items in working memory reduces the available capacity for task relevant objects. In their experiemnt, @fukuda_human_2009 included a working memory version of their paradigm where participants stored a set of objects which were followed by probes after 50ms, and then were tesed on the stored objects after short delay. @fukuda_human_2009 used an electrophysiological measure of object storage which increases as working memory set size increases [@vogel_neural_2005]. Individuals whose measure of object storage increased in the presence of distractors were posited to be unnecessarily storing those objects, and the size of this effect was correated with attentional capture by irrelevant objects. They concluded that low capacity individuals have impaired distractor inhibition which may lead to the unnecessary storage of distractor items in working memory.

Similar effects have been used by other authors in order to reinforce the view that working memory capacity is specfically related to an individual's ability to ignore irrelevant objects. Brain activity recorded using fMRI has also measured filtering ability by informing participants of the presence or absence of distractors in upcoming displays, and measuring the difference in preparatory activity. This activity is significantly correlated with working memory capacity [@mcnab_prefrontal_2008]. EEG evidence of item storage has shown that low capacity individuals can be shown to have stored more objects than high capacity individuals when some of the objects displayed are irrelevant, again suggesting that they are storing not only the task relevant objects but the irrelevant objects as well. While these experiments have concluded that low cpaacity individuals struggle with the ability to ignore irrelevant objects, as was the case with evidence for target selection, they lack the functional specificty to make this claim with certainty.

In all cases these paradigms seem unable to rule out the possibilty that low capacity individuals are failing at the maintenance of target information. In the task used by @fukuda_human_2009, it is possible that high capacity individuals are better at using the cue to constrain attention to the target representation. Apparent evidence of differences in distractor capture is therefore only a consequnce of differences in target selection. Low and high capacity individuals may be equally prone to the capture of their attention by distractor items present in the focus of their attention, but high caacity individuals are simply capacble of narrowing this focus better than low capacity individuals. Similary the preparatory activity measured by [@mcnab_prefrontal_2008], and unnecessary storage itself may be a consequence of impaired target selection and maintenance. A third alternatie has also since been proposed, that it is not the initial capture of attention which differs, but rather the subsequent recovery speed.

### Distractor disengagement.

The fact that irrelevant distractors impact more on individuals with low working memory capacity more than individuals with high working memory capacity could suggest that low capacity individuals struggle more with suppressing distractor capture. An alternate accoutn however is that both groups are equally prone to the intiial capture of attention by irrelevant distractors, and that performance differences are the result of differences in their ability to disengge their attention from the distractor object, before reorienting attention to the target. This nuanced distinction was tested specifically by @fukuda_individual_2011.

@fukuda_individual_2011 used both psychophysical and electrophysiological measures in a visual search task in order to disitnguish between distractor capture and distractor disengagement. Participants in their task had to identify the orientation of a target objec defined by a specific colour. Prior to the onset of the search array, a flanker would briefly appear in two thirds of trials possessing either the target colour, or a non-target colour. The onset of the flanker is predicted to cause a shift of attention to the flanker location, decreasing performance on the search task relative to trials where no flanker is presented. Flankers possessing the target colour are predicted to be mre difficult to disengage form and therefore differences in distractor disengagement speed should be present in these trials. @fukuda_individual_2011 also titrated the length of time between flanker and target in order to observe the length of time it takes for an individual to recover from flanker onset. Their results showed that high and low capacity individuals are equally prone to attentional capture by non-target flankers, however high capacity individuals recover faster from the onset of target coloured flankers, and recovery time is corrrelated with working memory capacity.

This was followed up with an EEG experiment in order to provide neural evidence to distinguish between distractor capture and distractor disengagement [@fukuda_individual_2011]. In this task, @fukuda_individual_2011 used a task based on their previous study measuring distractor capture which was described above [@fukuda_human_2009]. Participants were cued to the location of an upcoming target, repsonded to the target amongst distractors, and then a salient probe appeared either at the target location or a distractor location. In this version however they varied the interval between target and probe displays from 50ms to 200ms in order to measure the effect that the probe location has on neural responses as a function of available disengagement time. Their results show that with a 50ms interval, there is no difference between the neural response to probes at distrator and target locations for either high or low capacity individuals, indicating that with such short delays, neither group has managed to disengage from distractor locations and focus attention on the target. High capacity individuals show a reliable difference by 100ms, whereas low capacity individuals don't show equivalent differences until the interval is 200ms long. These results corroborate the initial findings that low caacity individuals are not necessarily more prone to capture by distractors, but specifically struggle with the ability to disengage efficiently from distractors which have captured attention.

Evidence for impairments of ditractor disengagement in low capacity individuals is relatively scant at the moment. While there is very little evidence to contradict the findings of @fukuda_individual_2011, there is also very little replication or extension of the effects they reported. The experimental paradigms used to date have typically lacked the functional specificity required in order to tease apart nuanced subprocesses of attention like target selection, distractor capture, and distractor disengagement.

## Measuring Attention with EEG
The apparent overlap in executive control and attentional control mechanisms leads to the current situation where we want to see whether measures of attentional control can be recorded in a working memory context and shown to be effected by working memory availability. 

Although it has been established that the appropriate allocation of attention can significantly improve performance on visual tasks to compensate for limitations in the visual system, a major goal of research in this field is to understand the neural mechanisms which facilitate the selective process. A number of models of visual selective attention have been proposed, usually relying on either target enhancement which h increases processing of the attended objects, noise reduction which suppresses irrelevant, distractor stimuli, or a combination of both (Phaf, van der Heijden & Hudson, 1990; Houghton and Tipper, 1994; Desimone & Duncan, 1995). Early models of selective attention have been based on the use of classic behavioral paradigms to establish evidence for both target processing (Carrasco, Williams, & Yeshurun, 2002; Carrasco, Ling, & Read, 2004; Ling & Carrasco, 2006) and distractor suppression (Lu & Dosher, 2000; Frings, Wentura, & Wuhr, 2012), and recent work has supplemented these paradigms with neuroimaging techniques which allow for a more direct examination of the neural processes involved. Single cell recordings in non-human primates has been able to provide support for the presence of target enhancement (Motter, 1993; Treue & Maunsell, 1999; Reynolds, Pasternak, & Desimone, 2000) and distractor suppression (Reynolds, Chelazzi, & Desimone 1999; Miller, Gochen, & Gross, 1993; Reynolds & Desimone, 2003), as has functional magnetic resonance imaging (fMRI) in humans (Gandhi, Heeger, & Boynton, 1999; Brefczynski & DeYoe, 1999; Kastner, Pinsk, De Weerd, Desimone, & Ungerleider, 1999; Kastner, De Weerd, Desimone, & Ungerleider, 1998). The high temporal resolution of EEG has allowed for detailed study of the time course of attentional processes in humans, however EEG analysis often involves traditional event related potential (ERP) techniques which are limited in their ability to attribute changes in activity to specific psychological processes.

### Alpha.

Things that Katharina said

### VEP components.

Electrophysiological recordings in humans have provided evidence of attention's role in enhancing the signal of an attended item. When EEG is used to calculate ERPs in the Posner cuing paradigm (Posner, 1980), valid trials (where individuals are cued and therefore attend to the location of a subsequent stimulus) correspond to increases in the amplitude of the P100 and N100 when compared to invalid trials (where the stimulus appears in a non-cued location) (Mangun & Hillyard, 1991). Luck, Hillyard, Mouloua, Woldorff, Clark, and Hawkins (1994) refined this finding and suggested that it is the amplitude of the N100 specifically which indexed enhancement of an attended stimulus. The P300 has also been shown to significantly increase in amplitude during attention demanding tasks as has the N400, a component traditionally observed in response to words (Coull, 1998). The number of studies utilizing traditional ERP methods to investigate distractor representations is comparatively small. One ERP component which has been associated with distractors is the P3a which, along with the P3b, is a subcomponent of the P300. Bledowski et al. (2004) used an oddball paradigm to show that while a P3b is elicited by both targets and distractors, the P3a is exclusively elicited by distractors and localized to the precentral sulcus and anterior insula. A frontal negativity has also been observed to cumulatively activate as the number of distractors preceding a target increases (Niedeggen, Michael, & Hesselman, 2012). While these traditional measures have provided some evidence for target and distractor related activity in the human visual system, it is hard to attribute changes in the ERP activity to specific psychological processes. One of the best studied electrophysiological components which is used as an index of attentional selection is the N2pc, a laterallized component which is produced with the contralateral control method.

### Lateralized components.

While frequency based measures like alpha power, and event-related components like the P3 provide neural indices of attentional processing, they typically suffer from a lack of function specificity. A procedure known as the contralateral control method has recently been applied to event-related potentials in the visual search domain yielding a set of dissociable components which appear to index the processes of target selection, distractor suppression, and storage of target features relevant to the upcoming response. This technique is promising in providing the functional specificity we need in order to interrogate the fundamental processes shared by working memory and attention.

#### The contralateral control method.

The contralateral control method addresses many of the problems associated with traditional ERP measures. It allows for the isolation of activity related specifically to the experimental variables that are being manipulated and removes unrelated activity (Luck, 2005), taking advantage of the hemispheric organisation of the cortex. A well-known example of contralateral organisation is observed in the motor cortex, where preparing movements of the right hand will elicit greater activity in the left motor cortex whereas preparing movements of the left hand elicits increased activity in the right motor cortex. It is possible then, if EEG is recorded during these tasks, to use the contralateral control method of analysis to extract only that activity which is systematically related to a hand movement.

Standard EEG nets are arranged symmetrically such that each electrode on the left-hand side of the scalp, has an equivalently placed electrode on the right. This means that in the case of preparing a right handed movement, activity is recorded at equivalent scalp locations over the right and left motor cortex and when participants are preparing a left handed movement, activity is again recorded at equivalent scalp locations over the right and left motor cortex. Activity is then collapsed across conditions by averaging the contralateral activity together (left hemisphere electrodes for the right hand condition and right hemisphere electrodes in the left hand condition) and then the ipsilateral activity together (right hemisphere electrodes for the right hand condition and left hemisphere electrodes in the left hand condition). Finally, ipsilateral activity is subtracted from contralateral activity to produce the difference wave which shows only that activity which is produced contralateral to a prepared hand action. At this stage all activity that is the same in both hemispheres has been removed, as well as any activity that is systematically different between hemispheres. This makes it easier to relate brain activity to underlying psychological processes because as long as appropriate experimental design is used, the only activity remaining is the activity systematically laterallized in response to manipulations of the experimental variable (Gratton, 1998). 

The visual system has a hemispheric organisation similar to the motor system such that the left visual field (LVF) projects to the right visual cortex and the right visual field (RVF) projects to the left visual cortex. Researchers have therefore been able to apply the contralateral control method to isolate laterallized activity which specifically indexes attentional processes in the visual system. There are important methodological points which must be considered in order to ensure that the activity is specifically related to processes of attention as opposed to any non-attentional activity. The major point to be considered is that the sensory energy of each visual field should be equivalent (Woodman & Luck, 2003). If attention were measured by simply having participants attend to a target which appeared in different parts of the display then the contralateral control method would result in a difference wave containing the activity related to the systematic movement of the stimulus as well as the activity related to the systematic movement of attention. While ideally the sensory stimulation should be identical in each visual field, a number of studies have demonstrated that it is sufficient to balance luminance (@hickey_electrophysiological_2009; Hilimire, Mounts, Parks, & Corballis, 2009; Sawaki & Luck, 2010).

Lateralized ERPs have typically been studied in visual selective attention with visual search paradigms, where participants are presented with an array of objects and must identify and respond to some feature of a target stimulus embedded within the array. Participants fixate on a central cross throughout and bilateral displays are used in order to ensure a sensory balance between visual fields. Using measurements around the onset of the visual search array and applying the contralateral control method makes it possible to identify laterallized ERPs which reflect mechanisms of selective attention. Electrophysiological studies utilizing this approach have identified a number of laterallized components which appear to consistently index attentional processes and may therefore be crucial to the study of visual attention.

#### The N2pc.

The laterallized component which has become a focus of studies of visual selective attention is the N2pc, named after its latency and scalp distribution. It is recorded as an increased negative voltage occurring approximately 180-250ms post-stimulus presentation, around the N2 time range, at posterior scalp sites contralateral to the attended stimulus. The precise attentional mechanism which the N2pc reflects is still unclear however a full understanding of the N2pc is becoming increasingly important for researchers in a number of fields because it is being used as a tool for studying cognitive systems. N2pc-like effects were originally observed in a number of studies (Heinze, Luck, Mangun, & Hillyard, 1990; Luck, Heinze, Mangun, & Hillyard, 1990; Luck & Hillyard, 1990) but were first described as the N2pc by Luck and Hillyard (1994a). It has since been described as indexing both target selection and distractor suppression by different authors at various times and the details of its functional significance are still contentious.

Luck and Hillyard (1994a) used displays containing 8 identical bars scattered around a fixation cross. In half of the displays, one of the bars would pop-out from the rest by being different in either orientation, color, or size and participants had to identify whether the pop-out bar possessed a predefined target attribute. Their results showed that the N2pc was significantly larger when the pop-out was a target than when a non-target pop-out appeared in the display and that despite its late latency, current source density (CSD) maps estimated its generator to be in the occipital lobe, a region associated with early visual processing. They concluded from the N2pc modulations, latency, and location estimates, that it indexes a process being applied to targets rather than non-targets, and may reflect the control of information flow in the visual system through a top-down filtering mechanism. Eimer (1996) extended this finding by showing that target attributes like form, color, and content could affect the N2pc time range, arguing also that the presence of the N2pc when distraction is minimal indicates that it represents the identification of task-relevant stimuli.

A group of early experiments however appear to contradict this finding and instead suggest that the N2pc indexes distractor suppression. When distracting items are removed from a display, made relevant to the task at hand, or when all items in the display are made to be identical targets, an N2pc is no longer elicited (Luck & Hillyard, 1994b). Luck, Girelli, McDermott, and Ford (1997) proposed the ambiguity resolution theory as a result of this work as well as their own work comparing the N2pc to electrophysiological studies in monkeys. Single unit recordings in monkeys have provided significant evidence for the existence of a suppressive mechanism in visual attention, and the fact that N2pc modulations are consistent with monkey electrophysiology in response to changes in the number of stimuli in each hemifield, the location of the stimulus in upper or lower visual fields, and changes in task difficulty, led Luck and colleagues to suggest that the N2pc reflects a human correlate of this well established suppressive mechanism. 

More recent studies however have provided evidence once again for the conception of the N2pc as an index of target selection. When a target and an irrelevant salient distractor are presented in opposite hemifields, an N2pc is elicited initially by the salient distractor and subsequently by the less salient target. It is difficult to reconcile this shifting of the N2pc from distractor to target with an N2pc which has a primary role in distractor suppression (Hickey, McDonald, & Theeuwes, 2006). Similar effects were found with displays consisting of sequential streams of stimuli either side of fixation, when participants were randomly instructed to attend to targets in one of the two streams (Dell'Acqua, Sessa, Jolicouer, & Robitaille, 2006). More recently, Mazza, Turatto, and Caramazza (2009) used different visual displays and showed that an increased N2pc was in fact found when distractors were necessary for identifying the target, that increased proximity of distractors to the target did not modulate the amplitude of the N2pc, and that heterogeneous distractors did not modulate N2pc amplitude while they did negatively effect behavioral performance. The results of these studies have been argued as evidence that while distractor numerosity may play some part in producing the N2pc, it primarily indexes target enhancement processes.

Resolving the questions surrounding the nature of the N2pc is becoming increasingly important as researchers begin to utilize it as a tool for understanding cognitive systems. Properties of the visual system itself have been investigated through the use of the N2pc, which has been used as evidence that visual search is executed by serial processing of multiple targets within a scene rather than through parallel processes (Woodman & Luck, 1999). It has also been used in various lines of research to argue for example that the right hemisphere has a processing advantage for fast sequences (Verleger, Smigasiewicz, & Moller, 2011), that top-down processes are necessary for the attentional capture of target singletons (Holguin, Doalla, Vizoso, & Cadaveira, 2009), and that color cues which are not consciously perceived and do not register behavioral effects, are still capturing attention (Ansorge, Kiss & Eimer, 2009). The N2pc has been combined with other techniques to demonstrate that single pulse transcranial magnetic stimulation (TMS) to the right posterior parietal cortex effects behavioral performance through interference of attentional selection (Fugetta, Pavone, Walsh, Kiss, & Eimer, 2006). Participants with high trait anxiety have been shown to elicit enhanced N2pc components to threatening stimuli (Fox, Derakshan, & Shoker, 2008), and similarly people with blood phobia have been shown to elicit an enhanced N2pc to images of injuries (Buodo, Sarlo, & Munafo, 2010). In both cases this has been provided as evidence that these groups have early attentional biases towards these stimuli. A detailed understanding of the N2pc and the processes it reflects appears to be crucial for a detailed understanding of the mechanisms of selective attention and important because of its use as a tool in other areas of research. Electrophysiological studies of visual selective attention have sought to clarify the target and distractor related characteristics of the N2pc.


#### Ptc/Pd.

A suggestion which may resolve the discrepancies in studies of the N2pc is that the N2pc itself is actually the summation of two subcomponents which individually index target and distractor processing, named the Nt and Pd respectively. Hickey, Di Lollo, and McDonald (2009) took advantage of one of the features of the contralateral control method in order to tease apart the contributions of targets and distractors to laterallized potentials. In their series of experiments, Hickey and colleagues (2009) presented participants with displays consisting of two objects, one of which was designated the target which participants had to respond to, while the other served as a distractor. A crucial feature of the contralateral control method is that activity which is equal in both hemispheres will be subtracted to zero. If an object is on the midline in Hickey and colleagues' (2009) displays, activity related to that object will be equal in both hemispheres and therefore its contribution to the final laterallized potentials will be zero. By including trials where a distractor was laterallized from a target on the midline, and trials where a target was laterallized from a distractor on the midline, they were able to isolate activity related to each of these objects individually. Their results showed an increased negativity contralateral to targets which peaked around 200ms post-stimulus, and an increased positivity contralateral to distractors which peaked around 240ms post-stimulus. They named these components the target negativity (Nt) and the distractor positivity (Pd) which, when summed together produced an N2pc-like potential.

Further evidence for a target related negativity and distractor related positivity was provided by an electrophysiological study of salient singletons. Sawaki & Luck (2010) instructed participants to search for a target within a specific region which sometimes included distractors. The distractors could be similar to the target or have increased bottom-up salience. An N2pc was observed in relation to targets and target-similar distractors in the attended region but not the unattended region. An increased positivity peaking around 200ms post-stimulus presentation was elicited by salient distractors regardless of whether or not they were in the attended region. This was interpreted as showing that the salient objects produced a bottom-up attention grabbing signal which is actively suppressed by the Pd when it is task-irrelevant. In both of these investigations of the Nt and Pd, scalp topographies of the voltages indicated that both components had their maximal voltage at the same lateral occipitotemporal sites.

Multiple contributions to the N2pc are also consistent with earlier attempts at localizing the N2pc wave. Hopf and colleagues (2000) used magnetoencephalography (MEG) to record and localize the magnetic analogue of the N2pc with a simple orientation discrimination task. Displays consisted of 24 vertical and horizontal bars randomly distributed across the display, one of which was the target color. Participants had to indicate whether the target bar was horizontal or vertical while EEG and MEG was recorded. A number of source localisation procedures identified an early parietal source for activity between 180-200ms and a later occipito-temporal source between 220-240ms post-stimulus. Originally these two sources were presented as representing the initial orienting and subsequent focusing of attention to an object however the visual search tasks did not allow for the dissociation of target and distractor related activity and an alternative interpretation may be that they were inadvertently localizing the magnetic analogues of the Nt and Pd.

A similar or possibly identical component was independently identified by Hilimire etc. (2009) and has since been referred to as the Ptc.

The Ptc was first described in a study where the target-decoy paradigm was being used to investigate the effects of spatial competition on the amplitude of the N2pc. In their version of the target-decoy paradigm, Hilimire and colleagues (2009) randomized the color of the target and decoy on each trial such that the target could be green or orange, the distractor could be green or orange, but they could never be the same color on a given trial. This ensured that participants first had to discern which of the colored objects was the target, before reporting its orientation. They also randomly varied the distance between the target and the decoy to be 2°, 6°, or 10° of visual angle on each trial. Previous experiments have demonstrated a phenomenon called localized attentional interference, where objects which are closer together result in increased competition for attentional resources and therefore slower responses and increased error rates. By recreating this effect with the target-decoy paradigm, Hilimire and colleagues (2009) were able to control for variables which would otherwise confound the contralateral control method and investigate the effects of localized attentional interference on laterallized potentials. The results showed a modulation of the N2pc as a consequence of spatial competition, where N2pc amplitude decreased as targets and distractors moved closer together. A second unexpected result however was the observation of an increased positivity following the N2pc which also appeared to be modulated by completion, increasing in amplitude as targets and distractors moved closer together. This component was named the Ptc because it was a positivity, temporal in scalp distribution to the N2pc, and contralateral to attended items. The Ptc appeared to be distinct from the Pd due to its different latency and scalp topography.

Initially it was unclear exactly what process the Ptc might be reflecting and given that it appeared immediately following the N2pc, Hilimire and colleagues (2009) suggested it may reflect the individuation or isolation of a target after it has been identified by the N2pc related process. It was also possible at this point that the Ptc modulations were nothing more than a result of the N2pc extending into the time range of this positive component such that the increasing Ptc was simply the result of the decreased negativity of the N2pc (Hilimire et al. 2009; Hilimire, Mounts, Parks, & Corballis, 2010). Partial dissociation of these components was achieved through the manipulation of salience and task requirements in the same target-decoy paradigm used to discover the Ptc (Hilimire et al. 2010). The results of these manipulations showed that in some conditions it was possible to elicit modulations of the N2pc without subsequent modulation of the Ptc therefore ruling out the possibility that the Ptc reflected late N2pc activity and instead providing evidence that it reflects a subsequent process necessary for target individuation. 

Target enhancement and distractor suppression are both candidate mechanisms which would allow for the individuation of a target object. Hilimire, Parks, Mounts, and Corballis (2011) carried out a follow up study which took advantage of the same aspect of the contralateral control method that Hickey and colleagues (2009) had used to dissociate Nt and Pd. Utilizing the same target decoy displays, Hilimire and colleagues (2011) this time included conditions in which one of either the target or distractor was placed on the midline while the other was lateralized. The target-decoy paradigm used in this experiment allowed for the measurement of the N2pc and Ptc in displays with multiple objects that were equal in luminance, shape, and color, something which had not been achieved in examinations of the Nt and Pd. The results showed that an N2pc in response to both targets and distractors indicating, as hypothesized, that both objects captured attention initially. The Ptc however was only elicited contralateral to a distractor, suggesting that it reflects a mechanism of suppression which allows the distractor to be ignored, aiding in the isolation of the target. The apparent functional differences between the N2pc and Ptc, as well as the consistent difference of their scalp topographies suggest that they may reflect distinct processes with separate neural generators. These facts as well as Hopf and colleagues' (2000) finding that multiple generators may be contributing to the lateralized components in visual attention suggest that it may be possible to further dissociate target from distractor processing in the target-decoy paradigm through the use of EEG source localisation.

#### SPCN.

Visual short term memory is an integral part of the visual attention system that is limited in both storage capacity and encoding rates, and studies of the N2pc have also provided evidence for an electrophysiological analogue of VSTM (Cowan, 2000; Marois & Ivanoff, 2005). Sustained negativities contralateral to stimuli passing through VSTM have been identified in a range of studies and referred to as the contralateral negative slow wave (CNSW) (Klaver, Talsma, Wijers, Heinze, & Mulder, 1999), contralateral delayed activity (CDA) (Vogel & Machizawa, 2004), and sustained posterior contralateral negativity (SPCN) (Eimer 1996; Luck, Fan, & Hillyard 1993; Robitaille & Jolicoeur, 2006). While there are variations in the details of these different components, it is possible that these differences are due to differences in high level task demands and low level stimulation and therefore for the purposes of this study we will refer to all sustained negativities at posterior electrodes subsequent to the N2pc time range as SPCN.

The SPCN is often observed in experiments which require visual search for a target object, followed by further processing and/or memory for features of that target. In the previously mentioned experiment by Dell'Acqua and colleagues (2006) where the N2pc was related to the shift of attention towards targets, subjects were presented with two sequential sets of stimuli. One or both of the sets required attention, and in some instances one or both of the stimuli also required retention of target characteristics. In their experiment, an SPCN was observed following the N2pc contralateral to attended targets, and it was suppressed in the same conditions which caused a suppression of the N2pc. Kiss, Van Velzen, and Eimer (2008) recorded an SPCN in a visual search task with displays consisting of cued circular arrays. They found that the SPCN was suppressed along with the N2pc when a target was absent from the search array. While these experiments are primarily related to visual search, the nature of the tasks also require the use of VSTM to hold the target object in memory, extract relevant information about its features, and therefore inform the participant's response (Jolicoeur, Brisson, & Robitaille, 2008). It has been argued on the basis of these results that the SPCN indexes this retention process, however these experiments are not direct tests of VSTM.

A stronger link between the SPCN and VSTM processing comes from experiments specifically designed to investigate VSTM. Klaver, Talsma, Wijers, Heinze, and Mulder (1999) used bilateral displays of polygons to test the contribution of VSTM processing to laterallized ERPs. One of the objects, as indicated by a cue, had to be retained in VSTM for 1500ms before participants were tested on its attributes. The presence of an SPCN contralateral to the remembered object during both the encoding and retrieval phases was used as direct evidence that it indexes memory processing. Vogel and Machizawa (2004) used arrays of briefly presented colored squares in the left and right visual field in order to test similar effects. Once again participants were cued as to which side of the display they should retain in memory and after a delay, they were shown a test display and had to indicate whether the two displays matched. In agreement Klaver and colleagues' (1999) findings, Vogel and Machizawa (2004) observed an SPCN throughout the retention period and more importantly, demonstrated that the SPCN increases in amplitude as the number of remembered stimuli increases, but only up to its estimated capacity limit. The finding that SPCN is modulated by changes in the number of stimuli held in VSTM has since been replicated and extended to rule out confounds (McCollough, Machizawa, & Vogel, 2007).

These results provide direct evidence for the involvement of the SPCN in VSTM and support the suggestion that its presence in visual search paradigms is a result of the use of VSTM as an intermediate processing buffer. Jolicoeur and colleagues (2008) wanted to establish that the SPCN observed in direct measures of VSTM was the same as that seen in traditional search tasks, and also functionally dissociate the N2pc from the SPCN within the same experiment. Participants were presented with bilateral displays consisting of 4 digits (2 in the LVF and 2 in the RVF) and had to encode and respond to the object of a specified color. Participants therefore had to search for the appropriate item before responding and on half of the trials they were required to encode both objects in the visual field of the target object. The results showed that requiring individuals to encode multiple objects led to an increase in the amplitude of the SPCN and that the N2pc was not modulated by memory load in this way. This demonstrates that the SPCN in visual tasks is likely the same component as the SPCN in memory tasks and that it serves a distinct functional role from the N2pc.


