
# Introduction

For most of our daily lives our senses are bombarded with vast amounts of information. Even the most mundane tasks like grocery shopping can involve encountering thousands of objects, people, and sounds. Successfully completing even small short-term goals like finding a specific flavoured ice cream involves holding information in mind while we sift through the near unlimited amount of information available in the environment. The images we hold in memory inform those objects that capture our attention. We might recall a specific colour from the packaging and filter information based on whether it matches that colour, or we might remember its general location and select information from that area. At the same time, the information we receive from the environment updates what we have stored in memory. We store the prices, and sizes of the objects we have encountered and use this information to mentally compare across brands. Successful performance in everyday situations depends on the effortless execution of a continual back and forth between these complex processes, and in this very real-world sense, the processes of selective attention and short-term memory are functionally linked.           

Since the beginning of experimental psychology in the late 19th century, the study of human cognition has been parcellated into a set of distinct, fundamental constructs. Typically, these distinctions have been made based on the intuitions of foundational thinkers in psychology, and in his seminal work \textit{The Principles of Psychology}, William James recapitulated one such historic distinction between the constructs of attention and memory [@james_1890]. Throughout the course of the 20th century, conceptions of attention and memory were specified, and formalized. The performance of selective attention encompasses a set of underlying distinctions like overt versus covert orienting, and endogenous versus exogenous attention. Similarly, the concept of memory was separated into specialized processes like short-term versus long-term memory, and semantic versus episodic memory. These processes have in turn been parcellated into even more specific functional units such that the deployment of endogenous, covert attention for example, is dependent on fundamental neural processes like target selection, and distractor suppression.

Recently, empirical work has started to show that the fundamental units necessary for the optimal functioning of selective attention may be related to, or shared by, the fundamental units necessary for the maintenance of objects in short-term memory. Modern models of short-term memory, or working memory as it has come to be known, typically depend on a system of executive control. Executive control determines the set of information that gains access to those limited resources that are involved in storing and processing information in the short term. The role of this executive control system has a lot of conceptual overlap with the role that selective attention plays more broadly in information processing in the human brain. Modern approaches in experimental psychology and cognitive neuroscience are now beginning to unify these traditionally disparate constructs and specify the nature of their interaction.

While historically, progress in experimental psychology has been based on measures of behaviour, a range of non-invasive techniques now exist which allow for the measurement of brain activity in awake humans. One of the most popular techniques for recording neural activity is electroencephalography (EEG) which allows for the direct measurement of neural activity at the time scale of actual neural processing. Methods of EEG data analysis have matured to the point where modern work has started to rely on direct measures of neural activity to make nuanced distinctions between processes that are invisible to behavioural measures. The event-related potential (ERP) technique is one such method of EEG processing which has gained wide adoption and can provide reliable, and dissociable measures of fundamental neural processes like target selection and distractor suppression.

The aim of this thesis is to expand our understanding of the relationship between working memory and selective attention, and to specify the neural mechanisms that may be shared by these two seemingly disparate systems. In study one, we used a behavioural task to perform a systematic analysis of the effect that irrelevant objects have on performance in the change-detection task. The change-detection task is a popular way of measuring visual working memory capacity however there are a number of subtle variations in the way it has been used and the effect of these variations on capacity measures is undetermined. Study one sought to fill this gap in the literature. Studies two and three aimed to follow up two of the benchmark effects established by study one while using EEG to simultaneously measure neural indices of attentional control. In study two we were interested in seeing the effect that increased working memory load can have on neural measures of target selection, and distractor suppression. In study three, our aim was to understand how the effect of irrelevant objects in a change detection task effect neural indices of target selection and distractor suppression.

# Working Memory

Dedicated study of the concept of memory in western thought goes back at least as far as Aristotle [@burnham1888memory], however systematic study of the short-term retention of information began in earnest with investigations into short-term memory span originally published in 1885 by Hermann Ebbinghaus [-@ebbinghaus2013memory]. Working memory is a relatively new term coined by  Miller, Galanter, and Pribram, (1960) which has largely supplanted the concept of short-term memory to define a cognitive system which temporarily stores information for the purposes of active processing and manipulation. The dominant model of working memory which survives to this day (albeit with revisions) was originally proposed by Baddeley and Hitch in 1974 aand has placed working memory at the centre of perception, memory, and action. A large body of empirical work has accumulated to show the important role that working plays in diverse areas of cognitive functioning, and as a result, methods for the measurement and understanding of working memory have become increasingly important.

## Short-term memory
MEASURES OF SHORT-TERM MEMORY: A HISTORICAL REVIEW
John T.E. Richardson

## Miller coining term and magical numbers
## Baddeley Model
WORKING MEMORY: LOOKING BACK AND LOOKING FORWARD
Alan Baddeley
## Working memory and its role in other abilities
## The measurement of capacity
There's a lot of variation in working memory capacity between individuals and this can be measured by each of these tasks. In OSPAN  etc... blah blah, in nback ... in sternberg... in change detection ..
Can't train it, says William james and modern stuff (not really relevant)
Working Memory Updating and Binding Training: Bayesian Evidence Supporting the Absence of Transfer - JEP:G
## Neuroanatomy of working memory/neural measures of working memory (kinda irrelevant)
# Selective attention
```{r notesText} 
#Main goal of this section should be to determine what abilities underlie successful performance of selective attention. End up talking about the dual importance of selecting relevant information and suppressing irrelevant information. Then discuss neural measures of these things.

#https://www.researchgate.net/post/Estimates_of_quantified_human_sensory_system_throughput10

#\begin{quote}
#"Everyone knows what attention is. It is the taking possession by the mind, in clear and vivid form, of one out of what seem several simultaneously possible objects or trains of thought. Focalization, concentration, of consciousness are of its essence. It implies withdrawal from some things in order to deal effectively with others, and is a conditions which has a real opposite in the confused, dazed, scattered state which in French is called distraction, and Zerstreutheit in German."
#\end{quote} - William James
```
## Sub-processes of attention
## Neural measures of attention.

# The relationship between working memory and attention
```{r copiedTextFromSAWMDistIntro}
#Everyday situations such as grocery shopping and driving depend on our ability to both efficiently allocate attention to relevant objects while suppressing distraction, as well as maintain and retrieve information from working memory. Although research over the past decade has demonstrated significant functional overlap between attention and working memory, the multifaceted nature of the relationship between these two constructs is not well understood [@fougnie_relationship_2008;@de_fockert_beyond_2013]. Converging evidence suggests that when load on a concurrent working memory task is increased, performance on an attention task is subject to increased interference from irrelevant distractors [@ahmed_focusing_2012;@de_fockert_role_2001;@stins_role_2004]. There is also evidence that individuals low in working memory capacity show greater interference on a standard Stroop task [@kane_working-memory_2003], as well as greater interference on an Eriksen flanker task [@shipstead_working_2012]. Taken together, these findings suggest that the relationship between selective attention and working memory may be better framed in terms of working memory availability. From this perspective, increasing the working memory load on an individual would lead to a decrease in their working memory availability. What's more, individuals with low working memory capacity would have less overall available working memory (see @de_fockert_beyond_2013 for a review).

#Contemporary accounts of working memory availability now typically incorporate attentional control either as an important contributor to working memory capacity[@kane_controlled-attention_2001; @shipstead_mechanisms_2014], or in some cases as the primary determinant of working memory capacity [@engle_working_2018]. The question of why working memory availability is important for selective attention remains unanswered. The aim of this research was to specify the relationship between selective attention and working memory by recording electrophysiological indices of attentional control under varying working memory load.

#Evidence for the effects of low working memory availability on attentional interference is equivocal, and interference with any one of these processes [target selection, distractor suppression] would produce impaired behavioral performance associated with low working memory availability. Some evidence suggests that low working memory availability delays the speed with which individuals can deploy attention to relevant targets [@heitz_focusing_2007; @scalf_working_2011]. Yet, findings from other work suggests that low working memory availability may cause an increase in capture by irrelevant distractors [@fukuda_individual_2011; @vogel_neural_2005].

#A different account was proposed by @fukuda_individual_2011 in research using both psychophysical and electrophysiological measures of recovery from attentional capture in low and high capacity individuals. Findings from this work suggest that the two groups are equally prone to initial capture of attention, but availability of working memory allows more efficient disengagement from irrelevant objects after they have captured attention.
```
## working memory guides attention

One of the primary ways that working memory and attention have been linked is through either implicit or explicit recognition of working memory as the store for attention-guiding templates.

### Contingent capture
## Attention selects the contents of working memory
## Engle incorporating attention into working memory models
Working Memory and Executive Attention: A Revisit
Randall W. Engle
## Unnecessary storage and distractor suppression
## Working memory bechmarks and relevant attention effects
# Measuring attention with EEG
## Alpha
## Regular components
## Lateralized components
### N2pc
### Ptc/Pd
### SPCN