---
header-includes: 
  - \pagenumbering{roman}
#  - \AtBeginDocument{\let\maketitle\relax}
  - \thispagestyle{empty}
  - \usepackage{setspace}
  - \setstretch{2}
  - \AtBeginEnvironment{tabular}{\doublespacing}
  - \AtBeginEnvironment{lltable}{\doublespacing}
  - \AtBeginEnvironment{tablenotes}{\doublespacing}
  - \captionsetup[table]{font={stretch=1.5}}
  - \captionsetup[figure]{font={stretch=1.5}}

title             : "Investigating the Relationship Between Working Memory and Selective Attention"
shorttitle        : "."

author: 
  - name          : "Dion T. Henare"

affiliation:
  - id            : "1"
    institution   : "School of Psychology, University of Auckland"

author_note: |
  \begin{center} A thesis submitted in fulfilment of the requirements for the degree of Doctorate of Philosophy in Psychology, the University of Auckland, 2018. \\ This thesis is for examination purposes only and is confidential to the examination process. \end{center}

abstract: |
  Optimal performance of everyday tasks like driving depend critically on both the ability to store and retrieve small amounts of information in the short term, and the ability to selectively find and process relevant objects while preventing distraction. These two abilities have traditionally been viewed as distinct processes in human cognition, however research now demonstrates significant overlap between the constructs of working memory and selective attention. Previous work has established a role for working memory resources in the successful control of attention, however there are many processes underlying successful attentional control, and affecting any one of them would produce the pattern of results that have been observed. In this thesis we used behavioural and electroencephalographic evidence to investigate working memory and selective attention. We aim to provide a more detailed understanding of the processes underlying the relationship between these two constructs.
  
  Study 1 provided systematic documentation of the effect that distractor objects have on performance in a traditional working memory task, as well as the relationship between these effects and individual differences in working memory capacity. Study 2 used lateralized event-related potentials to measure dissociable components related to target selection, distractor capture, and distractor disengagement while working memory load was manipulated. Study 2 showed that increased working memory load has a specific effect on neural indices of distractor disengagement, while individual differences in working memory performance are related to neural indices of distractor capture. Study 3 used a similar paradigm to Study 2 to show that the presence of irrelevant objects during working memory encoding leads to impairments in performance and modulation of the neural response to targets in a concurrent visual search task. Together, our results provide greater specificity of the relationship between attention and working memory while demonstrating the utility of lateralized ERPs in providing dissociable measures of specific attentional sub-processes. This provides a promising tool for future research which investigates the relationship between working memory and selective attention.
  
  \pagestyle{plain}
  \newpage
  
  \centerline{Acknowledgements} \
  I would first like to thank my primary supervisor Associate Professor Paul Corballis for allowing me to work in your lab and for providing a relaxed, friendly atmosphere where I was able to develop my research skills and independence. You gave me the freedom to pursue my own line of research and never intervened to prevent me from pursuing experimental designs and analyses that I was passionate about. I leave your lab with a huge amount of confidence in not only my research skills, but my ability to manage, and supervise other students. I owe that to the independent atmosphere you have fostered. Thank you also to my co-supervisor Professor Ian Kirk for your support throughout my PhD. I appreciated the friendly atmosphere that you created in your lab and always felt welcome to join you and your students in both academic and social settings. 
  
  I would also like to thank Katharina Limbach for being an amazing role model of not only how to do science, but how to create a supportive lab culture, and maintain a healthy work/life balance. I learnt so much from you ever since we started working together in that glorified closet down in the HSB dungeon, and I feel incredibly lucky to have shared so much time with you and your family.
  
  I am also very grateful to Stuart McGill who had such a large impact on my research practices. You spent a huge amount of time patiently explaining and demonstrating programming skills which became a fundamental part of my degree. The entire lab benefitted from having you around and I'm especially grateful for your ability to put up with all of my stupid questions without ever making me feel like the annoyance that I'm sure I was.
  
  I am very thankful to all my CogNeuro friends who made my degree so much more enjoyable, providing support and encouragement whenever I needed. Those of you who were ahead of me, especially Katharina, Carolyn, and Haeme who were able to give me advice and information that made my introduction to postgrad so much easier and made me feel so welcome. Those of you who went on the same journey, Nicole and Laura especially. I'm not sure how many bottles of wine were shared between us over the course of the last seven years, but it kept me sane and I look forward to sharing many more. Finally, those who joined in on the madness along the way, especially Eric, Steph, Kristina, Emily, and Nicole with whom I shared a lot of drinks and parks, writing sessions, board games, "N2pc WHAT"'s, and summer hangs respectively. You all turned what would have been an interesting postgrad experience into an interesting, exciting, and fun seven years.
  
  An army of technical and admin staff have smoothed the journey for me, and I would like to highlight the contributions especially of Veema, who kept the EEG lab running smoothly and enabled all of my data collection, and Margaret who kept all of our computers up and running and single-handedly ran the most efficient and responsive IT service there's ever been. Similarly, Michelle contributed a huge amount to my time in postgrad and is one of the few people who truly respected the GTAs who worked for her.
  
  Finally, and most importantly, I want to acknowledge and thank my family for their lifetime of support. My parents especially, who have been incredible role models of not only hard work, but of unconditional love and support. I have lived my life with an implicit belief that I could be and do whatever I wanted, and that's because you ingrained that belief in me. You always fostered my interests and allowed me to follow whatever path I chose, backing me up no matter what and I am so lucky to have had you with me. I hope that I can repay in some way the enormous debt of gratitude that I feel I owe you both for everything you've given me. Thank you so much.

bibliography      : ["r-references.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no

numbersection     : no
toc               : TRUE
class             : "man"
output            : papaja::apa6_pdf

---
\begin{document}
\raggedbottom

\newpage
\addcontentsline{toc}{subsection}{\listfigurename}
\listoffigures
\newpage
\addcontentsline{toc}{subsection}{\listtablename}
\listoftables
\newpage
```{r}
knitr::include_graphics("Figures/Chap2_Lenore.pdf", auto_pdf = TRUE)
knitr::include_graphics("Figures/Chap3_Jude.pdf", auto_pdf = TRUE)
knitr::include_graphics("Figures/Chap4.pdf", auto_pdf = TRUE)
```

\newpage
\pagenumbering{arabic}

\section{CHAPTER 1: General Introduction}
\newpage
```{r child = 'GeneralIntroduction.Rmd'}
```

\newpage
\section{CHAPTER 2: Working Memory Capacity in a Change Detection Task is Affected by the Number of Irrelevant
Objects in the Display}
\newpage
```{r child = 'T-WMBehav.Rmd'}
```

\newpage
\section{CHAPTER 3: Working Memory Availability Affects Neural Indices of Distractor Processing During Visual
Search}
\newpage
```{r child = 'T-SAWMLoad.Rmd'}
```

\newpage
\section{CHAPTER 4: Working Memory Distractor Presence Affects Neural Indices of Target Processing During Visual
Search}
\newpage
```{r child = 'T-SAWMDist.Rmd'}
```

\newpage
\section{CHAPTER 5: General Discussion}
\newpage
```{r child = 'GeneralDiscussion.Rmd'}
```

\newpage
# References

```{r create_r-references}
r_refs(file = "r-references.bib")
```

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

