---
title             : "Working memory capacity in a change detection task is effected by the number of irrelevant objects in the display"
shorttitle        : "Effects of distractor number on change detection"

author: 
  - name          : "Dion T. Henare"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "School of Psychology, University of Auckland, Private Bag 92019, Auckland 1010, New Zealand"
    email         : "dion.henare@auckland.ac.nz"
  - name          : "Paul M. Corballis"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "School of Psychology, Univeristy of Auckland"

author_note: |
  School of Psychology, University of Auckland, Private Bag 92019, Auckland 1010, New Zealand

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.
  
keywords          : "working memory capacity, change detection, delayed matching to sample, distraction, filtering"
wordcount         : "X"

bibliography      : ["WMBehav-references.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no

class             : "man"
output            : papaja::apa6_pdf
---

```{r load_packages, include = FALSE}
library("papaja")
#library(plyr)
library(dplyr)
library(ggplot2)
library(afex)
library(knitr)
```

```{r helper_functions, include=FALSE, echo=FALSE}
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
    library(plyr)

    # New version of length which can handle NA's: if na.rm==T, don't count them
    length2 <- function (x, na.rm=FALSE) {
        if (na.rm) sum(!is.na(x))
        else       length(x)
    }

    # This does the summary. For each group's data frame, return a vector with
    # N, mean, and sd
    datac <- ddply(data, groupvars, .drop=.drop,
      .fun = function(xx, col) {
        c(N    = length2(xx[[col]], na.rm=na.rm),
          mean = mean   (xx[[col]], na.rm=na.rm),
          sd   = sd     (xx[[col]], na.rm=na.rm)
        )
      },
      measurevar
    )

    # Rename the "mean" column    
    datac <- rename(datac, c("mean" = measurevar))

    datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean

    # Confidence interval multiplier for standard error
    # Calculate t-statistic for confidence interval: 
    # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
    ciMult <- qt(conf.interval/2 + .5, datac$N-1)
    datac$ci <- datac$se * ciMult

    return(datac)
}
```

```{r load_raw_data, incude = FALSE}
#Find all files
filePath <- "P:/dhen061/WMBehav-RawFolder/data/"
files <- list.files(path = filePath, pattern = ".csv")
#load the first one and get the variable names
allData <- read.csv(file=paste(filePath,files[1], sep=""), header=TRUE, sep=",")
allData <- subset(allData, select = c(targetColour, DistNum, matchType, targetNum, CorrAns, key_resp_2.keys, key_resp_2.rt))
#delete data so we just have a dataframe with the relevant variables
allData <- allData[0,]
#set PID to 1
pid = 1

#Loop through the files, load them , and if there are 720 (as should be the case), add the PID and append to dataframe
for (file in files){
  curData <- read.csv(file=paste(filePath,file, sep=""), header=TRUE, sep=",")
  curData <- filter(curData,  !is.na(curData$trials.thisRepN))
  curData <- subset(curData, select = c(targetColour, DistNum, matchType, targetNum, CorrAns, key_resp_2.keys, key_resp_2.rt))
  if (nrow(curData) == 720) {
    curData$PID <- pid
    allData <- rbind(allData,curData)
    pid = pid+1
  } else {
    #If file doesn't have 720 rows, print the name
    #print(file)
  }
}
```

```{r tidy_data, include = FALSE}
#Tidy the data, remove non-response trials, and calculate correct response column
allData <- filter(allData, !allData$key_resp_2.keys=="None")
allData$CorrAns <- factor(allData$CorrAns)
allData$key_resp_2.keys <- factor(allData$key_resp_2.keys)
allData$correctResponse <- as.integer(allData$CorrAns==allData$key_resp_2.keys)

#Participant rejection
participants <- group_by(allData,PID)
numberOfTrials <- summarise(participants, nrow=NROW(correctResponse))
#Which participants have less than 700 trials meaning over 20 non-responses
nonRespFails <- numberOfTrials$PID[numberOfTrials$nrow<695]
#remove failed participants
for (subj in 1:length(nonRespFails)) {
  allData <- allData[!allData$PID==nonRespFails[subj],]
}
#Which participnats have <60% accuracy in 2 targ 0 dist condition
easyCond <- filter(allData, targetNum==2 & DistNum==0)
easyAccuracy <- summarise(group_by(easyCond,PID), avg=mean(correctResponse))
accuracyFails <- easyAccuracy$PID[easyAccuracy$avg<0.60]
for (subj in 1:length(accuracyFails)) {
  allData <- allData[!allData$PID==accuracyFails[subj],]
}
#check remaining
summary(as.factor(allData$PID))
length(summary(as.factor(allData$PID)))
```

```{r create_measure, include = FALSE}
#Create hits column and FA column
allData$hits <- as.integer(allData$CorrAns=="m" & allData$key_resp_2.keys=="m")
allData$FA <- as.integer(allData$CorrAns=="x" & allData$key_resp_2.keys=="m")

#Create summary table
participants <- group_by(allData,PID, targetNum, DistNum)
#Get number of hits and false alarms and calculate pashlers K
#Apply loglinear approach to prevent Hit rate and FA rate of 1 or 0 (Hautus,1995)
summaryTable <- summarise(participants, correctResponse=mean(correctResponse)*100, hits=sum(hits)+0.5, fa=sum(FA)+0.5, possHits=sum(as.integer(CorrAns=="m"))+1, possFA=sum(as.integer(CorrAns=="x"))+1)
summaryTable$hitProp <- summaryTable$hits/summaryTable$possHits
summaryTable$faProp <- summaryTable$fa/summaryTable$possFA
#calculate capacity pashlers K
summaryTable$pashlerK <- summaryTable$targetNum*((summaryTable$hitProp-summaryTable$faProp)/(1-summaryTable$faProp))

#Separate fixed and variable blocks
fixNames <- c("0", "2","4","6")
fixed.Vals <- filter(summaryTable, DistNum %in% fixNames)
varNames <- c("targEqual","targOpp")
var.Vals <- filter(summaryTable, DistNum %in% varNames)
var.Vals$numDist <- ifelse(var.Vals$DistNum=="targEqual",var.Vals$targetNum,8-var.Vals$targetNum)
var.Vals$Block <- var.Vals$DistNum
#fix up factors in fix v var mat
fixVmat.Vals <- filter(summaryTable, DistNum == "targEqual" | (DistNum=="2" & targetNum==2) | (DistNum=="4" & targetNum==4)  | (DistNum=="6" & targetNum==6))
fixVmat.Vals$numDist <- fixVmat.Vals$DistNum
fixVmat.Vals$numDist[fixVmat.Vals$DistNum=="targEqual"] <- fixVmat.Vals$targetNum[fixVmat.Vals$DistNum=="targEqual"]
fixVmat.Vals$Block <- fixVmat.Vals$DistNum
levels(fixVmat.Vals$Block) <- c(levels(fixVmat.Vals$Block),"fixed")
fixVmat.Vals$Block[fixVmat.Vals$Block!="targEqual"] <- 'fixed'
fixVmat.Vals$Block <- factor(fixVmat.Vals$Block)
fixVmat.Vals$numDist <- factor(fixVmat.Vals$numDist)
#Fix up factors in fix v var opp
fixVopp.Vals <- filter(summaryTable, DistNum == "targOpp" | (DistNum=="2" & targetNum==6) | (DistNum=="4" & targetNum==4)  | (DistNum=="6" & targetNum==2))
fixVopp.Vals$numDist <- fixVopp.Vals$DistNum
fixVopp.Vals$numDist[fixVopp.Vals$DistNum=="targOpp"] <- 8-fixVopp.Vals$targetNum[fixVopp.Vals$DistNum=="targOpp"]
fixVopp.Vals$Block <- fixVopp.Vals$DistNum
levels(fixVopp.Vals$Block) <- c(levels(fixVopp.Vals$Block),"fixed")
fixVopp.Vals$Block[fixVopp.Vals$Block!="targOpp"] <- 'fixed'
fixVopp.Vals$Block <- factor(fixVopp.Vals$Block)
```

# Introduction
Woring memory is central to functioning and important for stuff like fluid intelligence, attention, IQ or whatever.

change detection tasks are popular for measuring WM capacity across individuals. (basic outline, increasing popularity, benefits).

Many variations in change detection tasks. Pashler vs Cowan.

working memory related to attention and specificaly distractor filtering things.

Estimates of capacity may be effected by the number of distractors that are presented in the change detection task - our study.

trial-to-trial context effets working memory so distractor effect may also be mediated by context - our study.

# Methods

## Participants

62 individuals participated. One participant did not complete the entire task and was therefore excluded from analysis. Five participants were deemed not to have performed the task properly (3 had over 25 non-responses, and two had less than 60% accuracy on a set size of two with no distractors). Leaving us with 56 individuals to be included in the analysis.

# Results

## Accuracy

### Fixed distractor blocks
```{r accuracy_fixedonly_targets, include=FALSE, echo=FALSE}
accuracy.fixedonly.targanddist.aov <- aov_ez(
  data = fixed.Vals,
  dv = "correctResponse",
  id = "PID", 
  within = c("targetNum","DistNum")
)
summary(accuracy.fixedonly.targanddist.aov)
#Interaction
accuracy.fixedonly.targanddist.targXdistk <- pairs(emmeans(accuracy.fixedonly.targanddist.aov, ~ targetNum|DistNum))
accuracy.fixedonly.targanddist.distXtarg <- pairs(emmeans(accuracy.fixedonly.targanddist.aov, ~ DistNum|targetNum))
#Interaction table
summary(accuracy.fixedonly.targanddist.targXdistk)
summary(accuracy.fixedonly.targanddist.distXtarg)
#Plot data
accuracy.targXdist.violin <- ggplot(data=fixed.Vals, aes( x=DistNum,y=correctResponse)) +
  geom_violin( position = position_dodge(width = 1), scale = "width", fill="gray") +
  geom_boxplot(width=0.1, position = position_dodge(width = 1)) +
  scale_y_continuous(name ="Accuracy (%)") +
  facet_grid(.~targetNum) +
  theme_apa()

plotData <- summarySE(fixed.Vals, measurevar="correctResponse", groupvars=c("targetNum","DistNum"))

accuracy.targXdist.bar <- ggplot(plotData, aes( x=DistNum,y=correctResponse)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  facet_grid(.~targetNum) +
  geom_errorbar(aes(ymin=correctResponse-se, ymax=correctResponse+se), size=0.5,   
    width=.25,position=position_dodge(.9)) +
  facet_grid(~targetNum, labeller = as_labeller(c(`2`="Set size 2", `4`="Set size 4", `6`="Set size 6"))) +
  scale_y_continuous("Accuracy (%)",expand = c(0, 0), limits=c(0,100)) +
  scale_x_discrete("Number of distractors") +
  theme_apa()

pdf("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_accuracytargXdistPlot.pdf", width = 7, paper = "special")
accuracy.targXdist.bar
dev.off()
```

Interaction between target number and dist number. Set size 2 > set size 4 > set size 6. For set size 2 there are no differences between dist num blocks. For est size 4 0 is different from 4 and 6 and approaching for 2. For set size 6, 0 is diff from 4 and 6, 2 is diff from 4. Figure\ \@ref(fig:accuracytargXdistPlot)

```{r accuracytargXdistPlot, fig.cap = "Participant accuracy as a function of set size and number of distractors present at encoding and retrieval.", fig.align = "center"}
include_graphics("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_accuracytargXdistPlot.pdf", auto_pdf = TRUE)
```

### Fixed distractor vs variable distractor blocks
#### Fixed vs targEqual
```{r accuracy_fixVopp_distractors, include=FALSE, echo=FALSE}
accuracy.fixVmatch.distractors.aov <- aov_ez(
  data = fixVmat.Vals,
  dv = "correctResponse",
  id = "PID", 
  within = c("numDist", "Block")
)
summary(accuracy.fixVmatch.distractors.aov)
#Interaction
accuracy.fixVmatch.distractors.distXblock <- pairs(emmeans(accuracy.fixVmatch.distractors.aov, ~ numDist|Block))
accuracy.fixVmatch.distractors.blockXdist <- pairs(emmeans(accuracy.fixVmatch.distractors.aov, ~ Block|numDist))
#Interaction table
summary(accuracy.fixVmatch.distractors.distXblock)
summary(accuracy.fixVmatch.distractors.blockXdist)
#Plot data
accuracy.fixVmat.violin <- ggplot(data=fixVmat.Vals, aes( x=Block,y=correctResponse)) +
  geom_violin( position = position_dodge(width = 1), scale = "width") +
  #scale_fill_manual(values=c("#FFFFFF", "#999999")) +
  geom_boxplot(width=0.1, position = position_dodge(width = 1)) +
  scale_y_continuous(name ="Accuracy (%)") +
  facet_grid(.~numDist) +
  theme_apa()

pdf("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_accuracyfixvmatPlot.pdf", width = 7, paper = "special")
accuracy.fixVmat.violin
dev.off()
```

Interaction between block and distnum. within block type, accuracy graded with distnum. For distnum 2 and 4 no difference between block types. For dist 6, targEqual more accurate than fixed equivalent.

#### Fixed vs targOpp
```{r accuracy_fixVmat_distractors, include=FALSE, echo=FALSE}
accuracy.fixVopp.distractors.aov <- aov_ez(
  data = fixVopp.Vals,
  dv = "correctResponse",
  id = "PID", 
  within = c("numDist", "Block")
)
summary(accuracy.fixVopp.distractors.aov)
#Interaction
accuracy.fixVopp.distractors.distmain <- pairs(emmeans(accuracy.fixVopp.distractors.aov, ~ numDist))
summary(accuracy.fixVopp.distractors.distmain)

#Plot data
accuracy.fixVopp.violin <- ggplot(data=fixVopp.Vals, aes( x=Block,y=correctResponse)) +
  geom_violin( position = position_dodge(width = 1), scale = "width", fill="gray") +
  geom_boxplot(width=0.1, position = position_dodge(width = 1)) +
  scale_y_continuous(name ="Accuracy (%)") +
  facet_grid(.~numDist) +
  theme_apa()

pdf("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_accuracyfixvoppPlot.pdf", width = 7, paper = "special")
accuracy.fixVopp.violin
dev.off()
```

Main effect of distnum, as distnum increases accuracy goes up (because set size is going down).

## Capacity

### Fixed distractors

#### Targets

```{r capacity_fixedonly_targets, include = FALSE, echo=FALSE}
capacity.fixedonly.targets.aov <- aov_ez(
  data = fixed.Vals,
  dv = "pashlerK",
  id = "PID", 
  within = "targetNum"
)
summary(capacity.fixedonly.targets.aov)
capacity.fixedonly.targets.targmain <- pairs(emmeans(capacity.fixedonly.targets.aov, ~ targetNum))
summary(capacity.fixedonly.targets.targmain)
```

Results show that as number of targets increases, capacity estimates increase as well (2 sig> 4 sig> 6). This is a feature of the math used to calculate capacity where estimates are limited to half of the number of targets displayed. This means that as number of targets increases, we are able to estimate higher values for capacity and this is reflected in the results here. It's not that capacity is increased in trials with more targets, it's that we are able to estimate larger capacities in trials with more targets.

#### Distractors
```{r fcapacity_fixedonly_distractors, include = FALSE, echo=FALSE}
capacity_fixedonly_distractors.aov <- aov_ez(
  data = fixed.Vals,
  dv = "pashlerK",
  id = "PID", 
  within = c("DistNum")
)
summary(capacity_fixedonly_distractors.aov)
capacity.fixedonly.targets.distmain <- pairs(emmeans(capacity_fixedonly_distractors.aov, ~ DistNum))
summary(capacity.fixedonly.targets.distmain)

#Plot data
capacity.distractors.violin <- ggplot(data=fixed.Vals, aes( x=DistNum,y=pashlerK)) +
  geom_violin( position = position_dodge(width = 1), scale = "width", fill="gray") + 
  geom_boxplot(width=0.1, position = position_dodge(width = 1)) +
  scale_y_continuous(name ="Capacity (K)" ) +
  theme_apa()
```

Results show that when distractors are added to the encoding and retrieval displays, capacity estimates drop. The effect is graded where 0 dist is not sig diff from 2 dist but 0 is signif diff from 4 and 6 dist. 2 dist is sig diff from 4 and 6 dist. There is no sig diff between 4 and 6 dist. (as dist number increases, capacity estimates are dropping)

### Variable distractors

#### Targets

```{r capacity_variableonly_targets,include = FALSE, echo=FALSE}
capacity.variableonly.targets.aov <- aov_ez(
  data = var.Vals,
  dv = "pashlerK",
  id = "PID", 
  within = c("targetNum","Block")
)
summary(capacity.variableonly.targets.aov)
capacity.variableonly.targets.targmain <- pairs(emmeans(capacity.variableonly.targets.aov, ~ targetNum))
summary(capacity.variableonly.targets.targmain)
```

Main effect of target, 2 < 4 < 6

#### Distractors

```{r capacity_variableonly_distractors,include = FALSE, echo=FALSE}
capacity.variableonly.distractors.aov <- aov_ez(
  data = var.Vals,
  dv = "pashlerK",
  id = "PID", 
  within = c("numDist","Block")
)
summary(capacity.variableonly.distractors.aov)
#Interaction
capacity.variableonly.distractors.distXblock <- pairs(emmeans(capacity.variableonly.distractors.aov, ~ numDist|Block))
capacity.variableonly.distractors.blockXdist <- pairs(emmeans(capacity.variableonly.distractors.aov, ~ Block|numDist))
#Interaction table
summary(capacity.variableonly.distractors.distXblock)
summary(capacity.variableonly.distractors.blockXdist)
```

Interaction between dist number and block context. For targEqual 2<4<6 and for targopp 2>4>6. for dist 2, block diff is sig (euqla <opp), for 4 it isn't, for 6 it is (equal > opp).

### Fixed vs. variable distractor blocks (block context effect)
Now we wanna test whether there is a difference between having distractor number fixed across a block, versus varying trial by trial within a block. We compared trial types which were identical in terms of number of targets and distractors but differed with respect to whether they ocurred in a block where distractor number was fixed or variable. There were two types of variable blocks. One in which the number of distractors always matched the number of targets within the block (ie, 2 targets with 2 distractors, 4 targets with 4 distractors, or 6 targets with 6 distractors). We refer to this as the match distractor block. In the other, the total number of objec ts on screen was fixed across the block and therefore the number of distractors was always the inverse of the number of target (ie, 2 targets with 6 distractors, 4 targets with 4 distractors, or 6 targets with 2 distractors). We refer to this as the inverse distractor block. A separate analysis was performed in order to compare the match distractor block with the fixed condition, and the inverse distractor block with the fixed condition.

#### Fixed vs. matched block

```{r capacity_fixVmatch_distractors,include = FALSE, echo=FALSE}
capacity.fixVmatch.distractors.aov <- aov_ez(
  data = fixVmat.Vals,
  dv = "pashlerK",
  id = "PID", 
  within = c("numDist", "Block")
)
summary(capacity.fixVmatch.distractors.aov)
#Interaction
capacity.fixVmatch.distractors.distXblock <- pairs(emmeans(capacity.fixVmatch.distractors.aov, ~ numDist|Block))
capacity.fixVmatch.distractors.blockXdist <- pairs(emmeans(capacity.fixVmatch.distractors.aov, ~ Block|numDist))
#Interaction table
summary(capacity.fixVmatch.distractors.distXblock)
summary(capacity.fixVmatch.distractors.blockXdist)

#Plot  facet grid style
fixVmat.violin.facet <- ggplot(data=fixVmat.Vals, aes( x=Block,y=pashlerK)) +
  geom_violin( position = position_dodge(width = 1), scale = "width") +
  #scale_fill_manual(values=c("#FFFFFF", "#999999")) +
  geom_boxplot(width=0.1, position = position_dodge(width = 1)) +
  scale_y_continuous(name ="Accuracy (%)") +
  facet_grid(.~numDist) +
  theme_apa()

#Plot data
fixVmat.violin <- ggplot(data=fixVmat.Vals, aes( x=numDist,y=pashlerK, fill=Block)) +
  geom_violin( position = position_dodge(width = 1), scale = "width") +
  scale_fill_manual(values=c("#FFFFFF", "#999999")) +
  geom_boxplot(width=0.1, position = position_dodge(width = 1)) +
  scale_y_continuous(name ="Capacity (K)",limits = c(-2, 6)) +
  theme_apa()

```

Results show an interaction between block context and distractor effect. For variable, 2<4<6, for fixed, 2<4, 2<6, 4=6. for dist 2, no diff between block, for dist 4, no diff between block, for dist 6, var>fixed 

#### Fixed vs. opposite block
```{r capacity_fixVopp_distractors,include = FALSE, echo=FALSE}
capacity.fixVopp.distractors.aov <- aov_ez(
  data = fixVopp.Vals,
  dv = "pashlerK",
  id = "PID", 
  within = c("numDist","Block")
)
summary(capacity.fixVopp.distractors.aov)

capacity.fixVopp.distractors.distmain <- pairs(emmeans(capacity.fixVopp.distractors.aov, ~ numDist))
summary(capacity.fixVopp.distractors.distmain)

#Plot data
fixVopp.violin <- ggplot(data=fixVopp.Vals, aes( x=numDist,y=pashlerK, fill=Block)) +
  geom_violin( position = position_dodge(width = 1), scale = "width") +
  scale_fill_manual(values=c("#FFFFFF", "#999999")) +
  geom_boxplot(width=0.1, position = position_dodge(width = 1)) +
  scale_y_continuous(name ="Capacity (K)",limits = c(-2, 6)) +
  theme_apa()
```

Main effect of dist. 2>4>6

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
