---
title             : "Working memory capacity in a change detection task is effected by the number of irrelevant objects in the display"
shorttitle        : "Effects of distractor number on change detection"

author: 
  - name          : "Dion T. Henare"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "School of Psychology, University of Auckland, Private Bag 92019, Auckland 1010, New Zealand"
    email         : "dion.henare@auckland.ac.nz"
  - name          : "Paul M. Corballis"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "School of Psychology, Univeristy of Auckland"

author_note: |
  School of Psychology, University of Auckland, Private Bag 92019, Auckland 1010, New Zealand

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.
  
keywords          : "working memory capacity, change detection, delayed matching to sample, distraction, filtering"
wordcount         : "X"

bibliography      : ["WMBehav-references.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no

class             : "man"
output            : papaja::apa6_pdf
---

```{r load_packages, include = FALSE}
library("papaja")
#library(plyr)
library(dplyr)
library(ggplot2)
library(afex)
library(knitr)
library(xtable)
library(caTools) #split-half data
```

```{r helper_functions, include=FALSE, echo=FALSE}
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
    library(plyr)

    # New version of length which can handle NA's: if na.rm==T, don't count them
    length2 <- function (x, na.rm=FALSE) {
        if (na.rm) sum(!is.na(x))
        else       length(x)
    }

    # This does the summary. For each group's data frame, return a vector with
    # N, mean, and sd
    datac <- ddply(data, groupvars, .drop=.drop,
      .fun = function(xx, col) {
        c(N    = length2(xx[[col]], na.rm=na.rm),
          mean = mean   (xx[[col]], na.rm=na.rm),
          sd   = sd     (xx[[col]], na.rm=na.rm)
        )
      },
      measurevar
    )

    # Rename the "mean" column    
    datac <- rename(datac, c("mean" = measurevar))

    datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean

    # Confidence interval multiplier for standard error
    # Calculate t-statistic for confidence interval: 
    # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
    ciMult <- qt(conf.interval/2 + .5, datac$N-1)
    datac$ci <- datac$se * ciMult

    return(datac)
}
```

```{r load_raw_data, incude = FALSE, echo=FALSE}
#Find all files
filePath <- "P:/dhen061/WMBehav-RawFolder/data/"
files <- list.files(path = filePath, pattern = ".csv")
#load the first one and get the variable names
allData <- read.csv(file=paste(filePath,files[1], sep=""), header=TRUE, sep=",")
demoData <- subset(allData, select = c(X2..Age,X1..Sex))
demoData$X1..Sex <- as.character(demoData$X1..Sex)
allData <- subset(allData, select = c(targetColour, DistNum, matchType, targetNum, CorrAns, key_resp_2.keys, key_resp_2.rt))
#delete data so we just have a dataframe with the relevant variables
allData <- allData[0,]
demoData <- demoData[0,]
#set PID to 1
pid = 1

#Loop through the files, load them , and if there are 720 (as should be the case), add the PID and append to dataframe
for (file in files){
  curData <- read.csv(file=paste(filePath,file, sep=""), header=TRUE, sep=",")
  curData <- filter(curData,  !is.na(curData$trials.thisRepN))
  curDemo <- subset(curData, select = c(X2..Age,X1..Sex))
  curDemo$X1..Sex <- as.character(curDemo$X1..Sex)
  curData <- subset(curData, select = c(targetColour, DistNum, matchType, targetNum, CorrAns, key_resp_2.keys, key_resp_2.rt))
  if (nrow(curData) == 720) {
    curData$PID <- pid
    curDemo$PID <- pid
    allData <- rbind(allData,curData)
    demoData <- rbind(demoData,curDemo[1,])
    pid = pid+1
  } else {
    #If file doesn't have 720 rows, print the name
    #print(file)
  }
}
```

```{r tidy_data, include = FALSE}
#Tidy the data, remove non-response trials, and calculate correct response column
allData <- filter(allData, !allData$key_resp_2.keys=="None")
allData$CorrAns <- factor(allData$CorrAns)
allData$key_resp_2.keys <- factor(allData$key_resp_2.keys)
allData$correctResponse <- as.integer(allData$CorrAns==allData$key_resp_2.keys)
#Spit half the data
sample = sample.split(allData$correctResponse, SplitRatio = 0.5)
odd = subset(allData, sample == TRUE)
even = subset(allData, sample == FALSE)

#Participant rejection
participants <- group_by(allData,PID)
numberOfTrials <- summarise(participants, nrow=NROW(correctResponse))
#Which participants have less than 700 trials meaning over 20 non-responses
nonRespFails <- numberOfTrials$PID[numberOfTrials$nrow<695]
if (!is.null(nonRespFails)) {
#remove failed participants
for (subj in 1:length(nonRespFails)) {
  allData <- allData[!allData$PID==nonRespFails[subj],]
  demoData <- demoData[!demoData$PID==nonRespFails[subj],]
  odd <- odd[!odd$PID==nonRespFails[subj],]
  even <- even[!even$PID==nonRespFails[subj],]
}
}
#Which participnats have <60% accuracy in 2 targ 0 dist condition
easyCond <- filter(allData, targetNum==2 & DistNum==0)
easyAccuracy <- summarise(group_by(easyCond,PID), avg=mean(correctResponse))
accuracyFails <- easyAccuracy$PID[easyAccuracy$avg<0.60]
if (!is.null(accuracyFails)) {
for (subj in 1:length(accuracyFails)) {
  allData <- allData[!allData$PID==accuracyFails[subj],]
  demoData <- demoData[!demoData$PID==accuracyFails[subj],]
  odd <- odd[!odd$PID==accuracyFails[subj],]
  even <- even[!even$PID==accuracyFails[subj],]
}
}
```

```{r create_measure, include = FALSE}
#Create hits column and FA column
allData$hits <- as.integer(allData$CorrAns=="m" & allData$key_resp_2.keys=="m")
allData$FA <- as.integer(allData$CorrAns=="x" & allData$key_resp_2.keys=="m")
odd$hits <- as.integer(odd$CorrAns=="m" & odd$key_resp_2.keys=="m")
odd$FA <- as.integer(odd$CorrAns=="x" & odd$key_resp_2.keys=="m")
even$hits <- as.integer(even$CorrAns=="m" & even$key_resp_2.keys=="m")
even$FA <- as.integer(even$CorrAns=="x" & even$key_resp_2.keys=="m")

#Create summary table
participants <- group_by(allData,PID, targetNum, DistNum)
#Get number of hits and false alarms and calculate pashlers K
#Apply loglinear approach to prevent Hit rate and FA rate of 1 or 0 (Hautus,1995)
summaryTable <- summarise(participants, correctResponse=mean(correctResponse)*100, hits=sum(hits)+0.5, fa=sum(FA)+0.5, possHits=sum(as.integer(CorrAns=="m"))+1, possFA=sum(as.integer(CorrAns=="x"))+1)
summaryTable$hitProp <- summaryTable$hits/summaryTable$possHits
summaryTable$faProp <- summaryTable$fa/summaryTable$possFA
#calculate capacity pashlers K
summaryTable$pashlerK <- summaryTable$targetNum*((summaryTable$hitProp-summaryTable$faProp)/(1-summaryTable$faProp))

#Repeat calculations for split half data
oddParticipants <- group_by(odd,PID, targetNum)
oddTable <- summarise(oddParticipants, correctResponse=mean(correctResponse)*100, hits=sum(hits)+0.5, fa=sum(FA)+0.5, possHits=sum(as.integer(CorrAns=="m"))+1, possFA=sum(as.integer(CorrAns=="x"))+1)
oddTable$hitProp <- oddTable$hits/oddTable$possHits
oddTable$faProp <- oddTable$fa/oddTable$possFA
oddTable$pashlerK <- oddTable$targetNum*((oddTable$hitProp-oddTable$faProp)/(1-oddTable$faProp))

evenParticipants <- group_by(even,PID, targetNum)
evenTable <- summarise(evenParticipants, correctResponse=mean(correctResponse)*100, hits=sum(hits)+0.5, fa=sum(FA)+0.5, possHits=sum(as.integer(CorrAns=="m"))+1, possFA=sum(as.integer(CorrAns=="x"))+1)
evenTable$hitProp <- evenTable$hits/evenTable$possHits
evenTable$faProp <- evenTable$fa/evenTable$possFA
evenTable$pashlerK <- evenTable$targetNum*((evenTable$hitProp-evenTable$faProp)/(1-evenTable$faProp))

#Separate fixed and variable blocks
fixNames <- c("0", "2","4","6")
fixed.Vals <- filter(summaryTable, DistNum %in% fixNames)
varNames <- c("targEqual","targOpp")
var.Vals <- filter(summaryTable, DistNum %in% varNames)
var.Vals$numDist <- ifelse(var.Vals$DistNum=="targEqual",var.Vals$targetNum,8-var.Vals$targetNum)
var.Vals$Block <- var.Vals$DistNum
#fix up factors in fix v var mat
fixVmat.Vals <- filter(summaryTable, DistNum == "targEqual" | (DistNum=="2" & targetNum==2) | (DistNum=="4" & targetNum==4)  | (DistNum=="6" & targetNum==6))
fixVmat.Vals$numDist <- fixVmat.Vals$DistNum
fixVmat.Vals$numDist[fixVmat.Vals$DistNum=="targEqual"] <- fixVmat.Vals$targetNum[fixVmat.Vals$DistNum=="targEqual"]
fixVmat.Vals$Block <- fixVmat.Vals$DistNum
levels(fixVmat.Vals$Block) <- c(levels(fixVmat.Vals$Block),"fixed")
fixVmat.Vals$Block[fixVmat.Vals$Block!="targEqual"] <- 'fixed'
fixVmat.Vals$Block <- factor(fixVmat.Vals$Block)
fixVmat.Vals$numDist <- factor(fixVmat.Vals$numDist)
#Fix up factors in fix v var opp
fixVopp.Vals <- filter(summaryTable, DistNum == "targOpp" | (DistNum=="2" & targetNum==6) | (DistNum=="4" & targetNum==4)  | (DistNum=="6" & targetNum==2))
fixVopp.Vals$numDist <- fixVopp.Vals$DistNum
fixVopp.Vals$numDist[fixVopp.Vals$DistNum=="targOpp"] <- 8-fixVopp.Vals$targetNum[fixVopp.Vals$DistNum=="targOpp"]
fixVopp.Vals$Block <- fixVopp.Vals$DistNum
levels(fixVopp.Vals$Block) <- c(levels(fixVopp.Vals$Block),"fixed")
fixVopp.Vals$Block[fixVopp.Vals$Block!="targOpp"] <- 'fixed'
fixVopp.Vals$Block <- factor(fixVopp.Vals$Block)
```

# Introduction

Working memory is a term used to describe the active maintenance of information for brief periods of time. It is well known that there are limits to the amount of information that can be stored, and that an individual's working memory capacity is associated with a range of other important cognitive abilities. Individuals with larger working memory capacities have been shown to have better long-term memory, language comprehension, problem solving, multi-tasking, emotion regulation, and higher general fluid intelligence. Working memory capacity has also been shown to predict real-world abilities such as hazard detection in drivers. The estimation of working memory capacity is therefore increasingly important for research in all of these cognitive domains, and recent evidence has shown that capacity estimates can vary depending not only on the general paradigm being used, but the details of that paradigm [Shipstead Engle, primary secondary stuff].
```
"long-term memory, language comprehension, and problem solving."
"multi-tasking (Hambrick, Oswald, Darowski, Rench, & Brou, 2010), emotion regulation (Kleider, Parrott, & King, 2009), hindsight bias (Calvillo, 2012), and susceptibility to stereotype threat (Hutchison, Smith, & Ferris, 2012). Perhaps most famously, working memory capacity shares at least half its statistical variance with general fluid intelligence (the ability to reason with novel information; Kane, Hambrick, & Conway, 2005)."
"WM capacity predicts attentional control, fluid intelligence, and real-world outcomes such as perceiving hazards while driving (Engle, Tuholski, Laughlin, & Conway, 1999; Fukuda, Vogel, Mayr, & Awh, 2010; Wood, Hartley, Furley, & Wilson, 2016)"
```

Change detection tasks are an increasingly popular way of measuring visual working memory capacity across individuals. Change detection involves the brief presentation of an encoding display, where a number of simple objects are shown on screen for the participant to encode. This is followed by a delay period where the participant must maintain the encoded information in working memory, and then a retrieval probe is presented. The participant must indicate whether or not the retrieval probe matches the encoded stimuli. Typically, set size (the number of objects that should be encoded) is varied across trials and performance is measured using either accuracy on the task, or by estimating capacity. Capacity is quantified for a given set size based on the proportion of hits (the number of correctly identified match probes), and the proportion of false alarms (the number of non-matches that are misidentified as matches). As a result of their short, simple structure, change detection tasks are well suited to use with developmental and clinical populations, as well as with neural recordings that require large trial numbers. Change detection tasks also translate well to paradigms used with non-human animals and taken together, these features have contributed to their rising popularity.
```
The reliability and stability of visual working memory capacity - for the benefits stuff.
How to measure working memory capacity in the change detection paradigm -for the measurement of capacity

```

Specific incarnations of the change detection paradigm can vary significantly in terms of the type of stimuli used, and the number of stimuli that are presented at both encoding and retrieval. Historically, one of the main ways that change detection tasks have varied is with regard to the number of probes presented on the retrieval display. In the single-probed retrieval version of the task, participants are shown only one of the encoded stimuli and must therefore indicate whether that specific object has changed in any way. In the whole-display retrieval version of the task however, the entire set of encoded stimuli are presented as probes and the participant must indicate whether any one of the stimuli have changed. Another way in which the task varies is with regard to the number of encode stimuli that need to be remembered. In some versions of the task, all of the objects presented during encoding must be remembered by the participant. In other versions of the task participants receive a cue ahead of the encoding display which indicates which subset of the encoding stimuli needs to be remembered. For example, participants may be cued to encode only the blue objects in an upcoming display which contains both blue and red stimuli. These features have been shown to effect not just the absolute capacity values reported, but the underlying cognitive mechanisms that are being tested.

One set of cognitive mechanisms that is especially important to consider when measuring working memory is selective attention. Converging evidence from both within and between-participant experiments now suggests that there is significant functional overlap between selective attention and working memory. When working memory load on an individual is increased, performance on a concurrent visual search task is impeded. Similarly, individuals who naturally possess a larger working memory capacity perform better on standard measures of attentional control like the Stroop task and the Eriksen flanker task. Modern accounts of working memory availability typically recognise this close association between attention and working memory by either incorporating elements of attentional control, or in some cases suggesting that attentional control is the primary determinant of working memory capacity. More specific investigations of this relationship using both behavioural and neural measures now suggest that it is specifically the ability to disengage from irrelevant distractors which differentiates high and low capacity individuals.

The critical role that distractor suppression plays in working memory performance raises questions around the effect that irrelevant objects may have in a change detection task. In our study, we used a cued, whole-display retrieval version of the change detection task while varying the number of distractors across blocks. This allowed us to measure the effect that distraction in the change detection task has on both participant accuracy, and estimates of individual capacity. Set size varied within each block however the number of distractors remained fixed in 4 conditions (ranging from 0 distractors to 6 distractors). We also included two conditions where the number of distractors varied within a block. In one of these variable conditions, the number of distractors was simply the same as the number of targets on a given trial. In the other variable block, we sought to keep the total number of objects on screen the same, and therefore the number of distractors was always inverse to the number of targets.

Woring memory is central to functioning and important for stuff like fluid intelligence, attention, IQ or whatever.

change detection tasks are popular for measuring WM capacity across individuals. (basic outline, increasing popularity, benefits).

Many variations in change detection tasks. Pashler vs Cowan.

working memory related to attention and specificaly distractor filtering things.

Estimates of capacity may be effected by the number of distractors that are presented in the change detection task - our study.

trial-to-trial context effets working memory so distractor effect may also be mediated by context - our study.

# Methods

## Participants
```{r demo_Analysis, echo=FALSE, include=FALSE}
demographics <- group_by(demoData,PID, X2..Age, X1..Sex)
#Get number of hits and false alarms and calculate pashlers K
#Apply loglinear approach to prevent Hit rate and FA rate of 1 or 0 (Hautus,1995)
demoTable <- summarise(demographics)
demoTable$X1..Sex <- toupper(substr(demoTable$X1..Sex,start=1,stop=1))
demoTable$X2..Age <- as.numeric(substr(demoTable$X2..Age,start=1,stop=2))
demoTable$SexBin <- ifelse(demoTable$X1..Sex=="F",1,0)

meanAge <- mean(demoTable$X2..Age)
sdAge <- sd(demoTable$X2..Age)
minAge <- min(demoTable$X2..Age)
maxAge <- max(demoTable$X2..Age)

totalSubj <- length(summary(as.factor(demoTable$PID)))
totalFemale <- sum(demoTable$SexBin)
```

62 individuals participated. One participant did not complete the entire task and was therefore excluded from analysis. Five participants were deemed not to have performed the task properly (3 had over 25 non-responses, and two had less than 60% accuracy on a set size of two with no distractors). Leaving us with 56 individuals (`r totalFemale` female) with an age range of `r minAge` to `r maxAge` (mean = `r meanAge` and sd = `r sdAge`) to be included in the analysis.

# Results

## Reliability
```{r reliability,echo=FALSE,include=FALSE}
oddVeven.cor <- cor(oddTable$pashlerK, evenTable$pashlerK)
```

We tested the internal reliability of the capacity measure (pashler's K) by performing a correlation on capacity measured from odd and even trials. The results show an r of 0.83

## Accuracy

### Fixed distractor blocks
```{r accuracy_fixedonly_targets, include=FALSE, echo=FALSE}
accuracy.fixedonly.targanddist.aov <- aov_ez(
  data = fixed.Vals,
  dv = "correctResponse",
  id = "PID", 
  within = c("targetNum","DistNum")
)
#Pairwise comparisons
accuracy.fixedonly.targanddist.targXdist <- pairs(emmeans(accuracy.fixedonly.targanddist.aov, ~ targetNum|DistNum))
accuracy.fixedonly.targanddist.distXtarg <- pairs(emmeans(accuracy.fixedonly.targanddist.aov, ~ DistNum|targetNum))

#Create tables
accuracy.fixedonly.targanddist.table <- apa_print(accuracy.fixedonly.targanddist.aov)
# FPairwise tables
accuracy.fixedonly.targanddist.targXdist.table <- xtable(summary(accuracy.fixedonly.targanddist.targXdist), caption = "Summary of the pairwise comparisons used to follow up the main interaction (accuracy)", label = "tab:accuracy.fixedonly.targanddist.targXdist.Table")
accuracy.fixedonly.targanddist.distXtarg.table <- xtable(summary(accuracy.fixedonly.targanddist.distXtarg), caption = "Summary of the pairwise comparisons used to follow up the main interaction (accuracy)", label = "tab:accuracy.fixedonly.targanddist.distXtarg.Table")

#Create plot
accuracy.targXdist.summarydata <- summarySE(fixed.Vals, measurevar="correctResponse", groupvars=c("targetNum","DistNum"))
accuracy.targXdist.bar <- ggplot(accuracy.targXdist.summarydata, aes( x=DistNum,y=correctResponse)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymin=correctResponse-se, ymax=correctResponse+se), size=0.5,   
    width=.25,position=position_dodge(.9)) +
  facet_grid(~targetNum, labeller = as_labeller(c(`2`="Set size 2", `4`="Set size 4", `6`="Set size 6"))) +
  scale_y_continuous("Accuracy (%)",expand = c(0, 0), limits=c(0,100)) +
  scale_x_discrete("Number of distractors") +
  theme_apa()
pdf("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_accuracytargXdistPlot.pdf", width = 7, paper = "special")
accuracy.targXdist.bar
dev.off()
```

Interaction between target number and dist number. Set size 2 > set size 4 > set size 6. For set size 2 there are no differences between dist num blocks. For est size 4 0 is different from 4 and 6 and approaching for 2. For set size 6, 0 is diff from 4 and 6, 2 is diff from 4. Figure\ \@ref(fig:accuracytargXdistPlot)

```{r accuracy_fixedonly_targanddist_table, results = 'asis'}
apa_table(accuracy.fixedonly.targanddist.table$table, caption = "Summary of the 3 x 4 repeated measures ANOVA used to test the effects of set size and distractor number on participant accuracy in the working memory task.", escape = FALSE)
```

```{r accuracy_fixedOnly_pairwise, results = 'asis'}
print(accuracy.fixedonly.targanddist.targXdist.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
print(accuracy.fixedonly.targanddist.distXtarg.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
```

```{r accuracytargXdistPlot, fig.cap = "Participant accuracy as a function of set size and number of distractors present at encoding and retrieval.", fig.align = "center"}
include_graphics("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_accuracytargXdistPlot.pdf", auto_pdf = TRUE)
```

### Block context
#### Fixed vs targEqual
```{r accuracy_fixVopp_distractors, include=FALSE, echo=FALSE}
accuracy.fixVmatch.distractors.aov <- aov_ez(
  data = fixVmat.Vals,
  dv = "correctResponse",
  id = "PID", 
  within = c("numDist", "Block")
)
#Interaction
accuracy.fixVmatch.distractors.distXblock <- pairs(emmeans(accuracy.fixVmatch.distractors.aov, ~ numDist|Block))
accuracy.fixVmatch.distractors.blockXdist <- pairs(emmeans(accuracy.fixVmatch.distractors.aov, ~ Block|numDist))

#Create tables
accuracy.fixVmatch.distractors.table <- apa_print(accuracy.fixVmatch.distractors.aov)
#Create pairwise tables
accuracy.fixVmatch.distractors.distXblock.table <- xtable(summary(accuracy.fixVmatch.distractors.distXblock), caption = "Summary of the pairwise comparisons used to follow up the main interaction (accuracy)", label = "tab:accuracy.fixVmatch.distractors.distXblock.table")
accuracy.fixVmatch.distractors.blockXdist.table <- xtable(summary(accuracy.fixVmatch.distractors.blockXdist), caption = "Summary of the pairwise comparisons used to follow up the main interaction (accuracy)", label = "tab:accuracy.fixVmatch.distractors.blockXdist.table")

#Create plots
accuracy.fixVmat.summarydata <- summarySE(fixVmat.Vals, measurevar="correctResponse", groupvars=c("Block","numDist"))
accuracy.fixVmat.bar <- ggplot(accuracy.fixVmat.summarydata, aes( x=Block,y=correctResponse)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymin=correctResponse-se, ymax=correctResponse+se), size=0.5,   
    width=.25,position=position_dodge(.9)) +
  facet_grid(~numDist, labeller = as_labeller(c(`2`="2 distractors", `4`="4 distractors", `6`="6 distractors"))) +
  scale_y_continuous("Accuracy (%)",expand = c(0, 0), limits=c(0,100)) +
  scale_x_discrete("Block type") +
  theme_apa()
pdf("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_accuracyfixvmatPlot.pdf", width = 7, paper = "special")
accuracy.fixVmat.bar
dev.off()
```

Interaction between block and distnum. within block type, accuracy graded with distnum. For distnum 2 targequal <fixed, no diff for distnum4 or distnum 6 Figure\ \@ref(fig:accuracyfixVmatPlot)

```{r accuracy_fixVmatch_distractors_table, results = 'asis'}
apa_table(accuracy.fixVmatch.distractors.table$table, caption = "Summary of the 3 x 4 repeated measures ANOVA used to test the effects of set size and distractor number on participant accuracy in the working memory task.", escape = FALSE)
```

```{r accuracy_fixVmat_pairwise, results = 'asis'}
print(accuracy.fixVmatch.distractors.distXblock.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
print(accuracy.fixVmatch.distractors.blockXdist.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
```

```{r accuracyfixVmatPlot, fig.cap = "Participant accuracy as a function of set size and number of distractors present at encoding and retrieval.", fig.align = "center"}
include_graphics("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_accuracyfixVmatPlot.pdf", auto_pdf = TRUE)
```

#### Fixed vs targOpp
```{r accuracy_fixVmat_distractors, include=FALSE, echo=FALSE}
accuracy.fixVopp.distractors.aov <- aov_ez(
  data = fixVopp.Vals,
  dv = "correctResponse",
  id = "PID", 
  within = c("numDist", "Block")
)
#Interaction
accuracy.fixVopp.distractors.distmain <- pairs(emmeans(accuracy.fixVopp.distractors.aov, ~ numDist))

#create table
accuracy.fixVopp.distractors.table <- apa_print(accuracy.fixVopp.distractors.aov)
#Create followup table
accuracy.fixVopp.distractors.distmain.table <- xtable(summary(accuracy.fixVopp.distractors.distmain), caption = "Summary of the pairwise comparisons used to follow up the main interaction (accuracy)", label = "tab:accuracy.fixVopp.distractors.distmain.table")

#create plot
accuracy.fixVopp.summarydata <- summarySE(fixVopp.Vals, measurevar="correctResponse", groupvars=c("Block","numDist"))
accuracy.fixVopp.bar <- ggplot(accuracy.fixVopp.summarydata, aes( x=Block,y=correctResponse)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymin=correctResponse-se, ymax=correctResponse+se), size=0.5,   
    width=.25,position=position_dodge(.9)) +
  facet_grid(~numDist, labeller = as_labeller(c(`2`="2 distractors", `4`="4 distractors", `6`="6 distractors"))) +
  scale_y_continuous("Accuracy (%)",expand = c(0, 0), limits=c(0,100)) +
  scale_x_discrete("Block type") +
  theme_apa()
pdf("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_accuracyfixvoppPlot.pdf", width = 7, paper = "special")
accuracy.fixVopp.bar
dev.off()
```

Main effect of distnum, as distnum increases accuracy goes up (because set size is going down). Figure\ \@ref(fig:accuracyfixVoppPlot)

```{r accuracy_fixVopp_distractors_table, results = 'asis'}
apa_table(accuracy.fixVopp.distractors.table$table, caption = "Summary of the 2 x 4 repeated measures ANOVA used to test the effects of block type and distractor number on participant accuracy in the working memory task.", escape = FALSE)
```

```{r accuracy_fixVopp_pairwise, results = 'asis'}
print(accuracy.fixVopp.distractors.distmain.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
```

```{r accuracyfixVoppPlot, fig.cap = "Participant accuracy as a function of set size and number of distractors present at encoding and retrieval.", fig.align = "center"}
include_graphics("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_accuracyfixVoppPlot.pdf", auto_pdf = TRUE)
```
## Capacity
### Fixed distractor blocks
```{r capacity_fixedonly_targets, include=FALSE, echo=FALSE}
capacity.fixedonly.targanddist.aov <- aov_ez(
  data = fixed.Vals,
  dv = "pashlerK",
  id = "PID", 
  within = c("targetNum","DistNum")
)
#Pairwise comparisons
capacity.fixedonly.targanddist.targXdist <- pairs(emmeans(capacity.fixedonly.targanddist.aov, ~ targetNum|DistNum))
capacity.fixedonly.targanddist.distXtarg <- pairs(emmeans(capacity.fixedonly.targanddist.aov, ~ DistNum|targetNum))

#Create tables
capacity.fixedonly.targanddist.table <- apa_print(capacity.fixedonly.targanddist.aov)
# FPairwise tables
capacity.fixedonly.targanddist.targXdist.table <- xtable(summary(capacity.fixedonly.targanddist.targXdist), caption = "Summary of the pairwise comparisons used to follow up the main interaction (capacity)", label = "tab:capacity.fixedonly.targanddist.targXdist.Table")
capacity.fixedonly.targanddist.distXtarg.table <- xtable(summary(capacity.fixedonly.targanddist.distXtarg), caption = "Summary of the pairwise comparisons used to follow up the main interaction (capacity)", label = "tab:capacity.fixedonly.targanddist.distXtarg.Table")

#Create plot
capacity.targXdist.summarydata <- summarySE(fixed.Vals, measurevar="pashlerK", groupvars=c("targetNum","DistNum"))
capacity.targXdist.bar <- ggplot(capacity.targXdist.summarydata, aes( x=DistNum,y=pashlerK)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymin=pashlerK-se, ymax=pashlerK+se), size=0.5,   
    width=.25,position=position_dodge(.9)) +
  facet_grid(~targetNum, labeller = as_labeller(c(`2`="Set size 2", `4`="Set size 4", `6`="Set size 6"))) +
  scale_y_continuous("Capacity (%)",expand = c(0, 0)) +
  scale_x_discrete("Number of distractors") +
  theme_apa()
pdf("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_capacitytargXdistPlot.pdf", width = 7, paper = "special")
capacity.targXdist.bar
dev.off()
```

Interaction between target number and dist number. Set size 2 > set size 4 > set size 6. For set size 2 there are no differences between dist num blocks. For est size 4 0 is different from 4 and 6 and approaching for 2. For set size 6, 0 is diff from 4 and 6, 2 is diff from 4. Figure\ \@ref(fig:capacitytargXdistPlot)

```{r capacity_fixedonly_targanddist_table, results = 'asis'}
apa_table(capacity.fixedonly.targanddist.table$table, caption = "Summary of the 3 x 4 repeated measures ANOVA used to test the effects of set size and distractor number on participant capacity in the working memory task.", escape = FALSE)
```

```{r capacity_fixedOnly_pairwise, results = 'asis'}
print(capacity.fixedonly.targanddist.targXdist.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
print(capacity.fixedonly.targanddist.distXtarg.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
```

```{r capacitytargXdistPlot, fig.cap = "Participant capacity as a function of set size and number of distractors present at encoding and retrieval.", fig.align = "center"}
include_graphics("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_capacitytargXdistPlot.pdf", auto_pdf = TRUE)
```

### Fixed distractor vs variable distractor blocks
#### Fixed vs targEqual
```{r capacity_fixVopp_distractors, include=FALSE, echo=FALSE}
capacity.fixVmatch.distractors.aov <- aov_ez(
  data = fixVmat.Vals,
  dv = "pashlerK",
  id = "PID", 
  within = c("numDist", "Block")
)
#Interaction
capacity.fixVmatch.distractors.distXblock <- pairs(emmeans(capacity.fixVmatch.distractors.aov, ~ numDist|Block))
capacity.fixVmatch.distractors.blockXdist <- pairs(emmeans(capacity.fixVmatch.distractors.aov, ~ Block|numDist))

#Create tables
capacity.fixVmatch.distractors.table <- apa_print(capacity.fixVmatch.distractors.aov)
#Create pairwise tables
capacity.fixVmatch.distractors.distXblock.table <- xtable(summary(capacity.fixVmatch.distractors.distXblock), caption = "Summary of the pairwise comparisons used to follow up the main interaction (capacity)", label = "tab:capacity.fixVmatch.distractors.distXblock.table")
capacity.fixVmatch.distractors.blockXdist.table <- xtable(summary(capacity.fixVmatch.distractors.blockXdist), caption = "Summary of the pairwise comparisons used to follow up the main interaction (capacity)", label = "tab:capacity.fixVmatch.distractors.blockXdist.table")

#Create plots
capacity.fixVmat.summarydata <- summarySE(fixVmat.Vals, measurevar="pashlerK", groupvars=c("Block","numDist"))
capacity.fixVmat.bar <- ggplot(capacity.fixVmat.summarydata, aes( x=Block,y=pashlerK)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymin=pashlerK-se, ymax=pashlerK+se), size=0.5,   
    width=.25,position=position_dodge(.9)) +
  facet_grid(~numDist, labeller = as_labeller(c(`2`="2 distractors", `4`="4 distractors", `6`="6 distractors"))) +
  scale_y_continuous("Capacity (%)",expand = c(0, 0)) +
  scale_x_discrete("Block type") +
  theme_apa()
pdf("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_capacityfixvmatPlot.pdf", width = 7, paper = "special")
capacity.fixVmat.bar
dev.off()
```

Interaction between block and distnum. within block type, capacity graded with distnum. For distnum 2 and 4 no difference between block types. For dist 6, targEqual more accurate than fixed equivalent. Figure\ \@ref(fig:capacityfixVmatPlot)

```{r capacity_fixVmatch_distractors_table, results = 'asis'}
apa_table(capacity.fixVmatch.distractors.table$table, caption = "Summary of the 3 x 4 repeated measures ANOVA used to test the effects of set size and distractor number on participant capacity in the working memory task.", escape = FALSE)
```

```{r capacity_fixVmat_pairwise, results = 'asis'}
print(capacity.fixVmatch.distractors.distXblock.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
print(capacity.fixVmatch.distractors.blockXdist.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
```

```{r capacityfixVmatPlot, fig.cap = "Participant capacity as a function of set size and number of distractors present at encoding and retrieval.", fig.align = "center"}
include_graphics("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_capacityfixVmatPlot.pdf", auto_pdf = TRUE)
```

#### Fixed vs targOpp
```{r capacity_fixVmat_distractors, include=FALSE, echo=FALSE}
capacity.fixVopp.distractors.aov <- aov_ez(
  data = fixVopp.Vals,
  dv = "pashlerK",
  id = "PID", 
  within = c("numDist", "Block")
)
#Interaction
capacity.fixVopp.distractors.distmain <- pairs(emmeans(capacity.fixVopp.distractors.aov, ~ numDist))

#create table
capacity.fixVopp.distractors.table <- apa_print(capacity.fixVopp.distractors.aov)
#Create followup table
capacity.fixVopp.distractors.distmain.table <- xtable(summary(capacity.fixVopp.distractors.distmain), caption = "Summary of the pairwise comparisons used to follow up the main interaction (capacity)", label = "tab:capacity.fixVopp.distractors.distmain.table")

#create plot
capacity.fixVopp.summarydata <- summarySE(fixVopp.Vals, measurevar="pashlerK", groupvars=c("Block","numDist"))
capacity.fixVopp.bar <- ggplot(capacity.fixVopp.summarydata, aes( x=Block,y=pashlerK)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymin=pashlerK-se, ymax=pashlerK+se), size=0.5,   
    width=.25,position=position_dodge(.9)) +
  facet_grid(~numDist, labeller = as_labeller(c(`2`="2 distractors", `4`="4 distractors", `6`="6 distractors"))) +
  scale_y_continuous("Capacity (%)",expand = c(0, 0)) +
  scale_x_discrete("Block type") +
  theme_apa()
pdf("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_capacityfixvoppPlot.pdf", width = 7, paper = "special")
capacity.fixVopp.bar
dev.off()
```

Main effect of distnum, as distnum increases capacity goes up (because set size is going down). Figure\ \@ref(fig:capacityfixVoppPlot)

```{r capacity_fixVopp_distractors_table, results = 'asis'}
apa_table(capacity.fixVopp.distractors.table$table, caption = "Summary of the 2 x 4 repeated measures ANOVA used to test the effects of block type and distractor number on participant capacity in the working memory task.", escape = FALSE)
```

```{r capacity_fixVopp_pairwise, results = 'asis'}
print(capacity.fixVopp.distractors.distmain.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
```

```{r capacityfixVoppPlot, fig.cap = "Participant capacity as a function of set size and number of distractors present at encoding and retrieval.", fig.align = "center"}
include_graphics("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_capacityfixVoppPlot.pdf", auto_pdf = TRUE)
```



## Hits
### Fixed distractor blocks
```{r hits_fixedonly_targets, include=FALSE, echo=FALSE}
hits.fixedonly.targanddist.aov <- aov_ez(
  data = fixed.Vals,
  dv = "hitProp",
  id = "PID", 
  within = c("targetNum","DistNum")
)
#Pairwise comparisons
hits.fixedonly.targanddist.targXdist <- pairs(emmeans(hits.fixedonly.targanddist.aov, ~ targetNum|DistNum))
hits.fixedonly.targanddist.distXtarg <- pairs(emmeans(hits.fixedonly.targanddist.aov, ~ DistNum|targetNum))

#Create tables
hits.fixedonly.targanddist.table <- apa_print(hits.fixedonly.targanddist.aov)
# FPairwise tables
hits.fixedonly.targanddist.targXdist.table <- xtable(summary(hits.fixedonly.targanddist.targXdist), caption = "Summary of the pairwise comparisons used to follow up the main interaction (hits)", label = "tab:hits.fixedonly.targanddist.targXdist.Table")
hits.fixedonly.targanddist.distXtarg.table <- xtable(summary(hits.fixedonly.targanddist.distXtarg), caption = "Summary of the pairwise comparisons used to follow up the main interaction (hits)", label = "tab:hits.fixedonly.targanddist.distXtarg.Table")

#Create plot
hits.targXdist.summarydata <- summarySE(fixed.Vals, measurevar="hitProp", groupvars=c("targetNum","DistNum"))
hits.targXdist.bar <- ggplot(hits.targXdist.summarydata, aes( x=DistNum,y=hitProp)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymin=hitProp-se, ymax=hitProp+se), size=0.5,   
    width=.25,position=position_dodge(.9)) +
  facet_grid(~targetNum, labeller = as_labeller(c(`2`="Set size 2", `4`="Set size 4", `6`="Set size 6"))) +
  scale_y_continuous("Hits (%)",expand = c(0, 0)) +
  scale_x_discrete("Number of distractors") +
  theme_apa()
pdf("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_hitstargXdistPlot.pdf", width = 7, paper = "special")
hits.targXdist.bar
dev.off()
```

Interaction between target number and dist number. Set size 2 > set size 4 > set size 6. For set size 2 there are no differences between dist num blocks. For est size 4 0 is different from 4 and 6 and approaching for 2. For set size 6, 0 is diff from 4 and 6, 2 is diff from 4. Figure\ \@ref(fig:hitstargXdistPlot)

```{r hits_fixedonly_targanddist_table, results = 'asis'}
apa_table(hits.fixedonly.targanddist.table$table, caption = "Summary of the 3 x 4 repeated measures ANOVA used to test the effects of set size and distractor number on participant hits in the working memory task.", escape = FALSE)
```

```{r hits_fixedOnly_pairwise, results = 'asis'}
print(hits.fixedonly.targanddist.targXdist.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
print(hits.fixedonly.targanddist.distXtarg.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
```

```{r hitstargXdistPlot, fig.cap = "Participant hits as a function of set size and number of distractors present at encoding and retrieval.", fig.align = "center"}
include_graphics("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_hitstargXdistPlot.pdf", auto_pdf = TRUE)
```

### Fixed distractor vs variable distractor blocks
#### Fixed vs targEqual
```{r hits_fixVopp_distractors, include=FALSE, echo=FALSE}
hits.fixVmatch.distractors.aov <- aov_ez(
  data = fixVmat.Vals,
  dv = "hitProp",
  id = "PID", 
  within = c("numDist", "Block")
)
#Interaction
hits.fixVmatch.distractors.distXblock <- pairs(emmeans(hits.fixVmatch.distractors.aov, ~ numDist|Block))
hits.fixVmatch.distractors.blockXdist <- pairs(emmeans(hits.fixVmatch.distractors.aov, ~ Block|numDist))

#Create tables
hits.fixVmatch.distractors.table <- apa_print(hits.fixVmatch.distractors.aov)
#Create pairwise tables
hits.fixVmatch.distractors.distXblock.table <- xtable(summary(hits.fixVmatch.distractors.distXblock), caption = "Summary of the pairwise comparisons used to follow up the main interaction (hits)", label = "tab:hits.fixVmatch.distractors.distXblock.table")
hits.fixVmatch.distractors.blockXdist.table <- xtable(summary(hits.fixVmatch.distractors.blockXdist), caption = "Summary of the pairwise comparisons used to follow up the main interaction (hits)", label = "tab:hits.fixVmatch.distractors.blockXdist.table")

#Create plots
hits.fixVmat.summarydata <- summarySE(fixVmat.Vals, measurevar="hitProp", groupvars=c("Block","numDist"))
hits.fixVmat.bar <- ggplot(hits.fixVmat.summarydata, aes( x=Block,y=hitProp)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymin=hitProp-se, ymax=hitProp+se), size=0.5,   
    width=.25,position=position_dodge(.9)) +
  facet_grid(~numDist, labeller = as_labeller(c(`2`="2 distractors", `4`="4 distractors", `6`="6 distractors"))) +
  scale_y_continuous("Hits (%)",expand = c(0, 0)) +
  scale_x_discrete("Block type") +
  theme_apa()
pdf("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_hitsfixvmatPlot.pdf", width = 7, paper = "special")
hits.fixVmat.bar
dev.off()
```

Interaction between block and distnum. within block type, hits graded with distnum. For distnum 2 and 4 no difference between block types. For dist 6, targEqual more accurate than fixed equivalent. Figure\ \@ref(fig:hitsfixVmatPlot)

```{r hits_fixVmatch_distractors_table, results = 'asis'}
apa_table(hits.fixVmatch.distractors.table$table, caption = "Summary of the 3 x 4 repeated measures ANOVA used to test the effects of set size and distractor number on participant hits in the working memory task.", escape = FALSE)
```

```{r hits_fixVmat_pairwise, results = 'asis'}
print(hits.fixVmatch.distractors.distXblock.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
print(hits.fixVmatch.distractors.blockXdist.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
```

```{r hitsfixVmatPlot, fig.cap = "Participant hits as a function of set size and number of distractors present at encoding and retrieval.", fig.align = "center"}
include_graphics("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_hitsfixVmatPlot.pdf", auto_pdf = TRUE)
```

#### Fixed vs targOpp
```{r hits_fixVmat_distractors, include=FALSE, echo=FALSE}
hits.fixVopp.distractors.aov <- aov_ez(
  data = fixVopp.Vals,
  dv = "hitProp",
  id = "PID", 
  within = c("numDist", "Block")
)
#Interaction
hits.fixVopp.distractors.distmain <- pairs(emmeans(hits.fixVopp.distractors.aov, ~ numDist))

#create table
hits.fixVopp.distractors.table <- apa_print(hits.fixVopp.distractors.aov)
#Create followup table
hits.fixVopp.distractors.distmain.table <- xtable(summary(hits.fixVopp.distractors.distmain), caption = "Summary of the pairwise comparisons used to follow up the main interaction (hits)", label = "tab:hits.fixVopp.distractors.distmain.table")

#create plot
hits.fixVopp.summarydata <- summarySE(fixVopp.Vals, measurevar="hitProp", groupvars=c("Block","numDist"))
hits.fixVopp.bar <- ggplot(hits.fixVopp.summarydata, aes( x=Block,y=hitProp)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymin=hitProp-se, ymax=hitProp+se), size=0.5,   
    width=.25,position=position_dodge(.9)) +
  facet_grid(~numDist, labeller = as_labeller(c(`2`="2 distractors", `4`="4 distractors", `6`="6 distractors"))) +
  scale_y_continuous("Hits (%)",expand = c(0, 0)) +
  scale_x_discrete("Block type") +
  theme_apa()
pdf("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_hitsfixvoppPlot.pdf", width = 7, paper = "special")
hits.fixVopp.bar
dev.off()
```

Main effect of distnum, as distnum increases hits goes up (because set size is going down). Figure\ \@ref(fig:hitsfixVoppPlot)

```{r hits_fixVopp_distractors_table, results = 'asis'}
apa_table(hits.fixVopp.distractors.table$table, caption = "Summary of the 2 x 4 repeated measures ANOVA used to test the effects of block type and distractor number on participant hits in the working memory task.", escape = FALSE)
```

```{r hits_fixVopp_pairwise, results = 'asis'}
print(hits.fixVopp.distractors.distmain.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
```

```{r hitsfixVoppPlot, fig.cap = "Participant hits as a function of set size and number of distractors present at encoding and retrieval.", fig.align = "center"}
include_graphics("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_hitsfixVoppPlot.pdf", auto_pdf = TRUE)
```

## False Alarms
### Fixed distractor blocks
```{r fa_fixedonly_targets, include=FALSE, echo=FALSE}
fa.fixedonly.targanddist.aov <- aov_ez(
  data = fixed.Vals,
  dv = "faProp",
  id = "PID", 
  within = c("targetNum","DistNum")
)
#Pairwise comparisons
fa.fixedOnly.targets.targmain <- pairs(emmeans(fa.fixedonly.targanddist.aov, ~targetNum))

#Create tables
fa.fixedOnly.targets.table <- apa_print(fa.fixedonly.targanddist.aov)
#Create pairwise tables
fa.fixedOnly.targets.targmain.table <- xtable(summary(fa.fixedOnly.targets.targmain), caption = "Summary of the pairwise comparisons used to follow up the main interaction (fa)", label = "tab:fa.fixedOnly.targets.targmain.table")

#Create plot
fa.targXdist.summarydata <- summarySE(fixed.Vals, measurevar="faProp", groupvars=c("targetNum","DistNum"))
fa.targXdist.bar <- ggplot(fa.targXdist.summarydata, aes( x=DistNum,y=faProp)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymin=faProp-se, ymax=faProp+se), size=0.5,   
    width=.25,position=position_dodge(.9)) +
  facet_grid(~targetNum, labeller = as_labeller(c(`2`="Set size 2", `4`="Set size 4", `6`="Set size 6"))) +
  scale_y_continuous("Fa (%)",expand = c(0, 0)) +
  scale_x_discrete("Number of distractors") +
  theme_apa()
pdf("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_fatargXdistPlot.pdf", width = 7, paper = "special")
fa.targXdist.bar
dev.off()
```

Interaction between target number and dist number. Set size 2 > set size 4 > set size 6. For set size 2 there are no differences between dist num blocks. For est size 4 0 is different from 4 and 6 and approaching for 2. For set size 6, 0 is diff from 4 and 6, 2 is diff from 4. Figure\ \@ref(fig:fatargXdistPlot)

```{r fa.fixedOnly.targets.table, results = 'asis'}
apa_table(fa.fixedOnly.targets.table$table, caption = "Summary of the 3 x 4 repeated measures ANOVA used to test the effects of set size and distractor number on participant fa in the working memory task.", escape = FALSE)
```

```{r fa_fixedOnly_pairwise, results = 'asis'}
print(fa.fixedOnly.targets.targmain.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
```

```{r fatargXdistPlot, fig.cap = "Participant fa as a function of set size and number of distractors present at encoding and retrieval.", fig.align = "center"}
include_graphics("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_fatargXdistPlot.pdf", auto_pdf = TRUE)
```

### Fixed distractor vs variable distractor blocks
#### Fixed vs targEqual
```{r fa_fixVopp_distractors, include=FALSE, echo=FALSE}
fa.fixVmatch.distractors.aov <- aov_ez(
  data = fixVmat.Vals,
  dv = "faProp",
  id = "PID", 
  within = c("numDist", "Block")
)
#Interaction
fa.fixVmatch.distractors.distmain <- pairs(emmeans(fa.fixVmatch.distractors.aov, ~ numDist))

#Create tables
fa.fixVmatch.distractors.table <- apa_print(fa.fixVmatch.distractors.aov)
#Create pairwise tables
fa.fixVmatch.distractors.distmain.table <- xtable(summary(fa.fixVmatch.distractors.distmain), caption = "Summary of the pairwise comparisons used to follow up the main interaction (fa)", label = "tab:fa.fixVmatch.distractors.distmain.table")

#Create plots
fa.fixVmat.summarydata <- summarySE(fixVmat.Vals, measurevar="faProp", groupvars=c("Block","numDist"))
fa.fixVmat.bar <- ggplot(fa.fixVmat.summarydata, aes( x=Block,y=faProp)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymin=faProp-se, ymax=faProp+se), size=0.5,   
    width=.25,position=position_dodge(.9)) +
  facet_grid(~numDist, labeller = as_labeller(c(`2`="2 distractors", `4`="4 distractors", `6`="6 distractors"))) +
  scale_y_continuous("Fa (%)",expand = c(0, 0)) +
  scale_x_discrete("Block type") +
  theme_apa()
pdf("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_fafixvmatPlot.pdf", width = 7, paper = "special")
fa.fixVmat.bar
dev.off()
```

Interaction between block and distnum. within block type, fa graded with distnum. For distnum 2 and 4 no difference between block types. For dist 6, targEqual more accurate than fixed equivalent. Figure\ \@ref(fig:fafixVmatPlot)

```{r fa_fixVmatch_distractors_table, results = 'asis'}
apa_table(fa.fixVmatch.distractors.table$table, caption = "Summary of the 3 x 4 repeated measures ANOVA used to test the effects of set size and distractor number on participant fa in the working memory task.", escape = FALSE)
```

```{r fa_fixVmat_pairwise, results = 'asis'}
print(fa.fixVmatch.distractors.distmain.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
```

```{r fafixVmatPlot, fig.cap = "Participant fa as a function of set size and number of distractors present at encoding and retrieval.", fig.align = "center"}
include_graphics("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_fafixVmatPlot.pdf", auto_pdf = TRUE)
```

#### Fixed vs targOpp
```{r fa_fixVmat_distractors, include=FALSE, echo=FALSE}
fa.fixVopp.distractors.aov <- aov_ez(
  data = fixVopp.Vals,
  dv = "faProp",
  id = "PID", 
  within = c("numDist", "Block")
)
#Interaction
fa.fixVopp.distractors.distmain <- pairs(emmeans(fa.fixVopp.distractors.aov, ~ numDist))

#create table
fa.fixVopp.distractors.table <- apa_print(fa.fixVopp.distractors.aov)
#Create followup table
fa.fixVopp.distractors.distmain.table <- xtable(summary(fa.fixVopp.distractors.distmain), caption = "Summary of the pairwise comparisons used to follow up the main interaction (fa)", label = "tab:fa.fixVopp.distractors.distmain.table")

#create plot
fa.fixVopp.summarydata <- summarySE(fixVopp.Vals, measurevar="faProp", groupvars=c("Block","numDist"))
fa.fixVopp.bar <- ggplot(fa.fixVopp.summarydata, aes( x=Block,y=faProp)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymin=faProp-se, ymax=faProp+se), size=0.5,   
    width=.25,position=position_dodge(.9)) +
  facet_grid(~numDist, labeller = as_labeller(c(`2`="2 distractors", `4`="4 distractors", `6`="6 distractors"))) +
  scale_y_continuous("Fa (%)",expand = c(0, 0)) +
  scale_x_discrete("Block type") +
  theme_apa()
pdf("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_fafixvoppPlot.pdf", width = 7, paper = "special")
fa.fixVopp.bar
dev.off()
```

Main effect of distnum, as distnum increases fa goes up (because set size is going down). Figure\ \@ref(fig:fafixVoppPlot)

```{r fa_fixVopp_distractors_table, results = 'asis'}
apa_table(fa.fixVopp.distractors.table$table, caption = "Summary of the 2 x 4 repeated measures ANOVA used to test the effects of block type and distractor number on participant fa in the working memory task.", escape = FALSE)
```

```{r fa_fixVopp_pairwise, results = 'asis'}
print(fa.fixVopp.distractors.distmain.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
```

```{r fafixVoppPlot, fig.cap = "Participant fa as a function of set size and number of distractors present at encoding and retrieval.", fig.align = "center"}
include_graphics("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_fafixVoppPlot.pdf", auto_pdf = TRUE)
```

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
