---
title             : "Working memory capacity in a change detection task is affected by the number of irrelevant objects in the display"
shorttitle        : "Effects of distractor number on change detection"

author: 
  - name          : "Dion T. Henare"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "School of Psychology, University of Auckland, Private Bag 92019, Auckland 1010, New Zealand"
    email         : "dion.henare@auckland.ac.nz"
  - name          : "Paul M. Corballis"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "School of Psychology, Univeristy of Auckland"

author_note: |
  School of Psychology, University of Auckland, Private Bag 92019, Auckland 1010, New Zealand

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.
  
keywords          : "working memory capacity, change detection, delayed matching to sample, distraction, filtering"
wordcount         : "X"

bibliography      : ["r-references.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no

class             : "man"
output            : papaja::apa6_pdf
#toc: true
---

\raggedbottom

```{r WMB_load_packages, include = FALSE}
library("papaja")
#library(plyr)
library(dplyr)
library(ggplot2)
library(afex)
library(knitr)
library(xtable)
library(caTools) #split-half data
library(psych)
library(cowplot)

set.seed(4609948)
```

```{r WMB_helper_functions, include=FALSE, echo=FALSE}
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
    library(plyr)

    # New version of length which can handle NA's: if na.rm==T, don't count them
    length2 <- function (x, na.rm=FALSE) {
        if (na.rm) sum(!is.na(x))
        else       length(x)
    }

    # This does the summary. For each group's data frame, return a vector with
    # N, mean, and sd
    datac <- ddply(data, groupvars, .drop=.drop,
      .fun = function(xx, col) {
        c(N    = length2(xx[[col]], na.rm=na.rm),
          mean = mean   (xx[[col]], na.rm=na.rm),
          sd   = sd     (xx[[col]], na.rm=na.rm)
        )
      },
      measurevar
    )

    # Rename the "mean" column    
    datac <- rename(datac, c("mean" = measurevar))

    datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean

    # Confidence interval multiplier for standard error
    # Calculate t-statistic for confidence interval: 
    # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
    ciMult <- qt(conf.interval/2 + .5, datac$N-1)
    datac$ci <- datac$se * ciMult

    return(datac)
}
```

```{r load_raw_data, incude = FALSE, echo=FALSE}
#Find all files
filePath <- "P:/dhen061/WMBehav-RawFolder/data/"
files <- list.files(path = filePath, pattern = ".csv")
#load the first one and get the variable names
allData <- read.csv(file=paste(filePath,files[1], sep=""), header=TRUE, sep=",")
demoData <- subset(allData, select = c(X2..Age,X1..Sex))
demoData$X1..Sex <- as.character(demoData$X1..Sex)
allData <- subset(allData, select = c(targetColour, DistNum, matchType, targetNum, CorrAns, key_resp_2.keys, key_resp_2.rt))
#delete data so we just have a dataframe with the relevant variables
allData <- allData[0,]
demoData <- demoData[0,]
#set PID to 1
pid = 1

#Loop through the files, load them , and if there are 720 (as should be the case), add the PID and append to dataframe
for (file in files){
  curData <- read.csv(file=paste(filePath,file, sep=""), header=TRUE, sep=",")
  curData <- filter(curData,  !is.na(curData$trials.thisRepN))
  curDemo <- subset(curData, select = c(X2..Age,X1..Sex))
  curDemo$X1..Sex <- as.character(curDemo$X1..Sex)
  curData <- subset(curData, select = c(targetColour, DistNum, matchType, targetNum, CorrAns, key_resp_2.keys, key_resp_2.rt))
  if (nrow(curData) == 720) {
    curData$PID <- pid
    curDemo$PID <- pid
    allData <- rbind(allData,curData)
    demoData <- rbind(demoData,curDemo[1,])
    pid = pid+1
  } else {
    #If file doesn't have 720 rows, print the name
    #print(file)
  }
}
```

```{r tidy_data, include = FALSE}
#Tidy the data, remove non-response trials, and calculate correct response column
allData <- filter(allData, !allData$key_resp_2.keys=="None")
allData$CorrAns <- factor(allData$CorrAns)
allData$key_resp_2.keys <- factor(allData$key_resp_2.keys)
allData$correctResponse <- as.integer(allData$CorrAns==allData$key_resp_2.keys)
#Spit half the data
sample = sample.split(allData$correctResponse, SplitRatio = 0.5)
odd = allData[seq(1,nrow(allData),by=2),] #subset(allData, sample == TRUE)
even = allData[seq(2,nrow(allData),by=2),] #subset(allData, sample == FALSE)

#Participant rejection
participants <- group_by(allData,PID)
numberOfTrials <- dplyr::summarise(participants, nrow=NROW(correctResponse))
#Which participants have less than 700 trials meaning over 20 non-responses
nonRespFails <- numberOfTrials$PID[numberOfTrials$nrow<695]
if (!is.null(nonRespFails)) {
#remove failed participants
for (subj in 1:length(nonRespFails)) {
  allData <- allData[!allData$PID==nonRespFails[subj],]
  demoData <- demoData[!demoData$PID==nonRespFails[subj],]
  odd <- odd[!odd$PID==nonRespFails[subj],]
  even <- even[!even$PID==nonRespFails[subj],]
}
}
#Which participnats have <60% accuracy in 2 targ 0 dist condition
easyCond <- filter(allData, targetNum==2 & DistNum==0)
easyAccuracy <- dplyr::summarise(group_by(easyCond,PID), avg=mean(correctResponse))
accuracyFails <- easyAccuracy$PID[easyAccuracy$avg<0.60]
if (!is.null(accuracyFails)) {
for (subj in 1:length(accuracyFails)) {
  allData <- allData[!allData$PID==accuracyFails[subj],]
  demoData <- demoData[!demoData$PID==accuracyFails[subj],]
  odd <- odd[!odd$PID==accuracyFails[subj],]
  even <- even[!even$PID==accuracyFails[subj],]
}
}
```

```{r create_measure, include = FALSE}
#Create hits column and FA column
allData$hits <- as.integer(allData$CorrAns=="m" & allData$key_resp_2.keys=="m")
allData$FA <- as.integer(allData$CorrAns=="x" & allData$key_resp_2.keys=="m")
odd$hits <- as.integer(odd$CorrAns=="m" & odd$key_resp_2.keys=="m")
odd$FA <- as.integer(odd$CorrAns=="x" & odd$key_resp_2.keys=="m")
even$hits <- as.integer(even$CorrAns=="m" & even$key_resp_2.keys=="m")
even$FA <- as.integer(even$CorrAns=="x" & even$key_resp_2.keys=="m")
allData$numDist <- as.numeric(as.character(allData$DistNum))
allData$numDist[allData$DistNum=="targEqual"]=allData$targetNum[allData$DistNum=="targEqual"]
allData$numDist[allData$DistNum=="targOpp"]=8-allData$targetNum[allData$DistNum=="targOpp"]
fixData <- subset(allData, DistNum!="targEqual" & DistNum!="targOpp")
pid=1
model <- summary(glm(correctResponse~targetNum+numDist,data=subset(fixData,PID==pid),family=binomial()))

#Create summary table
participants <- group_by(allData, PID, targetNum, DistNum)
#Get number of hits and false alarms and calculate pashlers K
#Apply loglinear approach to prevent Hit rate and FA rate of 1 or 0 (Hautus,1995)
summaryTable <- dplyr::summarise(participants, correctResponse=mean(correctResponse)*100, hits=sum(hits)+0.5, fa=sum(FA)+0.5, possHits=sum(as.integer(CorrAns=="m"))+1, possFA=sum(as.integer(CorrAns=="x"))+1)
summaryTable$hitProp <- summaryTable$hits/summaryTable$possHits
summaryTable$faProp <- summaryTable$fa/summaryTable$possFA
#calculate capacity pashlers K
summaryTable$cowanC <- summaryTable$targetNum*(summaryTable$hitProp-summaryTable$faProp)
#calculate d and c
summaryTable$zHit <- qnorm(summaryTable$hitProp)
summaryTable$zFA <- qnorm(summaryTable$faProp)
summaryTable$D <- summaryTable$zHit-summaryTable$zFA
summaryTable$C <- -((summaryTable$zHit+summaryTable$zFA)/2)

#Add group information
grouping <- subset(summaryTable,DistNum==0)
grouping$Group <- ifelse(grouping$cowanC<=median(grouping$cowanC),"Low","High")
for (subj in c(1:nrow(grouping))) {
  summaryTable$Group[summaryTable$PID==grouping$PID[subj]] <- grouping$Group[subj]
}

#Repeat calculations for split half data
oddParticipants <- group_by(odd,PID, targetNum,DistNum)
oddTable <- dplyr::summarise(oddParticipants, correctResponse=mean(correctResponse)*100, hits=sum(hits)+0.5, fa=sum(FA)+0.5, possHits=sum(as.integer(CorrAns=="m"))+1, possFA=sum(as.integer(CorrAns=="x"))+1)
oddTable$hitProp <- oddTable$hits/oddTable$possHits
oddTable$faProp <- oddTable$fa/oddTable$possFA
oddTable$cowanC <- oddTable$targetNum*(oddTable$hitProp-oddTable$faProp)

evenParticipants <- group_by(even,PID, targetNum,DistNum)
evenTable <- dplyr::summarise(evenParticipants, correctResponse=mean(correctResponse)*100, hits=sum(hits)+0.5, fa=sum(FA)+0.5, possHits=sum(as.integer(CorrAns=="m"))+1, possFA=sum(as.integer(CorrAns=="x"))+1)
evenTable$hitProp <- evenTable$hits/evenTable$possHits
evenTable$faProp <- evenTable$fa/evenTable$possFA
evenTable$cowanC <- evenTable$targetNum*(evenTable$hitProp-evenTable$faProp)

#Separate fixed and variable blocks
fixNames <- c("0", "2","4","6")
fixed.Vals <- filter(summaryTable, DistNum %in% fixNames)
varNames <- c("targEqual","targOpp")
var.Vals <- filter(summaryTable, DistNum %in% varNames)
var.Vals$numDist <- ifelse(var.Vals$DistNum=="targEqual",var.Vals$targetNum,8-var.Vals$targetNum)
var.Vals$Block <- var.Vals$DistNum
#fix up factors in fix v var mat
fixVmat.Vals <- filter(summaryTable, DistNum == "targEqual" | (DistNum=="2" & targetNum==2) | (DistNum=="4" & targetNum==4)  | (DistNum=="6" & targetNum==6))
fixVmat.Vals$numDist <- fixVmat.Vals$DistNum
fixVmat.Vals$numDist[fixVmat.Vals$DistNum=="targEqual"] <- fixVmat.Vals$targetNum[fixVmat.Vals$DistNum=="targEqual"]
fixVmat.Vals$Block <- fixVmat.Vals$DistNum
levels(fixVmat.Vals$Block) <- c(levels(fixVmat.Vals$Block),"fixed")
fixVmat.Vals$Block[fixVmat.Vals$Block!="targEqual"] <- "fixed"
fixVmat.Vals$Block <- factor(fixVmat.Vals$Block)
fixVmat.Vals$numDist <- factor(fixVmat.Vals$numDist)
#Fix up factors in fix v var opp
fixVopp.Vals <- filter(summaryTable, DistNum == "targOpp" | (DistNum=="2" & targetNum==6) | (DistNum=="4" & targetNum==4)  | (DistNum=="6" & targetNum==2))
fixVopp.Vals$numDist <- fixVopp.Vals$DistNum
fixVopp.Vals$numDist[fixVopp.Vals$DistNum=="targOpp"] <- 8-fixVopp.Vals$targetNum[fixVopp.Vals$DistNum=="targOpp"]
fixVopp.Vals$Block <- fixVopp.Vals$DistNum
levels(fixVopp.Vals$Block) <- c(levels(fixVopp.Vals$Block),"fixed")
fixVopp.Vals$Block[fixVopp.Vals$Block!="targOpp"] <- 'fixed'
fixVopp.Vals$Block <- factor(fixVopp.Vals$Block)
```

# Introduction

Working memory is a term used to describe the active maintenance of information for brief periods of time. It is well known that there are limits to the amount of information that can be stored, and that an individual's working memory capacity is associated with a range of other important cognitive abilities. Individuals with larger working memory capacities have been shown to have better language comprehension [@daneman_working_1996], problem solving, multi-tasking [@hambrick_predictors_2010], emotion regulation  [@kleider_shooting_2010], and higher general fluid intelligence [@kane_working_2005]. Working memory capacity has also been shown to predict real-world abilities such as hazard detection in drivers [@wood_working_2016]. The estimation of working memory capacity is therefore increasingly important for research in all of these cognitive domains, and recent evidence has shown that capacity estimates can vary depending not only on the general paradigm being used, but the details of that paradigm [@shipstead_mechanisms_2014].

Change detection tasks are an increasingly popular way of measuring visual working memory capacity across individuals. Change detection involves the brief presentation of an encoding display, where a number of simple objects are shown on screen for the participant to encode. This is followed by a delay period where the participant must maintain the encoded information in working memory, and then a retrieval probe is presented. The participant must indicate whether or not the retrieval probe matches the encoded stimuli. Typically, set size (the number of objects that should be encoded) is varied across trials and performance is measured using either accuracy on the task, or by estimating capacity [@rouder_how_2011]. Capacity is quantified for a given set size based on the proportion of hits (the number of correctly identified match probes), and the proportion of false alarms (the number of non-matches that are misidentified as matches) [@rouder_how_2011]. As a result of their short, simple structure, change detection tasks are well suited to use with developmental and clinical populations, as well as with neural recordings that require large trial numbers [@xu_reliability_2018]. Change detection tasks also translate well to paradigms used with non-human animals and taken together, these features have contributed to their rising popularity [@xu_reliability_2018].

Specific incarnations of the change detection paradigm can vary significantly in terms of the type of stimuli used, and the number of stimuli that are presented at both encoding and retrieval. Historically, one of the main ways that change detection tasks have varied is with regard to the number of probes presented on the retrieval display. In the single-probed retrieval version of the task, participants are shown only one of the encoded stimuli and must therefore indicate whether that specific object has changed in any way. In the whole-display retrieval version of the task however, the entire set of encoded stimuli are presented as probes and the participant must indicate whether any one of the stimuli have changed. Another way in which the task varies is with regard to the number of encode stimuli that need to be remembered. In some versions of the task, all of the objects presented during encoding must be remembered by the participant. In other versions of the task participants receive a cue ahead of the encoding display which indicates which subset of the encoding stimuli needs to be remembered. For example, participants may be cued to encode only the blue objects in an upcoming display which contains both blue and red stimuli. These features have been shown to effect not just the absolute capacity values reported, but the underlying cognitive mechanisms that are being tested.

One set of cognitive mechanisms that is especially important to consider when measuring working memory is selective attention. Converging evidence from both within and between-participant experiments now suggests that there is significant functional overlap between selective attention and working memory. When working memory load on an individual is increased, performance on a concurrent visual search task is impeded [@ahmed_focusing_2012;@de_fockert_role_2001;@stins_role_2004]. Similarly, individuals who naturally possess a larger working memory capacity perform better on standard measures of attentional control like the Stroop task [@kane_working-memory_2003] and the Eriksen flanker task [@shipstead_working_2012]. Modern accounts of working memory availability typically recognize this close association between attention and working memory by either incorporating elements of attentional control [@kane_controlled-attention_2001; @shipstead_mechanisms_2014, or in some cases suggesting that attentional control is the primary determinant of working memory capacity [@engle_working_2018]. More specific investigations of this relationship using both behavioral and neural measures now suggest that it is specifically the ability to disengage from irrelevant distractors which differentiates high and low capacity individuals [@fukuda_individual_2011;gaspar_inability_2016].

The critical role that distractor suppression plays in working memory performance raises questions around the effect that irrelevant objects may have in a change detection task. In our study, we used a cued, probed-retrieval version of the change detection task while varying the number of distractors across blocks. This allowed us to systematically measure the effect that distraction in the change detection task has on both participant performance, and estimates of individual capacity. Set size varied within each block however the number of distractors remained fixed in 4 conditions (ranging from 0 distractors to 6 distractors), and varied in two conditions (either to maintain the total number of objects on screen across the block, or to match the number of targets on each trial). We measured the effect of these distractor conditions on accuracy and capacity, as well as on signal detection measures of sensitivity (d'), and response bias (C).

Working memory is central to functioning and important for stuff like fluid intelligence, attention, IQ or whatever.

change detection tasks are popular for measuring WM capacity across individuals. (basic outline, increasing popularity, benefits).

Many variations in change detection tasks. Pashler vs Cowan.

working memory related to attention and specifically distractor filtering things.

Estimates of capacity may be effected by the number of distractors that are presented in the change detection task - our study.

trial-to-trial context effects working memory so distractor effect may also be mediated by context - our study.

# Methods

## Participants
```{r demo_Analysis, echo=FALSE, include=FALSE}
demographics <- group_by(demoData,PID, X2..Age, X1..Sex)
#Get number of hits and false alarms and calculate pashlers K
#Apply loglinear approach to prevent Hit rate and FA rate of 1 or 0 (Hautus,1995)
demoTable <- dplyr::summarise(demographics)
demoTable$X1..Sex <- toupper(substr(demoTable$X1..Sex,start=1,stop=1))
demoTable$X2..Age <- as.numeric(substr(demoTable$X2..Age,start=1,stop=2))
demoTable$SexBin <- ifelse(demoTable$X1..Sex=="F",1,0)

meanAge <- mean(demoTable$X2..Age)
sdAge <- sd(demoTable$X2..Age)
minAge <- min(demoTable$X2..Age)
maxAge <- max(demoTable$X2..Age)

totalSubj <- length(summary(as.factor(demoTable$PID)))
totalFemale <- sum(demoTable$SexBin)
```

62 individuals participated in the task and all had either normal or corrected-to-normal vision. One participant did not complete the entire task and was therefore excluded from analysis. Five participants were deemed not to have performed the task properly (3 had over 25 non-responses, and two had less than 60% accuracy on the easiest condition where the set size was 2 and there were no distractors on screen). As a result, 56 individuals (`r totalFemale` female) with an age range of `r minAge` to `r maxAge` (mean = `r meanAge` and sd = `r sdAge`) were included in the analysis.

## Change detection task

Participants were positioned 57cm away from the screen and performed two practice blocks of 12 trials each, followed by 18 blocks of 40 trials each for a total of 720 experimental trials. For each block, the participant was told which color (either blue or red) they would be focusing on for that block. Trials began with a 1 second fixation cross and involved being presented with a set of rectangles for 250ms, some of which matched the target color, and some of which were irrelevant colored distractors. Participants were required to encode only the subset of objects defined by the target color, maintain that information across a one second delay period, and were then presented with the retrieval display for 2 seconds (or until the participant responded). The retrieval display consisted of all of the stimuli presented in the encoding display however one of the target objects was marked with a probe and participants were required to indicate whether the probed object had changed since encoding. The probe object was rotated randomly on 50% of trials (constituting a non-match trial) and matched the encoded object on the other 50% of trials. A fixation cross was maintained in the center of the screen throughout the entire trial.

Blocks were separated into 6 different conditions. In four of the blocks, the number of distractors (objects of the irrelevant color) present at encoding and retrieval was fixed across the block at either 0, 2, 4, or 6. In the other two conditions, distractor number varied within the block. In one of these variable conditions, the number of distractors was simply the same as the number of targets on a given trial. In the other variable block, we sought to keep the total number of objects on screen the same, and therefore the number of distractors was always the inverse of the number of targets.

## Stimulus presentation

All stimuli were presented on a .X. monitor in  using psychopy (v.). The fixation cross0 .5x0.5 degrees and was fixed in the center of the screen throughout each trial. Each memory stimulus was a 0.5X2 degree bar of either red() or green() and rotated to one of four orientations  (0,45,90,135). The probe consisted of a 0.5x0.5 white square positioned on the center of the probed stimulus. All stimuli were kept within .X. degrees of the fixation cross and were separated by at least .X. degrees. Python code used to run the task is available at .X.link.

## Data processing
Trials which had no response were removed for all participants and performance measures were calculated for each block type and set size. For each of these conditions we calculated accuracy, capacity, hit rate, false alarm rate, D', and C.
groups created by...

# Results
## Target number
```{r target_number_effect, include=FALSE, echo=FALSE}
accuracy.targetNum.aov <- aov_ez(
  data = summaryTable,
  dv = "correctResponse",
  id = "PID",
  within = "targetNum"
)
target.followup <- pairs(emmeans(accuracy.targetNum.aov, ~ targetNum))
target.aov.result <- apa_print(accuracy.targetNum.aov)

twoTarg.mean <- describe(subset(summaryTable,targetNum==2)$correctResponse)$mean
twoTarg.sd <- describe(subset(summaryTable,targetNum==2)$correctResponse)$sd
fourTarg.mean <- describe(subset(summaryTable,targetNum==4)$correctResponse)$mean
fourTarg.sd <- describe(subset(summaryTable,targetNum==4)$correctResponse)$sd
sixTarg.mean <- describe(subset(summaryTable,targetNum==6)$correctResponse)$mean
sixTarg.sd <- describe(subset(summaryTable,targetNum==6)$correctResponse)$sd
```

First, to confirm a fundamental benchmark in the change detection task (that participant accuracy decreases as the number of to-be-remembered items goes up) we performed a one-way ANOVA to test for the effect of target number on accuracy. The independent variable was target number across all blocks types (which had three levels; two targets, four targets, or six targets) and the dependent variable was accuracy. The results showed a significant effect of target number (`r target.aov.result$full_result$targetNum`) on accuracy and follow up comparisons using tukey correction confirmed the expected effect that accuracy is significantly higher in the two target trials (M=`r twoTarg.mean`, sd=`r twoTarg.sd`) when compared to both the four target (M=`r fourTarg.mean`, sd=`r fourTarg.sd`, t(110)=12.81, p<0.001) and six target trials (M=`r sixTarg.mean`, sd=`r sixTarg.sd`, t(110)=22.2, p<0.001), and accuracy is also higher in the four target trials compared to the six target trials (t(110)=10.42, p<0.001).

## Fixed distractor blocks
```{r fixed_distractor_effect,include=FALSE, echo=FALSE}
accuracy.fixedonly.aov <- aov_ez(
  data = fixed.Vals,
  dv = "correctResponse",
  id = "PID", 
  within = "DistNum"
)
accuracy.fixed <- apa_print(accuracy.fixedonly.aov)
accuracy.fixed.followup <- pairs(emmeans(accuracy.fixedonly.aov, ~DistNum))
accuracy.fixed.distractors.table <- xtable(summary(accuracy.fixed.followup), caption = "Summary of the pairwise comparisons used to follow up the main effect of distractor number on accuracy", label = "tab:accuracyfixeddistractorstable")

capacity.fixedonly.aov <- aov_ez(
  data = fixed.Vals,
  dv = "cowanC",
  id = "PID", 
  within = "DistNum"
)
capacity.fixed <- apa_print(capacity.fixedonly.aov)
capacity.fixed.followup <- pairs(emmeans(capacity.fixedonly.aov, ~DistNum))
capacity.fixed.distractors.table <- xtable(summary(capacity.fixed.followup), caption = "Summary of the pairwise comparisons used to follow up the main effect of distractor number on capacity", label = "tab:capacityfixeddistractorstable")

sensitivity.fixedonly.aov <- aov_ez(
  data = fixed.Vals,
  dv = "D",
  id = "PID", 
  within = "DistNum"
)
sensitivity.fixed <- apa_print(sensitivity.fixedonly.aov)
sensitivity.fixed.followup <- pairs(emmeans(sensitivity.fixedonly.aov, ~DistNum))
sensitivity.fixed.distractors.table <- xtable(summary(sensitivity.fixed.followup), caption = "Summary of the pairwise comparisons used to follow up the main effect of distractor number on sensitivity", label = "tab:sensitivityfixeddistractorstable")

responseBias.fixedonly.aov <- aov_ez(
  data = fixed.Vals,
  dv = "C",
  id = "PID", 
  within = "DistNum"
)
responseBias.fixed <- apa_print(responseBias.fixedonly.aov)

# fixed distractor plots
accuracy.fixed.summarydata <- summarySE(fixed.Vals, measurevar="correctResponse", groupvars="DistNum")
accuracy.fixed.plot <- ggplot(accuracy.fixed.summarydata, aes( x=DistNum,y=correctResponse)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymin=correctResponse-se, ymax=correctResponse+se), size=0.5,
    width=.25,position=position_dodge(.9)) +
  scale_y_continuous("Accuracy (%)",expand = c(0, 0)) +
  coord_cartesian(ylim=c(50,80)) +
  scale_x_discrete("Number of distractors across block") +
  theme_apa()

capacity.fixed.summarydata <- summarySE(fixed.Vals, measurevar="cowanC", groupvars="DistNum")
capacity.fixed.plot <- ggplot(capacity.fixed.summarydata, aes( x=DistNum,y=cowanC)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymin=cowanC-se, ymax=cowanC+se), size=0.5,
    width=.25,position=position_dodge(.9)) +
  scale_y_continuous("Capacity",expand = c(0, 0)) +
  coord_cartesian(ylim=c(0,2)) +
  scale_x_discrete("Number of distractors across block") +
  theme_apa()

sensitivity.fixed.summarydata <- summarySE(fixed.Vals, measurevar="D", groupvars="DistNum")
sensitivity.fixed.plot <- ggplot(sensitivity.fixed.summarydata, aes( x=DistNum,y=D)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymin=D-se, ymax=D+se), size=0.5,
    width=.25,position=position_dodge(.9)) +
  scale_y_continuous("Sensitivity (d')",expand = c(0, 0)) +
  coord_cartesian(ylim=c(0,2)) +
  scale_x_discrete("Number of distractors across block") +
  theme_apa()

responseBias.fixed.summarydata <- summarySE(fixed.Vals, measurevar="C", groupvars="DistNum")
responseBias.fixed.plot <- ggplot(responseBias.fixed.summarydata, aes( x=DistNum,y=C)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymin=C-se, ymax=C+se), size=0.5,
    width=.25,position=position_dodge(.9)) +
  scale_y_continuous("ResponseBias (C)",expand = c(0, 0)) +
  coord_cartesian(ylim=c(-1,0)) +
  scale_x_discrete("Number of distractors across block") +
  theme_apa()

pdf("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_fixedBlock_distractors.pdf", width = 7, paper = "special")
plot_grid(accuracy.fixed.plot,capacity.fixed.plot,sensitivity.fixed.plot,responseBias.fixed.plot)
dev.off()

```
Next, we focused on blocks in which the number of distractors was fixed for the entire block at either zero, two, four, or six distractors. In order to test for the effect of distractor number on change detection performance, we calculated four behavioral measures (accuracy, working memory capacity, sensitivity, and response bias), and performed a one-way ANOVA for each of these measures with distractor number as the independent variable. The results showed that distractor number had a significant effect on accuracy (`r accuracy.fixed$full_result$DistNum`), capacity (`r capacity.fixed$full_result$DistNum`), and sensitivity (`r sensitivity.fixed$full_result$DistNum`), but no significant effect on response bias (`r responseBias.fixed$full_result$DistNum`). Follow up comparisons were performed using tukey correction for each of the significant effects and the results generally show that in blocks with larger numbers of irrelevant distractors, accuracy is lower (see table\ \@ref(tab:accuracyfixeddistractorstable) for details), capacity estimates are lower (see table\ \@ref(tab:capacityfixeddistractorstable) for details), and sensitivity is lower (see table\ \@ref(tab:sensitivityfixeddistractorstable) for details) however not every follow up comparison is significant.

```{r accuracy_fixed_distractors, results = 'asis'}
print(accuracy.fixed.distractors.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
print(capacity.fixed.distractors.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
print(sensitivity.fixed.distractors.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
```

```{r accuracyFixedDistractorsPlot, fig.cap = "Plots showing the mean and standard error for each behavioural measure across the fixed distractor blocks.", fig.align = "center"}
include_graphics("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_fixedBlock_distractors.pdf", auto_pdf = TRUE)
```

## Target-match blocks

In order to test for the effect of target-matching block context on performance, we first focused on those blocks where the number of distractors on a given trial always matched the number of targets on that trial. These target-match trials were compared to the equivalent trials taken from the fixed distractor blocks (two target trials from the two distractor blocks, four target trials from the four distractor blocks, and six target trials from the six distractor blocks). Once again we calculated accuracy, capacity, sensitivity, and response bias and performed a 2x3 ANOVA for each of these dependent variables, with block type (fixed, or target-match) and distractor number (two, four, or six) as the independent variables. In this case, main effects of distractor number would represent the same effects described above and therefore follow up comparisons were only performed on interactions between block type and distractor number. The results of these analyses are visualized in figure\ \@ref(fig:load_targMatch_Plots)

### Accuracy
```{r accuracy_fixVmat_distractors, include=FALSE, echo=FALSE}
accuracy.fixVmatch.distractors.aov <- aov_ez(
  data = fixVmat.Vals,
  dv = "correctResponse",
  id = "PID", 
  within = c("numDist", "Block")
)
#Interaction
accuracy.fixVmatch.distractors.distXblock <- pairs(emmeans(accuracy.fixVmatch.distractors.aov, ~ numDist|Block))
accuracy.fixVmatch.distractors.blockXdist <- pairs(emmeans(accuracy.fixVmatch.distractors.aov, ~ Block|numDist))

#Create tables
accuracy.fixVmatch.distractors.table <- apa_print(accuracy.fixVmatch.distractors.aov)
#Create pairwise tables
accuracy.fixVmatch.distractors.distXblock.table <- xtable(summary(accuracy.fixVmatch.distractors.distXblock), caption = "Summary of the pairwise comparisons used to follow up the main interaction (accuracy)", label = "tab:accuracyfixVmatchdistractorsdistXblocktable")
accuracy.fixVmatch.distractors.blockXdist.table <- xtable(summary(accuracy.fixVmatch.distractors.blockXdist), caption = "Summary of the pairwise comparisons used to follow up the main interaction (accuracy)", label = "tab:accuracyfixVmatchdistractorsblockXdisttable")

#Create plots
accuracy.fixVmat.summarydata <- summarySE(fixVmat.Vals, measurevar="correctResponse", groupvars=c("Block","numDist"))
accuracy.fixVmat.bar <- ggplot(accuracy.fixVmat.summarydata, aes( x=Block,y=correctResponse)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymin=correctResponse-se, ymax=correctResponse+se), size=0.5,   
    width=.25,position=position_dodge(.9)) +
  facet_grid(~numDist, labeller = as_labeller(c(`2`="2 distractors", `4`="4 distractors", `6`="6 distractors"))) +
  scale_y_continuous("Accuracy (%)",expand = c(0, 0)) +
  coord_cartesian(ylim=c(50,100)) +
  scale_x_discrete("Block type") +
  theme_apa()
pdf("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_accuracyfixvmatPlot.pdf", width = 7, paper = "special")
accuracy.fixVmat.bar
dev.off()
```

The results showed a main effect of distractor number (`r accuracy.fixVmatch.distractors.table$full_result$numDist`) on accuracy, but no main effect of block context (`r accuracy.fixVmatch.distractors.table$full_result$Block`). There was however a significant interaction between distractor number and block context (`r accuracy.fixVmatch.distractors.table$full_result$numDist_Block`) and pairwise comparisons using Tukey correction were performed in order to follow up this effect. For both block types, participants got significantly more accurate as distractor number decreased (see table\ \@ref(tab:accuracyfixVmatchdistractorsdistXblocktable) for full details). In the two distractor trials, participants were significantly less accurate in the target-match block compared to fixed distractor block, there was no significant difference between blocks for the four distractor, and six distractor trials (see table\ \@ref(tab:accuracyfixVmatchdistractorsblockXdisttable)). The results of this analysis are shown in figure\ \@ref(fig:accuracyfixVmatPlot).

```{r accuracy_fixVmatch_distractors_table, results = 'asis'}
#apa_table(accuracy.fixVmatch.distractors.table$table, caption = "FixVMat accuracy: Summary of the 2 x 4 repeated measures ANOVA used to test the effects of block type and distractor number on participant accuracy in the working memory task.", escape = FALSE)
```

```{r accuracy_fixVmat_pairwise, results = 'asis'}
print(accuracy.fixVmatch.distractors.distXblock.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
print(accuracy.fixVmatch.distractors.blockXdist.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
```

```{r accuracyfixVmatPlot, fig.cap = "Participant accuracy as a function of set size and number of distractors present at encoding and retrieval.", fig.align = "center"}
include_graphics("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_accuracyfixVmatPlot.pdf", auto_pdf = TRUE)
```
### Capacity
```{r capacity_fixVmat_distractors, include=FALSE, echo=FALSE}
capacity.fixVmatch.distractors.aov <- aov_ez(
  data = fixVmat.Vals,
  dv = "cowanC",
  id = "PID", 
  within = c("numDist", "Block")
)
#Interaction
capacity.fixVmatch.distractors.distMain <- pairs(emmeans(capacity.fixVmatch.distractors.aov, ~ numDist))
capacity.fixVmatch.distractors.distXblock <- pairs(emmeans(capacity.fixVmatch.distractors.aov, ~ numDist|Block))
capacity.fixVmatch.distractors.blockXdist <- pairs(emmeans(capacity.fixVmatch.distractors.aov, ~ Block|numDist))

#Create tables
capacity.fixVmatch.distractors.table <- apa_print(capacity.fixVmatch.distractors.aov)
#Create pairwise tables
capacity.fixVmatch.distractors.distMain.table <- xtable(summary(capacity.fixVmatch.distractors.distMain), caption = "Summary of the pairwise comparisons used to follow up the main effect of distractor number (capacity)", label = "tab:capacityfixVmatchdistractorsdistMaintable")
capacity.fixVmatch.distractors.distXblock.table <- xtable(summary(capacity.fixVmatch.distractors.distXblock), caption = "Summary of the pairwise comparisons used to follow up the main interaction (capacity)", label = "tab:capacity.fixVmatch.distractors.distXblock.table")
capacity.fixVmatch.distractors.blockXdist.table <- xtable(summary(capacity.fixVmatch.distractors.blockXdist), caption = "Summary of the pairwise comparisons used to follow up the main interaction (capacity)", label = "tab:capacity.fixVmatch.distractors.blockXdist.table")

#Create plots
capacity.fixVmat.summarydata <- summarySE(fixVmat.Vals, measurevar="cowanC", groupvars=c("Block","numDist"))
capacity.fixVmat.bar <- ggplot(capacity.fixVmat.summarydata, aes( x=Block,y=cowanC)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymin=cowanC-se, ymax=cowanC+se), size=0.5,   
    width=.25,position=position_dodge(.9)) +
  facet_grid(~numDist, labeller = as_labeller(c(`2`="2 distractors", `4`="4 distractors", `6`="6 distractors"))) +
  scale_y_continuous("Capacity (%)",expand = c(0, 0)) +
  scale_x_discrete("Block type") +
  theme_apa()
pdf("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_capacityfixvmatPlot.pdf", width = 7, paper = "special")
capacity.fixVmat.bar
dev.off()
```

The results showed a main effect of distractor number (`r capacity.fixVmatch.distractors.table$full_result$numDist`) on capacity, but no main effect of block context (`r capacity.fixVmatch.distractors.table$full_result$Block`), and no significant interaction between distractor number and block context (`r capacity.fixVmatch.distractors.table$full_result$numDist_Block`). The results of this analysis are shown in figure\ \@ref(fig:capacityfixVmatPlot).

```{r capacity_fixVmatch_distractors_table, results = 'asis'}
#apa_table(capacity.fixVmatch.distractors.table$table, caption = "FixVMat capacity. Summary of the 3 x 4 repeated measures ANOVA used to test the effects of set size and distractor number on participant capacity in the working memory task.", escape = FALSE)
```

```{r capacity_fixVmat_pairwise, results = 'asis'}
#print(capacity.fixVmatch.distractors.distMain.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
#print(capacity.fixVmatch.distractors.distXblock.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
#print(capacity.fixVmatch.distractors.blockXdist.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
```

```{r capacityfixVmatPlot, fig.cap = "Participant capacity as a function of set size and number of distractors present at encoding and retrieval.", fig.align = "center"}
include_graphics("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_capacityfixVmatPlot.pdf", auto_pdf = TRUE)
```
### Sensitivity
```{r sensitivity_fixVmat_distractors, include=FALSE, echo=FALSE}
sensitivity.fixVmatch.distractors.aov <- aov_ez(
  data = fixVmat.Vals,
  dv = "D",
  id = "PID", 
  within = c("numDist", "Block")
)
#Interaction
sensitivity.fixVmatch.distractors.distXblock <- pairs(emmeans(sensitivity.fixVmatch.distractors.aov, ~ numDist|Block))
sensitivity.fixVmatch.distractors.blockXdist <- pairs(emmeans(sensitivity.fixVmatch.distractors.aov, ~ Block|numDist))

#Create tables
sensitivity.fixVmatch.distractors.table <- apa_print(sensitivity.fixVmatch.distractors.aov)
#Create pairwise tables
sensitivity.fixVmatch.distractors.distXblock.table <- xtable(summary(sensitivity.fixVmatch.distractors.distXblock), caption = "Summary of the pairwise comparisons used to follow up the main interaction (sensitivity)", label = "tab:sensitivityfixVmatchdistractorsdistXblocktable")
sensitivity.fixVmatch.distractors.blockXdist.table <- xtable(summary(sensitivity.fixVmatch.distractors.blockXdist), caption = "Summary of the pairwise comparisons used to follow up the main interaction (sensitivity)", label = "tab:sensitivityfixVmatchdistractorsblockXdisttable")

#Create plots
sensitivity.fixVmat.summarydata <- summarySE(fixVmat.Vals, measurevar="D", groupvars=c("Block","numDist"))
sensitivity.fixVmat.bar <- ggplot(sensitivity.fixVmat.summarydata, aes( x=Block,y=D)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymin=D-se, ymax=D+se), size=0.5,   
                width=.25,position=position_dodge(.9)) +
  facet_grid(~numDist, labeller = as_labeller(c(`2`="2 distractors", `4`="4 distractors", `6`="6 distractors"))) +
  scale_y_continuous("sensitivity (%)",expand = c(0, 0)) +
  scale_x_discrete("Block type") +
  theme_apa()
pdf("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_sensitivityfixvmatPlot.pdf", width = 7, paper = "special")
sensitivity.fixVmat.bar
dev.off()
```

The results showed a main effect of distractor number (`r sensitivity.fixVmatch.distractors.table$full_result$numDist`) on sensitivity, but no main effect of block context (`r sensitivity.fixVmatch.distractors.table$full_result$Block`). There was however a significant interaction between distractor number and block context (`r sensitivity.fixVmatch.distractors.table$full_result$numDist_Block`) and pairwise comparisons using Tukey correction were performed in order to follow up this effect. For both block types, participants had significantly higher sensitivity as distractor number decreased (see table\ \@ref(tab:sensitivityfixVmatchdistractorsdistXblocktable) for full details). In the 6 distractor trials, participants had significantly higher sensitivity in the target-match block than the fixed block, there was no significant difference between blocks in the four distractor trials, but there was an effect approaching significance in the two distractor trials where participants had higher sensitivity in the fixed distractor blocks (see table\ \@ref(tab:sensitivityfixVmatchdistractorsblockXdisttable)). The results of this analysis are shown in figure\ \@ref(fig:sensitivityfixVmatPlot).

```{r sensitivity_fixVmatch_distractors_table, results = 'asis'}
#apa_table(sensitivity.fixVmatch.distractors.table$table, caption = "FixVMat sensitivity: Summary of the 2 x 4 repeated measures ANOVA used to test the effects of block type and distractor number on participant sensitivity in the working memory task.", escape = FALSE)
```

```{r sensitivity_fixVmat_pairwise, results = 'asis'}
print(sensitivity.fixVmatch.distractors.distXblock.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
print(sensitivity.fixVmatch.distractors.blockXdist.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
```

```{r sensitivityfixVmatPlot, fig.cap = "Participant sensitivity as a function of set size and number of distractors present at encoding and retrieval.", fig.align = "center"}
include_graphics("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_sensitivityfixVmatPlot.pdf", auto_pdf = TRUE)
```
### Response bias
```{r criterion_fixVmat_distractors, include=FALSE, echo=FALSE}
criterion.fixVmatch.distractors.aov <- aov_ez(
  data = fixVmat.Vals,
  dv = "C",
  id = "PID", 
  within = c("numDist", "Block")
)
#Interaction
criterion.fixVmatch.distractors.distXblock <- pairs(emmeans(criterion.fixVmatch.distractors.aov, ~ numDist|Block))
criterion.fixVmatch.distractors.blockXdist <- pairs(emmeans(criterion.fixVmatch.distractors.aov, ~ Block|numDist))

#Create tables
criterion.fixVmatch.distractors.table <- apa_print(criterion.fixVmatch.distractors.aov)

#Create plots
criterion.fixVmat.summarydata <- summarySE(fixVmat.Vals, measurevar="C", groupvars=c("Block","numDist"))
criterion.fixVmat.bar <- ggplot(criterion.fixVmat.summarydata, aes( x=Block,y=C)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymin=C-se, ymax=C+se), size=0.5,   
                width=.25,position=position_dodge(.9)) +
  facet_grid(~numDist, labeller = as_labeller(c(`2`="2 dist", `4`="4 distractors", `6`="6 distractors"))) +
  scale_y_continuous("criterion (%)",expand = c(0, 0)) +
  scale_x_discrete("Block type") +
  theme_apa()
pdf("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_criterionfixvmatPlot.pdf", width = 7, paper = "special")
criterion.fixVmat.bar
dev.off()
```

The results showed no significant main effect of distractor number (`r criterion.fixVmatch.distractors.table$full_result$numDist`) on response bias, no significant main effect of block context (`r criterion.fixVmatch.distractors.table$full_result$Block`), and no significant interaction between distractor number and block context (`r criterion.fixVmatch.distractors.table$full_result$numDist_Block`). The results are displayed in figure\ \@ref(fig:criterionfixVmatPlot).

```{r criterion_fixVmatch_distractors_table, results = 'asis'}
#apa_table(criterion.fixVmatch.distractors.table$table, caption = "FixVMat criterion: Summary of the 2 x 4 repeated measures ANOVA used to test the effects of block type and distractor number on participant criterion in the working memory task.", escape = FALSE)
```

```{r criterionfixVmatPlot, fig.cap = "Participant criterion as a function of set size and number of distractors present at encoding and retrieval.", fig.align = "center"}
include_graphics("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_criterionfixVmatPlot.pdf", auto_pdf = TRUE)
```

## Target-inverse blocks

Next, we tested for the effect of target-inverse block context on performance by focusing on those blocks where the number of distractors on a given trial was always the inverse of the number of targets on that trial. These target-inverse trials were compared to the equivalent trials taken from the fixed distractor blocks (two target trials from the six distractor blocks, four target trials from the four distractor blocks, and six target trials from the two distractor blocks). Once again we calculated accuracy, capacity, sensitivity, and response bias and performed a 2x3 ANOVA for each of these dependent variables, with block type (fixed, or target-match) and distractor number (two, four, or six) as the independent variables. Once again, follow up comparisons were only performed on interactions between block type and distractor number. 

### Accuracy
```{r accuracy_fixVopp_distractors, include=FALSE, echo=FALSE}
accuracy.fixVopp.distractors.aov <- aov_ez(
  data = fixVopp.Vals,
  dv = "correctResponse",
  id = "PID", 
  within = c("numDist", "Block")
)
#Interaction
accuracy.fixVopp.distractors.distmain <- pairs(emmeans(accuracy.fixVopp.distractors.aov, ~ numDist))

#create table
accuracy.fixVopp.distractors.table <- apa_print(accuracy.fixVopp.distractors.aov)
#Create followup table
accuracy.fixVopp.distractors.distmain.table <- xtable(summary(accuracy.fixVopp.distractors.distmain), caption = "Summary of the pairwise comparisons used to follow up the main interaction (accuracy)", label = "tab:accuracy.fixVopp.distractors.distmain.table")

#create plot
accuracy.fixVopp.summarydata <- summarySE(fixVopp.Vals, measurevar="correctResponse", groupvars=c("Block","numDist"))
accuracy.fixVopp.bar <- ggplot(accuracy.fixVopp.summarydata, aes( x=Block,y=correctResponse)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymin=correctResponse-se, ymax=correctResponse+se), size=0.5,   
    width=.25,position=position_dodge(.9)) +
  facet_grid(~numDist, labeller = as_labeller(c(`2`="2 distractors", `4`="4 distractors", `6`="6 distractors"))) +
  scale_y_continuous("Accuracy (%)",expand = c(0, 0)) +
  coord_cartesian(ylim=c(50,100)) +
  scale_x_discrete("Block type") +
  theme_apa()
pdf("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_accuracyfixvoppPlot.pdf", width = 7, paper = "special")
accuracy.fixVopp.bar
dev.off()
```

The results showed a main effect of distractor number (`r accuracy.fixVopp.distractors.table$full_result$numDist`), but no main effect of block context (`r accuracy.fixVopp.distractors.table$full_result$Block`), and no significant interaction between distractor number and block context (`r accuracy.fixVopp.distractors.table$full_result$numDist_Block`). The results of this analysis are shown in figure\ \@ref(fig:accuracyfixVoppPlot).

```{r accuracy_fixVopp_distractors_table, results = 'asis'}
#apa_table(accuracy.fixVopp.distractors.table$table, caption = "FixVOpp accuracy. Summary of the 2 x 4 repeated measures ANOVA used to test the effects of block type and distractor number on participant accuracy in the working memory task.", escape = FALSE)
```

```{r accuracy_fixVopp_pairwise, results = 'asis'}
#print(accuracy.fixVopp.distractors.distmain.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
```

```{r accuracyfixVoppPlot, fig.cap = "Participant accuracy as a function of set size and number of distractors present at encoding and retrieval.", fig.align = "center"}
include_graphics("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_accuracyfixVoppPlot.pdf", auto_pdf = TRUE)
```
### Capacity
```{r capacity_fixVopp_distractors, include=FALSE, echo=FALSE}
capacity.fixVopp.distractors.aov <- aov_ez(
  data = fixVopp.Vals,
  dv = "cowanC",
  id = "PID", 
  within = c("numDist", "Block")
)
#Interaction
capacity.fixVopp.distractors.distmain <- pairs(emmeans(capacity.fixVopp.distractors.aov, ~ numDist))

#create table
capacity.fixVopp.distractors.table <- apa_print(capacity.fixVopp.distractors.aov)
#Create followup table
capacity.fixVopp.distractors.distmain.table <- xtable(summary(capacity.fixVopp.distractors.distmain), caption = "Summary of the pairwise comparisons used to follow up the main interaction (capacity)", label = "tab:capacity.fixVopp.distractors.distmain.table")

#create plot
capacity.fixVopp.summarydata <- summarySE(fixVopp.Vals, measurevar="cowanC", groupvars=c("Block","numDist"))
capacity.fixVopp.bar <- ggplot(capacity.fixVopp.summarydata, aes( x=Block,y=cowanC)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymin=cowanC-se, ymax=cowanC+se), size=0.5,   
    width=.25,position=position_dodge(.9)) +
  facet_grid(~numDist, labeller = as_labeller(c(`2`="2 distractors", `4`="4 distractors", `6`="6 distractors"))) +
  scale_y_continuous("Capacity (%)",expand = c(0, 0)) +
  scale_x_discrete("Block type") +
  theme_apa()
pdf("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_capacityfixvoppPlot.pdf", width = 7, paper = "special")
capacity.fixVopp.bar
dev.off()
```

The results showed a main effect of distractor number (`r capacity.fixVopp.distractors.table$full_result$numDist`), but no main effect of block context (`r capacity.fixVopp.distractors.table$full_result$Block`), and no significant interaction between distractor number and block context (`r capacity.fixVopp.distractors.table$full_result$numDist_Block`). The results of this analysis are shown in figure\ \@ref(fig:capacityfixVoppPlot).

```{r capacity_fixVopp_distractors_table, results = 'asis'}
#apa_table(capacity.fixVopp.distractors.table$table, caption = "FixVOpp capacity. Summary of the 2 x 4 repeated measures ANOVA used to test the effects of block type and distractor number on participant capacity in the working memory task.", escape = FALSE)
```

```{r capacity_fixVopp_pairwise, results = 'asis'}
#print(capacity.fixVopp.distractors.distmain.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
```

```{r capacityfixVoppPlot, fig.cap = "Participant capacity as a function of set size and number of distractors present at encoding and retrieval.", fig.align = "center"}
include_graphics("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_capacityfixVoppPlot.pdf", auto_pdf = TRUE)
```

### Sensitivity
```{r sensitivity_fixVopp_distractors, include=FALSE, echo=FALSE}
sensitivity.fixVopp.distractors.aov <- aov_ez(
  data = fixVopp.Vals,
  dv = "D",
  id = "PID", 
  within = c("numDist", "Block")
)
#Interaction
sensitivity.fixVopp.distractors.distmain <- pairs(emmeans(sensitivity.fixVopp.distractors.aov, ~ numDist))

#create table
sensitivity.fixVopp.distractors.table <- apa_print(sensitivity.fixVopp.distractors.aov)
#Create followup table
sensitivity.fixVopp.distractors.distmain.table <- xtable(summary(sensitivity.fixVopp.distractors.distmain), caption = "Summary of the pairwise comparisons used to follow up the main interaction (sensitivity)", label = "tab:sensitivity.fixVopp.distractors.distmain.table")

#create plot
sensitivity.fixVopp.summarydata <- summarySE(fixVopp.Vals, measurevar="D", groupvars=c("Block","numDist"))
sensitivity.fixVopp.bar <- ggplot(sensitivity.fixVopp.summarydata, aes( x=Block,y=D)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymin=D-se, ymax=D+se), size=0.5,   
                width=.25,position=position_dodge(.9)) +
  facet_grid(~numDist, labeller = as_labeller(c(`2`="2 distractors", `4`="4 distractors", `6`="6 distractors"))) +
  scale_y_continuous("sensitivity (%)",expand = c(0, 0)) +
  scale_x_discrete("Block type") +
  theme_apa()
pdf("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_sensitivityfixvoppPlot.pdf", width = 7, paper = "special")
sensitivity.fixVopp.bar
dev.off()
```

The results showed a main effect of distractor number (`r sensitivity.fixVopp.distractors.table$full_result$numDist`), but no main effect of block context (`r sensitivity.fixVopp.distractors.table$full_result$Block`), and no significant interaction between distractor number and block context (`r sensitivity.fixVopp.distractors.table$full_result$numDist_Block`). The results of this analysis are shown in figure\ \@ref(fig:sensitivityfixVoppPlot).

```{r sensitivity_fixVopp_distractors_table, results = 'asis'}
#apa_table(sensitivity.fixVopp.distractors.table$table, caption = "FixVOpp sensitivity. Summary of the 2 x 4 repeated measures ANOVA used to test the effects of block type and distractor number on participant sensitivity in the working memory task.", escape = FALSE)
```

```{r sensitivity_fixVopp_pairwise, results = 'asis'}
#print(sensitivity.fixVopp.distractors.distmain.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
```

```{r sensitivityfixVoppPlot, fig.cap = "Participant sensitivity as a function of set size and number of distractors present at encoding and retrieval.", fig.align = "center"}
include_graphics("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_sensitivityfixVoppPlot.pdf", auto_pdf = TRUE)
```
### Response bias
```{r criterion_fixVopp_distractors, include=FALSE, echo=FALSE}
criterion.fixVopp.distractors.aov <- aov_ez(
  data = fixVopp.Vals,
  dv = "C",
  id = "PID", 
  within = c("numDist", "Block")
)
#Interaction
criterion.fixVopp.distractors.distmain <- pairs(emmeans(criterion.fixVopp.distractors.aov, ~ numDist))

#create table
criterion.fixVopp.distractors.table <- apa_print(criterion.fixVopp.distractors.aov)

#create plot
criterion.fixVopp.summarydata <- summarySE(fixVopp.Vals, measurevar="C", groupvars=c("Block","numDist"))
criterion.fixVopp.bar <- ggplot(criterion.fixVopp.summarydata, aes( x=Block,y=C)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymin=C-se, ymax=C+se), size=0.5,   
                width=.25,position=position_dodge(.9)) +
  facet_grid(~numDist, labeller = as_labeller(c(`2`="2 distractors", `4`="4 distractors", `6`="6 distractors"))) +
  scale_y_continuous("criterion (%)",expand = c(0, 0)) +
  scale_x_discrete("Block type") +
  theme_apa()
pdf("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_criterionfixvoppPlot.pdf", width = 7, paper = "special")
criterion.fixVopp.bar
dev.off()
```

The results showed no significant main effect of distractor number (`r criterion.fixVopp.distractors.table$full_result$numDist`), no significant main effect of block context (`r criterion.fixVopp.distractors.table$full_result$Block`), and no significant interaction between distractor number and block context (`r criterion.fixVopp.distractors.table$full_result$numDist_Block`). The results are displayed in figure\ \@ref(fig:criterionfixVoppPlot).

```{r criterion_fixVopp_distractors_table, results = 'asis'}
#apa_table(criterion.fixVopp.distractors.table$table, caption = "FixVOpp criterion. Summary of the 2 x 4 repeated measures ANOVA used to test the effects of block type and distractor number on participant criterion in the working memory task.", escape = FALSE)
```

```{r criterion_fixVopp_pairwise, results = 'asis'}
#print(criterion.fixVopp.distractors.distmain.table, comment=FALSE, caption.placement = "top", latex.environments="flushleft")
```

```{r criterionfixVoppPlot, fig.cap = "Participant criterion as a function of set size and number of distractors present at encoding and retrieval.", fig.align = "center"}
include_graphics("C:/Users/dhen061/Desktop/ThesisWriting/Figures/WMBehav_criterionfixVoppPlot.pdf", auto_pdf = TRUE)
```
## Individual capacity and distraction
```{r reliability,echo=FALSE,include=FALSE}
#Greate Group
extractGroupData <- subset(fixed.Vals,DistNum==0&targetNum>2)
groupDataSummary <- dplyr::summarise(group_by(extractGroupData, PID),capacity=mean(cowanC))
for (subj in unique(fixed.Vals$PID)) {
  fixed.Vals$avgCapacity[fixed.Vals$PID==subj] <- groupDataSummary$capacity[groupDataSummary$PID==subj]
  var.Vals$avgCapacity[var.Vals$PID==subj] <- groupDataSummary$capacity[groupDataSummary$PID==subj]
  
  fixVopp.Vals$avgCapacity[fixVopp.Vals$PID==subj] <- groupDataSummary$capacity[groupDataSummary$PID==subj]
  fixVmat.Vals$avgCapacity[fixVmat.Vals$PID==subj] <- groupDataSummary$capacity[groupDataSummary$PID==subj]
}

evenGroupData <- subset(evenTable,DistNum==0)
evenDataSummary <- dplyr::summarise(group_by(evenGroupData, PID),capacity=mean(cowanC),acc=mean(correctResponse))
for (subj in unique(evenTable$PID)) {
  evenTable$avgCapacity[evenTable$PID==subj] <- evenDataSummary$capacity[evenDataSummary$PID==subj]
}

oddGroupData <- subset(oddTable,DistNum==0)
oddDataSummary <- dplyr::summarise(group_by(oddGroupData, PID),capacity=mean(cowanC),acc=mean(correctResponse))
for (subj in unique(oddTable$PID)) {
  oddTable$avgCapacity[oddTable$PID==subj] <- oddDataSummary$capacity[oddDataSummary$PID==subj]
}

#capacity relibility
capacity.splithalf <- cor(oddDataSummary$capacity, evenDataSummary$capacity)
capacity.SB <- (2*capacity.splithalf)/(1+capacity.splithalf)
```

In our final set of analyses we sought to test the relationship between an individual's working memory capacity and distractor filtering in this task. Individual capacity was estimated using the fixed zero distractor blocks in order to prevent capacity estimates from including any trials which directly required distractor suppression.. We tested the internal reliability of this estimate by performing a split-half correlation on capacity measured from odd and even trials. The results produced a Spearman-Brown coefficient of `r as.character(round(capacity.SB,2))`.

### Individual differences in the fixed distractor blocks

```{r measuringDistractorEffectInFixed,echo=FALSE,include=FALSE}
#"First, we examined the correlation between the filtering cost described above and WM span."
zeroDist <- subset(fixed.Vals, DistNum==0)
nonZeroDist <- subset(fixed.Vals, DistNum!=0)
zeroDist<- dplyr::summarise(group_by(zeroDist,PID),accuracy=mean(D))
nonZeroDist<- dplyr::summarise(group_by(nonZeroDist,PID),accuracy=mean(D))
for (subj in unique(allData$PID)) {
  fixed.Vals$distDiff[fixed.Vals$PID==subj] <- zeroDist$accuracy[zeroDist$PID==subj]-nonZeroDist$accuracy[nonZeroDist$PID==subj]
}
testCorrel <- dplyr::summarise(group_by(fixed.Vals,PID),cap = mean(avgCapacity), dist=mean(distDiff))
corValue <- cor(testCorrel$cap,testCorrel$dist)
corValuep <- cor.test(testCorrel$cap,testCorrel$dist)
corPlot <- ggplot(data=fixed.Vals,aes(x=distDiff,y=avgCapacity)) +geom_point()+geom_smooth(method=lm) +theme_apa()

#"In our next analysis, we entered WM span as a covariate into the ANOVA described above."
accuracy.fixedonly.targanddist.ancova <- aov_ez(
  data = fixed.Vals,
  dv = "D",
  id = "PID", 
  within = "DistNum",
  covariate = "avgCapacity"
)
fixed.ancova <- apa_print(accuracy.fixedonly.targanddist.ancova)
#"Next, we used regression to estimate shared variance btween filtering and nonfiltering trials. Presumably he shared variance between distractor-absent (nonfiltering) and distractor-present (filtering" trials represents any demands on storage capacity and control processes that are common to all trial types. After controlling for this shared variance, any residual shared variance between WM span and distractor-present trials should be due to WM-related control abilities that are unique to these trials."
twoDist <- subset(fixed.Vals, DistNum==2)
twoDist <- dplyr::summarise(group_by(twoDist,PID),accuracy=mean(D))
fourDist <- subset(fixed.Vals, DistNum==4)
fourDist <- dplyr::summarise(group_by(fourDist,PID),accuracy=mean(D))
sixDist <- subset(fixed.Vals, DistNum==6)
sixDist <- dplyr::summarise(group_by(sixDist,PID),accuracy=mean(D))

fixedRegressSheet <- data.frame(PID=zeroDist$PID,zeroDist=zeroDist$accuracy,twoDist=twoDist$accuracy,fourDist=fourDist$accuracy,sixDist=sixDist$accuracy)
fixedRegressSheet$Capacity <- dplyr::summarise(group_by(subset(fixed.Vals, DistNum==0),PID),cap = mean(avgCapacity))$cap
fixedModel1 <- lm(sixDist~zeroDist,fixedRegressSheet)
fixedModel2 <- lm(sixDist~zeroDist+twoDist,fixedRegressSheet)
fixedModel3 <- lm(sixDist~zeroDist+twoDist+fourDist,fixedRegressSheet)
fixedModel4 <- lm(sixDist~zeroDist+twoDist+fourDist+Capacity,fixedRegressSheet)
fixedRegression <- anova(fixedModel1,fixedModel2,fixedModel3,fixedModel4)

resid1 <- resid(fixedModel1)
ggplot(fixedRegressSheet, aes(x=twoDist, y=resid1)) + geom_point() +geom_smooth(method=lm) +theme_apa()
resid2 <- resid(fixedModel2)
ggplot(fixedRegressSheet, aes(x=fourDist, y=resid2)) + geom_point() +geom_smooth(method=lm) +theme_apa()

#Plot the part correlation of capacity after accounting for fixNZ accuracy
fixedRegressSheet$m1Residual <- resid(fixedModel1)
ggplot(fixedRegressSheet, aes(x=Capacity, y=m1Residual)) + geom_point() +geom_smooth(method=lm) +theme_apa()
```

To evaluate the effect of capacity on distraction, first we entered capacity as a covariate in the above ANOVA which tested for the effect of distractor number on accuracy in the fixed distractor blocks. Although the results showed that there was a significant main effect of working memory capacity (`r fixed.ancova$full_result$avgCapacity`), such that individuals with larger capacities were more accurate on the task (r=0.40, p<0.001), capacity did not interact with distractor number (`r fixed.ancova$full_result$avgCapacity_DistNum`). Next, we performed a correlation to test for a relationship between working memory capacity and filtering cost in the fixed blocks. Filtering cost was calculated by subtracting accuracy in the the distractor present blocks from accuracy in the distractor absent blocks. The results showed a marginally significant relationship between capacity and filtering cost such that as capacity increased, the cost of distractors also increased (r = 0.27, p = 0.045).

### Individual differences in the target-match blocks
```{r measuringDistractorEffectIntargEqual,echo=FALSE,include=FALSE}
#Because distractor number and target number are conflated, we can't calculate filter cost like above, so we skip that analysis and jst do the other two.
#First, repeat ANOVAs from above including WM capacity as a covariate.
fixVmat.ancova.results <- aov_ez(
  data = fixVmat.Vals,
  dv = "D",
  id = "PID", 
  within = c("numDist", "Block"),
  covariate = "avgCapacity"
)
fixVmat.ancova <- apa_print(fixVmat.ancova.results)
#After accounting for shared variance between fixed and variable accuracy, can capacity predict some variance in var block accuracy
fixzeroDist <- subset(fixed.Vals, DistNum==0)
fixzeroDist<- dplyr::summarise(group_by(fixzeroDist,PID),accuracy=mean(D))
fixnonZDist <- subset(fixed.Vals, DistNum==targetNum)
fixnonZDist<- dplyr::summarise(group_by(fixnonZDist,PID),accuracy=mean(D))
varnonZeroDist <- subset(var.Vals, DistNum=="targEqual")
varnonZeroDist<- dplyr::summarise(group_by(varnonZeroDist,PID),accuracy=mean(D))

regressSheet <- data.frame(PID=fixzeroDist$PID)
regressSheet$fixZ <- fixzeroDist$accuracy
regressSheet$fixNZ <- fixnonZDist$accuracy
regressSheet$varAcc <- varnonZeroDist$accuracy
regressSheet$Capacity <- dplyr::summarise(group_by(subset(fixed.Vals, DistNum==0),PID),cap = mean(avgCapacity))$cap

model1 <- lm(varAcc ~fixNZ,regressSheet)
model2 <- lm(varAcc ~fixNZ+Capacity,regressSheet)
hRegression <- anova(model1,model2)
#Plot the part correlation of capacity after accounting for fixNZ accuracy
regressSheet$m1Residual <-residual <- resid(model1)
ggplot(regressSheet, aes(x=Capacity, y=m1Residual)) + geom_point() +geom_smooth(method=lm) +theme_apa()
```

```{r makeM1RegressionTable, include=FALSE,echo=FALSE}
#Make my own table because I can't get any of the packages to work >:/
m1Full <- summary(model1)
m2Full <- summary(model2)
m1Sum <- format(round(m1Full$coefficients[,1:3],2),nsmall=2)
m2Sum <- format(round(m2Full$coefficients[,1:3],2),nsmall=2)
m1Sum <- cbind(m1Sum,format(round(m1Full$coefficients[,4],3),nsmall=3))
m2Sum <- cbind(m2Sum,format(round(m2Full$coefficients[,4],3),nsmall=3))
m1Sum[as.numeric(m1Sum[,4])<0.001,4]="<0.001"
m2Sum[as.numeric(m2Sum[,4])<0.001,4]="<0.001"
fullTable <- rbind(c(""),m1Sum,c(""),m2Sum)
#fullTable <- format(round(fullTable,2),nsmall=2)
fullTable <- cbind(c("Step 1","Constant","Fixed trials","Step 2","Constant","Fixed trials","Capacity"),fullTable)
fullTable <- data.frame(fullTable)

R <- c(format(round(m1Full$r.squared,2),nsmall=2),"","",format(round(m2Full$r.squared,2),nsmall=2),"","","")
Adj.R <- c(format(round(m1Full$adj.r.squared,2),nsmall=2),"","",format(round(m2Full$adj.r.squared,2),nsmall=2),"","","")
p.value <- c("<0.001","","","<0.001","","","")
F.value <- c(format(round(m1Full$fstatistic[1],2),nsmall=2),"","",format(round(m2Full$fstatistic[1],2),nsmall=2),"","","")
df <- c(paste(as.character(round(m1Full$fstatistic[2])),",",round(m1Full$fstatistic[3]),sep=""),"","",paste(as.character(round(m2Full$fstatistic[2])),",",round(m2Full$fstatistic[3]),sep=""),"","","")
frame = data.frame(R,Adj.R,F.value,df,p.value)
fullTable <- cbind(fullTable,frame)
colnames(fullTable) <- c("","$B$","SE","t","p","$R^2$","$Adj. R^2$","F","df","p")


modelTable <- xtable(fullTable, caption = "Summary of the hierarchical regression results predicting performance in the target-match blocks", label = "tab:modelOneTable")
```

```{r printM1RegressTable, results='asis'}
print(modelTable, comment=FALSE, caption.placement = "top", latex.environments="flushleft",include.rownames=FALSE, sanitize.text.function = function(x) {x})
```

To evaluate the effect of capacity on distraction in the target-match blocks, first we entered capacity as a covariate in the above ANOVA which tested for the effect of block type and distractor number on accuracy in the target-match blocks. The results showed that there was no significant main effect of working memory capacity (`r fixVmat.ancova$full_result$avgCapacity`), and capacity did not interact with either block type (`r fixVmat.ancova$full_result$avgCapacity_Block`), distractor number (`r fixVmat.ancova$full_result$avgCapacity_numDist`), or the interaction between block type and distractor number (`r fixVmat.ancova$full_result$avgCapacity_numDist_Block`). Next, we used regression to estimate the shared variance between the targMat trials and their fixed block equivalents. After controlling for this variance, any residual shared variance between working memory capacity and accuracy in the targMat block should be due to working memory control abilities that are unique to inter-trial effects in the targMat block. As shown in table .X., accuracy in the fixed block trials accounts for a significant amount of variance in targMat accuracy, however working memory capacity also accounts for a unique portion of variance in the targMat block and significantly improves the model's performance (F(1,53)=7.92, p=0.007). Individuals with a higher working memory capacity perform more accurately on the target-inverse trials, even after controlling for the shared variance between their fixed block accuracy and target-inverse accuracy.  For a summary of the regression results see table\ \@ref(tab:modelOneTable).

### Individual differences in the target-inverse blocks
```{r measuringDistractorEffectIntargOpp,echo=FALSE,include=FALSE}
#Because distractor number and target number are conflated, we can't calculate filter cost like above, so we skip that analysis and jst do the other two.
#First, repeat ANOVAs from above including WM capacity as a covariate.
fixVopp.ancova.results <- aov_ez(
  data = fixVopp.Vals,
  dv = "D",
  id = "PID", 
  within = c("numDist", "Block"),
  covariate = "avgCapacity"
)
fixVopp.ancova <- apa_print(fixVopp.ancova.results)
#After accounting for shared variance between fixed and variable accuracy, can capacity predict some variance in var block accuracy?
fixnonZDist <- subset(fixed.Vals, DistNum==8-targetNum)
fixnonZDist<- dplyr::summarise(group_by(fixnonZDist,PID),accuracy=mean(D))
varnonZeroDist <- subset(var.Vals, DistNum=="targOpp")
varnonZeroDist<- dplyr::summarise(group_by(varnonZeroDist,PID),accuracy=mean(D))

regressSheet <- data.frame(PID=fixnonZDist$PID)
regressSheet$fixNZ <- fixnonZDist$accuracy
regressSheet$varAcc <- varnonZeroDist$accuracy
regressSheet$Capacity <- dplyr::summarise(group_by(subset(fixed.Vals, DistNum==4|DistNum==6),PID),cap = mean(avgCapacity))$cap

model1 <- lm(varAcc ~fixNZ,regressSheet)
model2 <- lm(varAcc ~fixNZ+Capacity,regressSheet)
hRegression <- anova(model1,model2)
#Plot the part correlation of capacity after accounting for fixNZ accuracy
regressSheet$m1Residual <-residual <- resid(model1)
ggplot(regressSheet, aes(x=Capacity, y=m1Residual)) + geom_point() +geom_smooth(method=lm) +theme_apa()
```

```{r makeM2RegressionTable, include=FALSE,echo=FALSE}
#Make my own table because I can't get any of the packages to work >:/
m1Full <- summary(model1)
m2Full <- summary(model2)
m1Sum <- format(round(m1Full$coefficients[,1:3],2),nsmall=2)
m2Sum <- format(round(m2Full$coefficients[,1:3],2),nsmall=2)
m1Sum <- cbind(m1Sum,format(round(m1Full$coefficients[,4],3),nsmall=3))
m2Sum <- cbind(m2Sum,format(round(m2Full$coefficients[,4],3),nsmall=3))
m1Sum[as.numeric(m1Sum[,4])<0.001,4]="<0.001"
m2Sum[as.numeric(m2Sum[,4])<0.001,4]="<0.001"
fullTable <- rbind(c(""),m1Sum,c(""),m2Sum)
#fullTable <- format(round(fullTable,2),nsmall=2)
fullTable <- cbind(c("Step 1","Constant","Fixed trials","Step 2","Constant","Fixed trials","Capacity"),fullTable)
fullTable <- data.frame(fullTable)

R <- c(format(round(m1Full$r.squared,2),nsmall=2),"","",format(round(m2Full$r.squared,2),nsmall=2),"","","")
Adj.R <- c(format(round(m1Full$adj.r.squared,2),nsmall=2),"","",format(round(m2Full$adj.r.squared,2),nsmall=2),"","","")
p.value <- c("<0.001","","","<0.001","","","")
F.value <- c(format(round(m1Full$fstatistic[1],2),nsmall=2),"","",format(round(m2Full$fstatistic[1],2),nsmall=2),"","","")
df <- c(paste(as.character(round(m1Full$fstatistic[2])),",",round(m1Full$fstatistic[3]),sep=""),"","",paste(as.character(round(m2Full$fstatistic[2])),",",round(m2Full$fstatistic[3]),sep=""),"","","")
frame = data.frame(R,Adj.R,F.value,df,p.value)
fullTable <- cbind(fullTable,frame)
colnames(fullTable) <- c("","$B$","SE","t","p","$R^2$","$Adj. R^2$","F","df","p")


modelTable <- xtable(fullTable, caption = "Summary of the hierarchical regression results predicting performance in the target-inverse blocks", label = "tab:modelTwoTable")
```

```{r printM2RegressTable, results='asis'}
print(modelTable, comment=FALSE, caption.placement = "top", latex.environments="flushleft",include.rownames=FALSE, sanitize.text.function = function(x) {x})
```

To evaluate the effect of capacity on distraction, first we entered capacity as a covariate in the above ANOVA which tested for the effect of bock type and distractor number on accuracy in the target-inverse blocks. The results showed that there was no significant main effect of working memory capacity (`r fixVopp.ancova$full_result$avgCapacity`), and capacity did not interact with either block type (`r fixVopp.ancova$full_result$avgCapacity_Block`), distractor number (`r fixVopp.ancova$full_result$avgCapacity_numDist`), or the interaction between block type and distractor number (`r fixVopp.ancova$full_result$avgCapacity_numDist_Block`). Next, we used regression to estimate the shared variance between the target-inverse trials and their fixed block equivalents. After controlling for this variance, any residual shared variance between working memory capacity and accuracy in the target-inverse block should be due to working memory control abilities that are unique to inter-trial effects in the target-inverse block. As shown in table .X., accuracy in the fixed block trials accounts for a significant amount of variance in target-inverse accuracy, however working memory capacity also accounts for a unique portion of variance in the target-inverse block and significantly improves the model's performance (F(1,53)=8.05, p=0.006). Individuals with a higher working memory capacity perform more accurately on the target-inverse trials, even after controlling for the shared variance between their fixed block accuracy and target-inverse accuracy. For a summary of the regression results see table\ \@ref(tab:modelTwoTable).

# Discussion

The number of irrelevant objects presented in the change detection task effects performance on the task.

There was little evidence of an effect of block context on individual performance.
 
Our variable distractor blocks never had 0 distractors, maybe this would boost block context effects as currently participants might be maintaining a filter the entire block whereas if there were 0 distractor trials maybe they would be fluctuating between active suppression or not. While we see some differences between distractor number in the fixed trials, the largest effects are between 0 and other blocks.

What about estimating the R across distractor number on jack knifed estimates of capacity etc. as measure of distractor effect (average of individual R is no the same as R of averaged data.)

Kinda makes sense that target-inverse no diff from fixed because in both cases, the proportion of targs to dists is changing on a trial by trial basis.

\newpage


# References
```{r WMB_create_r-references}
r_refs(file = "r-references.bib")
```

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}